### 2015-10-15 pmf.tex
initial

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Draft of cosmological analysis section in SPT lensing 2500 sq.deg. paper Zahn et al. (2015)
%Gabrielle Simard, Feb. 9th, 2015.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentclass[apj]{emulateapj}
\documentclass[preprint]{emulateapj}

\usepackage[table,usenames,dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{multirow}

\newcommand{\sqdeg}{deg$^2$ }
\newcommand{\lcdm}{$\Lambda CDM$ }
\newcommand{\omb}{\ensuremath{\Omega_b h^2}}
\newcommand{\omc}{\ensuremath{\Omega_c h^2}}
\newcommand{\clpp}{\ensuremath{C_{L}^{\phi\phi}}}

\newcommand{\planck}{{\sl Planck}}
\newcommand{\wmap}{{\sl WMAP}}

\newcommand{\gab}[1]{\textcolor{Orchid}{[{\bf GS}: #1]}}

\bibliographystyle{fapj}

% ref to section \S\ref{sec:label}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{PMF}
\author{TBD}

\section{Results}
\label{sec:results}

\bibliography{pmf}

\end{document}

### 2015-10-16 pmf.tex
inital work

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Draft of cosmological analysis section in SPT lensing 2500 sq.deg. paper Zahn et al. (2015)
-%Gabrielle Simard, Feb. 9th, 2015.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \documentclass[preprint]{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
 
@@
 \newcommand{\sqdeg}{deg$^2$ }
-\newcommand{\lcdm}{$\Lambda CDM$ }
 \newcommand{\omb}{\ensuremath{\Omega_b h^2}}
@@
 \newcommand{\clpp}{\ensuremath{C_{L}^{\phi\phi}}}
+\newcommand{\cpmf}{\ensuremath{C_{\ell}^{\rm pmf}}}
+\newcommand{\apmf}{\ensuremath{A_{\rm pmf}}}
+\newcommand{\alens}{\ensuremath{A_{\rm lens}}}
+\newcommand{\lcdm}{\ensuremath{\Lambda}CDM}
 
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
 \newcommand{\planck}{{\sl Planck}}
 \newcommand{\wmap}{{\sl WMAP}}
+\newcommand{\bicepkeck}{BICEP2/Keck}
+\newcommand{\sptnew}{SPT-3G}
+\newcommand{\pb}{POLARBEAR}
+\newcommand{\simons}{Simons Array}
+\newcommand{\sptpol}{SPTpol}
+\newcommand{\advactpol}{Adv.~ACTpol}
 
+\newcommand{\tbd}[1]{\textcolor{Red}{{\bf TBD}: #1}}
 \newcommand{\gab}[1]{\textcolor{Orchid}{[{\bf GS}: #1]}}
@@
 
-\title{PMF}
+\title{Current and future constraints on primordial magnetic fields}
 \author{TBD}
+
+\email{christian.reichardt@unimelb.edu.au}
+
+\begin{abstract}
+
+We present new limits on the amplitude of any primordial magnetic field (PMF) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
+We reduce six-fold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 2.0\tbd{XX}$ from Planck alone to $\apmf < 0.33$ for the combined dataset at 95\% CL. 
+Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
+We also consider future limits from stage III CMB experiments (like \sptnew{},  \advactpol, or the \simons) and a stage IV concept. 
+Stage III experiments will reduce the current limit by an additional factor of \tbd{XX}; this will become a factor of \tbd{XX} for stage IV. 
+\tbd{maybe:} The constraints from a stage IV experiment have the potential to rule out much of the parameter space for PMFs.
+\tbd{really if could rule out them as explanation for galaxy fields...
+is there a lower bound for them to be useful?}
+
+\end{abstract}
+
+\keywords{dark energy --- cosmic background radiation --- early universe }
+\section{Introduction}
+\label{sec:intro}
+
+The outline of the paper is as follows. 
+In \S\ref{sec:data}, we lay out the data used and the MCMC implementation used to constrain the PMF amplitude. 
+We present the results of this analysis on current data in \S\ref{sec:results}. 
+The assumed parameters for future experiments and the resulting Fisher matrix forecasts are described in \S\ref{sec:forecasts}. 
+We conclude in \S\ref{sec:conclusions}.
+
+\section{Data and Methods}
+\label{sec:data}
+
+We use  Markov chain Monte Carlo (MCMC) methods to study constraints on the primordial magnetic field. 
+In this section, we first describe the CMB temperature and polarization anisotropy data used, and then discuss the MCMC implementation.
+
+\subsection{Data}
+
+We use a compendium of current measurements of the CMB temperature and polarization anisotropies from ground-based and satellite experiments. 
+We use \planck{} data from the 2015 release to constrain the TT, TE, EE and lensing power spectra. 
+These include the \tbd{insert modules}.
+
+In addition to the \planck{} data, we use all recent CMB polarization measurements that are publicly available. 
+First, we include TE and EE spectrum measurements\citep{crites15} for $\ell \in [500,3000]$ and BB bandpowers covering $\ell \in [500,2000]$ \citep{keisler15} from SPTpol. 
+We also add the BB bandpowers from \pb{} that cover the multipoles from 500 to 2500 \citep{pb-bb15}. 
+Both the \sptpol{} and \pb{} bandpowers primary constrain the vector mode of the PMF given the angular scales measured. 
+Finally, we include the joint BICEP2, Keck Array and \planck{} joint analysis \citep{bicepkeckplanck15}. 
+This latter dataset also places limits on the tensor mode of the PMF due to its coverage of lower multipoles. 
+In all chains, we marginalize over the recommended foreground models for each data set. 
+We do not however require these consistency between these foreground models since the data don't have identical flux cuts and so on. 
+In the case of an upper limit this treatment is conservative since weaker foreground constraints or residual point source power would only add power and weaken the limit on the PMF.
+
+\subsection{Methods}
+
+We use MCMC methods to determine the parameter constraints reported in this work. 
+The results are calculated using  the {\textsc CosmoMC}\footnote{http://cosmologist.info/cosmomc (Aug 2011)} package \citep{lewis02b}. 
+CosmoMC invokes  CAMB\footnote{http://camb.info (July 2011)}  \citep{lewis00} to calculate the CMB power spectrum for each set of cosmological parameters. 
+Although CosmoMC and CAMB have a partial implementation of PMF, we choose to adopt a simpler, fast template-based calculation for the PMF power. 
+We have adapted CosmoMC to add a scaled version of the template to all four CMB power spectra: TT, TE, EE, and BB, where the scale factor is \apmf. 
+\be
+C_\ell = C_\ell (CAMB) + \apmf \cpmf
+\ee
+The calculation of the PMF template, \cpmf, is described later. 
+Note that no other effect of the PMF is considered; this is one reason we only consider CMB data.
+
+Unless noted, we assume the six parameter spatially flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF. 
+We adopt flat priors on all parameters. 
+In most chains, we also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
+Finally, in some cases, we allow non-zero tensors, parameterized as is normal, by the tensor-to-scalar ratio, r.
 
@@
 
+\section{Forecasts}
+\label{sec:forecasts}
+
+\section{Conclusions}
+\label{sec:conclusions}
+
 \bibliography{pmf}

### 2015-10-29 pmf.tex
param summ

@@
 
+\begin{table}[htb]
+\begin{center}
+\caption{\label{tab:param_all} All parameter constraints}
+\tiny
+\begin{tabular}{l || c c c c c c c | c}
+Chain & $\Omega_b h^2$  & $\Omega_c h^2$  & $\theta$  & $\tau$  & logA  & $n_s$  & $A_{lens}$  & $A_{pmf}$ \\
+lcdm\_alens\_all & $ 0.02240\pm  0.00026$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9696\pm  0.0062$ & $ 1.121 \pm  0.064$ & $< 0.33$ \\
+lcdm\_alens\_nopmf\_all & $ 0.02241\pm  0.00024$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.065\pm  0.016$ & $ 3.059\pm  0.029$ & $ 0.9694\pm  0.0062$ & $ 1.136 \pm  0.063$ & $< 0.00$ \\
+lcdm\_alens\_nopmf\_planck & $ 0.02256\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04121\pm  0.00048$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9721\pm  0.0063$ & $ 1.175 \pm  0.067$ & $< 0.00$ \\
+lcdm\_alens\_planckTT & $ 0.02252\pm  0.00031$ & $ 0.1174\pm  0.0027$ & $ 1.04122\pm  0.00053$ & $ 0.070\pm  0.050$ & $ 3.068\pm  0.098$ & $ 0.9713\pm  0.0080$ & $ 1.155 \pm  0.136$ & $< 1.34$ \\
+lcdm\_alens\_planckTT\_TEB & $ 0.02264\pm  0.00029$ & $ 0.1161\pm  0.0025$ & $ 1.04141\pm  0.00053$ & $ 0.055\pm  0.021$ & $ 3.036\pm  0.042$ & $ 0.9755\pm  0.0072$ & $ 1.241 \pm  0.104$ & $< 0.77$ \\
+lcdm\_alens\_planck & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00046$ & $ 0.068\pm  0.016$ & $ 3.065\pm  0.030$ & $ 0.9723\pm  0.0062$ & $ 1.171 \pm  0.070$ & $< 0.68$ \\
+lcdm\_alens\_planck\_bicep & $ 0.02255\pm  0.00026$ & $ 0.1174\pm  0.0020$ & $ 1.04120\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0063$ & $ 1.177 \pm  0.068$ & $< 0.36$ \\
+lcdm\_alens\_planck\_pb & $ 0.02255\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04119\pm  0.00046$ & $ 0.068\pm  0.017$ & $ 3.066\pm  0.031$ & $ 0.9725\pm  0.0064$ & $ 1.171 \pm  0.068$ & $< 0.63$ \\
+lcdm\_alens\_planck\_sptpolB & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0062$ & $ 1.159 \pm  0.067$ & $< 0.42$ \\
+lcdm\_alens\_planck\_sptpolE & $ 0.02239\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00048$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9698\pm  0.0061$ & $ 1.119 \pm  0.067$ & $< 0.73$ \\
+lcdm\_planck & $ 0.02225\pm  0.00023$ & $ 0.1184\pm  0.0020$ & $ 1.04102\pm  0.00047$ & $ 0.066\pm  0.017$ & $ 3.062\pm  0.030$ & $ 0.9682\pm  0.0060$ & $ 0.000 \pm  0.000$ & $< 0.73$ \\
+lcdm\_r\_alens\_all & $ 0.02240\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.029$ & $ 0.9702\pm  0.0062$ & $ 1.123 \pm  0.063$ & $< 0.27$ \\
+\end{tabular}
+\tablecomments{ 
+Summary of results (will be trimmed for paper). 
+} \normalsize
+\end{center}
+\end{table}
+
 \section{Forecasts}

### 2015-10-30 pmf.tex
edits

@@
 \newcommand{\apmf}{\ensuremath{A_{\rm pmf}}}
+\newcommand{\bpmf}{\ensuremath{B_{\rm 1\,Mpc}}}
 \newcommand{\alens}{\ensuremath{A_{\rm lens}}}
@@
 We use \planck{} data from the 2015 release to constrain the TT, TE, EE and lensing power spectra. 
-These include the \tbd{insert modules}.
+Specifically, these are the ``plik\_dx11dr21\_HM\_v18\_TT", ``lowTEB" and ``lensing" \planck{} likelihood modules.
 
@@
 We adopt flat priors on all parameters. 
-In most chains, we also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
+In particular, note that this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
+In many chains, we also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
 Finally, in some cases, we allow non-zero tensors, parameterized as is normal, by the tensor-to-scalar ratio, r.
+
+\subsection{Primordial Magnetic Field Template}
+
+\tbd{Chang to describe the template calculation and template parameters}
+
+We can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:
+\be
+\apmf \propto \bpmf^4.
+\ee
+An unfortunate consequence of this steep scaling is that substantial reductions in the observationally allowed power lead to only modestly better limits on the magnetic field strength. 
+However, if a PMF is detected, this same steep scaling would allow excellent constraints on its properties.
 
@@
 
-\begin{table}[htb]
+We find the addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement. 
+With Planck alone, the 95\% confidence upper limit is $\apmf <  0.68$ when $\alens$ is allowed to vary; with the ground-based experiments, this limit drops to $\apmf <  0.33$. 
+We test which datasets are important by adding single datasets to the \planck{} set, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  0.36$) and \sptpol{} ($\apmf <  0.42$) B-mode power spectrum measurements.
+The other datasets do not have a large impact on the observed limits.
+
+We propagate these limits on the observed PMF power into limits on the magnetic field strength, \bpmf. 
+Due to the scaling with the fourth power, an upper limit with a flat prior on \apmf{} would lead to an apparent `detection' of \bpmf. 
+We therefor importance sample the chains to generate a flat prior on \bpmf. 
+We find a 95\% limit of $\bpmf < XX$\,nG for \planck{} alone, consistent with \citep{planckpmf} with $n$ held fixed as we've done. 
+This is reduced to $\bpmf < XX$\,nG for the combined dataset.
+
+\begin{table*}[htb]
 \begin{center}
@@
 \end{center}
-\end{table}
+\end{table*}
 

### 2015-11-04 pmf.tex
chang's para

@@
 
+The density and stress perturbations introduced by PMFs give rise to the vorticity and gravitational waves.
+The CMB anisotropies created in this photon-baryon plasma inherit two characteristic properties, i.e., vector and tensor modes which can be determined by modified Boltzman equations involving sources from PMFs.
+The PMF filed is assumed to be Gaussian and its power spectrum is given by a power law $Ak^{n_s}$.
+Here $n_s$ is the spectral index of PMF and $A$ is its amplitude.
+The rms of the PMF energy can be quantified over a length 1\rm{Mpc} and $B_{\rm{1Mpc}}$ equivalently determines the PMF amplitude.
+The PMF stress anisotropies can be compensated by neutrinos if neutrinos decoupled too early so it is also important to consider when the PMF was generated and another parameter $\beta=\ln(a_{\nu}/a_{\rm{PMF}})$ is usually adopted.
+
 We can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:

### 2015-11-05 pmf.tex
TEST
Added the details of code and parameters

@@
 
+The PMF power spectra are computed by a modified code CMBACT\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} with parameters $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_s$=-2.9 and $a_{\nu}/a_{\rm{PMF}}$=$10^9$.
+They are used as a template of PMF power spectrum calculation, i.e., the new PMF power spectra with different amplitudes $B_{\rm{1Mpc}}$ are derived from a simply scaling law.
+
 We can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:

### 2015-11-09 pmf.tex
small

--- 2015-11-04 pmf.tex
@@
 
+Precision measurements of cosmic microwave background (CMB) polarization open up new tests for extensions to the  standard cosmological model. 
+One such extension would be the existence of a primordial magnetic field (PMF).
+
 The outline of the paper is as follows. 
@@
 Both the \sptpol{} and \pb{} bandpowers primary constrain the vector mode of the PMF given the angular scales measured. 
-Finally, we include the joint BICEP2, Keck Array and \planck{} joint analysis \citep{bicepkeckplanck15}. 
+Finally, we include the latest BICEP2 and Keck Array  joint analysis \citep{bicepkeck}. 
 This latter dataset also places limits on the tensor mode of the PMF due to its coverage of lower multipoles. 
@@
 We use MCMC methods to determine the parameter constraints reported in this work. 
-The results are calculated using  the {\textsc CosmoMC}\footnote{http://cosmologist.info/cosmomc (Aug 2011)} package \citep{lewis02b}. 
-CosmoMC invokes  CAMB\footnote{http://camb.info (July 2011)}  \citep{lewis00} to calculate the CMB power spectrum for each set of cosmological parameters. 
+The results are calculated using  the {\textsc CosmoMC}\footnote{http://cosmologist.info/cosmomc (July 2015 version)} package \citep{lewis02b}. 
+CosmoMC invokes  CAMB\footnote{http://camb.info}  \citep{lewis00} to calculate the CMB power spectrum for each set of cosmological parameters. 
 Although CosmoMC and CAMB have a partial implementation of PMF, we choose to adopt a simpler, fast template-based calculation for the PMF power. 
@@
 
-\tbd{Chang to describe the template calculation and template parameters}
-
 The density and stress perturbations introduced by PMFs give rise to the vorticity and gravitational waves. 
@@
 
+The PMF power spectrum template is computed by a modified code CMBACT\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} with parameters $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_s$=-2.9 and $a_{\nu}/a_{\rm{PMF}}$=$10^9$.
 We can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:

### 2015-11-10 pmf.tex
intro

@@
 
+Measurements of the cosmic microwave background (CMB) temperature anisotropy have provided some of the most powerful tests of cosmology. 
+With a number of experiments beginning to measure  ``B-modes" in CMB polarization for the first time \citep{XXXX}, we are entering a new era for CMB observations. 
+Precision measurements of cosmic microwave background (CMB) polarization promise new tests of the standard cosmological model. 
+The best known of these tests are the searches for inflationary gravitational waves in B-modes at large angular scales \citep{XXX} and plans to measure the sum of the neutrino masses through the lensing B-modes on small angular scales \citep{XXX}.
+
+CMB B-mode measurements will constrain more exotic models as well, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or a primordial magnetic field (PMF) \citep{kosowsky96, seshadri01}.
+In this work, we present new upper limits from current CMB polarization data on the possibility of a PMF or parity-violating physics. 
+Both effects lead to birefringence and the rotation of E-modes into B-modes. 
+By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
+We will therefor simply quote effective limits on a PMF.
+
+Parity-violating processes
+
+However, CMB polarization data are expected to improve constraints on extensions
+
+of precision measurements of CMB polarization. 
+CMB polarization opens up
+
+we are beginning a new era of precision measurements of CMB polarization.
+
+These measurements are now being extended to CMB polarization
+
+one of the main pillars of the standard cosmolog
 Precision measurements of cosmic microwave background (CMB) polarization open up new tests for extensions to the  standard cosmological model. 
-One such extension would be the existence of a primordial magnetic field (PMF).
+Such extensions include the
 
@@
 First, we include TE and EE spectrum measurements\citep{crites15} for $\ell \in [500,3000]$ and BB bandpowers covering $\ell \in [500,2000]$ \citep{keisler15} from SPTpol. 
-We also add the BB bandpowers from \pb{} that cover the multipoles from 500 to 2500 \citep{pb-bb15}. 
+We also add the BB bandpowers from \pb{} that cover the multipoles from 500 to 2500 \citep{polarbear14b}. 
 Both the \sptpol{} and \pb{} bandpowers primary constrain the vector mode of the PMF given the angular scales measured. 
-Finally, we include the latest BICEP2 and Keck Array  joint analysis \citep{bicepkeck}. 
+Finally, we include the latest BICEP2 and Keck Array  joint analysis \citep{bicepkeck15}. 
 This latter dataset also places limits on the tensor mode of the PMF due to its coverage of lower multipoles. 
@@
 
-The PMF power spectrum template is computed by a modified code CMBACT\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} with parameters $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_s$=-2.9 and $a_{\nu}/a_{\rm{PMF}}$=$10^9$.
+The PMF power spectrum template is computed by a modified code CMBACT\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99} with parameters $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_s$=-2.9 and $a_{\nu}/a_{\rm{PMF}}$=$10^9$.
 We can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:

### 2015-11-12 pmf.tex
summary of later chains

@@
 
-\begin{table*}[htb]
+\begin{table*}[h]
 \begin{center}
@@
 
+\begin{table*}[h]
+\begin{center}
+\caption{\label{tab:param_all} All parameter constraints}
+\tiny
+\begin{tabular}{l || c c c c c c c | c}
+Chain & $\Omega_b h^2$  & $\Omega_c h^2$  & $\theta$  & $\tau$  & logA  & $n_s$  & $A_{lens}$  & $A_{pmf}$ \\
+lcdm\_alens\_all\_bk14 & $ 0.02240\pm  0.00025$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00045$ & $ 0.065\pm  0.017$ & $ 3.058\pm  0.030$ & $ 0.9696\pm  0.0060$ & $ 1.131 \pm  0.061$ & $< 0.27$ \\
+lcdm\_alens\_all\_bk14\_tensor & $ 0.02243\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04110\pm  0.00047$ & $ 0.066\pm  0.017$ & $ 3.060\pm  0.030$ & $ 0.9704\pm  0.0062$ & $ 1.142 \pm  0.060$ & $< 0.29$ \\
+lcdm\_alens\_all\_bk14\_vector & $ 0.02240\pm  0.00025$ & $ 0.1181\pm  0.0019$ & $ 1.04107\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.029$ & $ 0.9687\pm  0.0061$ & $ 1.134 \pm  0.061$ & $< 0.68$ \\
+lcdm\_alens\_nopmf\_all\_bk14 & $ 0.02244\pm  0.00025$ & $ 0.1179\pm  0.0020$ & $ 1.04109\pm  0.00046$ & $ 0.066\pm  0.016$ & $ 3.061\pm  0.029$ & $ 0.9700\pm  0.0060$ & $ 1.145 \pm  0.061$ & $< 0.00$ \\
+lcdm\_alens\_planck\_bk14 & $ 0.02256\pm  0.00027$ & $ 0.1174\pm  0.0020$ & $ 1.04120\pm  0.00048$ & $ 0.069\pm  0.017$ & $ 3.068\pm  0.030$ & $ 0.9723\pm  0.0062$ & $ 1.188 \pm  0.066$ & $< 0.28$ \\
+lcdm\_alens\_planck\_bk14\_tensor & $ 0.02257\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9727\pm  0.0060$ & $ 1.186 \pm  0.065$ & $< 0.29$ \\
+lcdm\_alens\_planck\_bk14\_vector & $ 0.02241\pm  0.00029$ & $ 0.1180\pm  0.0021$ & $ 1.04114\pm  0.00048$ & $ 0.065\pm  0.017$ & $ 3.058\pm  0.030$ & $ 0.9670\pm  0.0074$ & $ 1.149 \pm  0.075$ & $< 4.64$ \\
+lcdm\_all\_bk14 & $ 0.02223\pm  0.00021$ & $ 0.1182\pm  0.0018$ & $ 1.04113\pm  0.00049$ & $ 0.074\pm  0.014$ & $ 3.074\pm  0.024$ & $ 0.9686\pm  0.0055$ & $ 0.000 \pm  0.000$ & $< 0.35$ \\
+lcdm\_all\_bk14\_tensor & $ 0.02220\pm  0.00024$ & $ 0.1186\pm  0.0019$ & $ 1.04100\pm  0.00047$ & $ 0.067\pm  0.016$ & $ 3.063\pm  0.029$ & $ 0.9672\pm  0.0057$ & $ 0.000 \pm  0.000$ & $< 0.31$ \\
+lcdm\_all\_bk14\_vector & $ 0.02215\pm  0.00022$ & $ 0.1188\pm  0.0020$ & $ 1.04088\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.028$ & $ 0.9653\pm  0.0055$ & $ 0.000 \pm  0.000$ & $< 0.83$ \\
+lcdm\_r\_alens\_all\_bk14 & $ 0.02242\pm  0.00025$ & $ 0.1175\pm  0.0021$ & $ 1.04111\pm  0.00048$ & $ 0.068\pm  0.018$ & $ 3.063\pm  0.032$ & $ 0.9710\pm  0.0063$ & $ 1.133 \pm  0.062$ & $< 0.24$ \\
+\end{tabular}
+\tablecomments{ 
+Summary of results (will be trimmed for paper). 
+} \normalsize
+\end{center}
+\end{table*}
+
 \section{Forecasts}

### 2015-11-13 pmf.tex
ii

@@
 We present new limits on the amplitude of any primordial magnetic field (PMF) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce six-fold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 2.0\tbd{XX}$ from Planck alone to $\apmf < 0.33$ for the combined dataset at 95\% CL. 
+We reduce six-fold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.30$ for the combined dataset at 95\% CL. 
 Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
@@
 
-Parity-violating processes
+Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
+There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
+High energy $\gamma$-rays can interact with IR-optical photons and produce electron-positron pairs. 
+These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
+Intergalactic magnetic fields could explain this by deflecting the particles.
 
-However, CMB polarization data are expected to improve constraints on extensions
-
-of precision measurements of CMB polarization. 
-CMB polarization opens up
-
-we are beginning a new era of precision measurements of CMB polarization.
-
-These measurements are now being extended to CMB polarization
-
-one of the main pillars of the standard cosmolog
-Precision measurements of cosmic microwave background (CMB) polarization open up new tests for extensions to the  standard cosmological model. 
-Such extensions include the
+recent results
 

### 2015-11-13 pmf.tex
i

@@
 \newcommand{\lcdm}{\ensuremath{\Lambda}CDM}
+\newcommand{\fermilat}{\textit{Fermi}-LAT}
 
@@
 There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
-High energy $\gamma$-rays can interact with IR-optical photons and produce electron-positron pairs. 
+High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
 These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
-Intergalactic magnetic fields could explain this by deflecting the particles.
+Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
+If due to intergalactic magnetic fields, the GeV results set lower limits on the magnetic field strength of $10^{-9} - 10^{-6}$.\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
+
+The mechanism to create large-scale magnetic fields, especially in intergalactic space, remains unclear. 
+One popular proposal is that the observed fields are the product of primordial magnetic fields, which are predicted by several theories of the early Universe \citep[e.g.,][]{turner88, grasso98,ichiki06}.
+Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed fields into the stronger fields observed today. 
+Of course, this amplification process may have a different initial seed; other ideas include AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
+However, this possibility opens up the intriguing idea that observations of large-scale magnetic fields may offer insights into the physics of the very early Universe.
 
@@
 We therefor importance sample the chains to generate a flat prior on \bpmf. 
-We find a 95\% limit of $\bpmf < XX$\,nG for \planck{} alone, consistent with \citep{planckpmf} with $n$ held fixed as we've done. 
+We find a 95\% limit of $\bpmf < XX$\,nG for \planck{} alone, consistent with \citep{planck15-19} with $n$ held fixed as we've done. 
 This is reduced to $\bpmf < XX$\,nG for the combined dataset.

### 2015-11-13 pmf.tex
intro v1

@@
 Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
-If due to intergalactic magnetic fields, the GeV results set lower limits on the magnetic field strength of $10^{-9} - 10^{-6}$.\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
+If due to intergalactic magnetic fields, the GeV results set lower limits on the magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
 
@@
 
-recent results
+Primordial magnetic fields would have observational consequences for Big Bang nucleosynthesis \citep[e..,][]{kahniashvili10}, large scale structure \citep[e.g.,][]{battaner97}, the black body spectrum of the CMB \citep[e.g.,][]{kunze14}, as well as the CMB anisotropy.
+The CMB anisotropies have yielded some of the strongest constraints on PMFs and are the focus of this work.
+There have been two recent results of note. 
+\citet{planck15-19} have used the \planck{} 2015 release of temperature and polarization data to set limits on a variety of PMF models. 
+With the CMB power spectrum data that will be the focus of this paper, \citet{planck15-19} find 95\% CL upper limits ranging from $\bpmf < 5.6$\,nG to $<0.7$\,nG depending on the exact model. 
+The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{pb}. 
+The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < \tbd{4.0}$\,nG. 
+Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{}.
+In this paper, we will combine the data from all four experiments to determine simple limits on the PMF, and then examine Fisher matrix forecasts on PMF models from the stage-III and stage-IV CMB experiments being built or designed right now.
 

### 2016-10-20 pmf.tex
a

@@
 
+The sensitivity of CMB experiments is increasing rapidly due to exponentially growing detector counts
+\citet{s4sciencebook} thus defines four stages of CMB experiments. 
+The current experiments (i.e.~the ones used for PMF constraints in the last section) are classified as Stage II experiments. 
+Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{spt3g,simonsarray,advactpol} have approximately ten times more detectors, and generically will start collecting data in 2017 and finish in 2020-21.
+In this section, we forecast the expected constraints from the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
+Finally, CMB stage IV is a planned experiment  with another order of magnitude expansion in detector counts that would (ideally) begin taking data in the early 2020s.
+We examine the likely PMF constraints from such an experiment, and consider which aspects of experimental or survey design are important to realizing these constraints.
+
+\subsection{Fiducial survey parameters}
+
+\subsection{Stage III forecasts}
+
+\subsection{Stage IV forecasts}
+
+\subsection{Survey considerations for Stage IV}
+
 \section{Conclusions}

### 2016-10-20 pmf.tex
a

@@
 \newcommand{\lcdm}{\ensuremath{\Lambda}CDM}
+\newcommand{\nrun}{\ensuremath{n_{\rm run}}}
+\newcommand{\neff}{\ensuremath{N_{\rm eff}}}
+\newcommand{\mnu}{\ensuremath{\sum m|\nu}}
 \newcommand{\fermilat}{\textit{Fermi}-LAT}
@@
 
-\subsection{Fiducial survey parameters}
+\subsection{Methods and Experimental Parameters}
+
+We use Fisher matrices to forecast the constraints on PMFs possible from each generation of experiment. 
+Fisher matrices make it easy to combine different experiments and forecast the final parameter constraints \citep{fisher}. 
+According to the Cramer-Rao bound, the Fisher information is the lower bound on the uncertainty
+
+We include two external datasets in all forecasts. 
+The first are the expected measurements of the  TT, TE and EE spectra from the \planck{} satellite. 
+We include \planck{} TT information in the multipole range $2\le \ell \le 3000$. 
+Due to the importance of galactic foreground removal at large scales in polarization, we only use TE and EE information starting from $\ell = 30$. 
+A prior on the optical depth of 0.005 is added to account for the expected optical depth constraint from the missing multipoles. 
+Second, we include a 1\% external measurement of the Hubble constant, such as would be expected from the Taipan experiment \citep{taipan}.
+
+One concern with combining Fisher matrices from different experiments is double-counting modes due to overlapping sky coverage. 
+We sidestep this issue for the TT or TE spectra, by only using the \planck{} measurements. 
+We do not expect the future experiments to substantially improve upon \planck{} in these spectra. 
+We throw away \planck{} EE data in the overlap region by appropriately increasing the forecast \planck{} EE uncertainties. 
+The exact increase depends on the assumed stage III or IV survey area.
+We do not include \planck{} BB information in the forecasts. 
+We ignore overlaps between the stage III or IV experiments, with the note that the overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small.
+
+\begin{table*}[h]
+\begin{center}
+\caption{\label{tab:experiments} Assumed survey parameters}
+\small
+\begin{tabular}{l || c c c c c }
+Experiment & Sky coverage & Polarized Noise level  & 1/f knee & Beam FWHM \\
+& &($\mu$K-arcmin)&&(arcmin.)\\
+\hline
+Stage III: & & & & \\
+
+~~~~SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
+~~~~Simons Array & 36\% & 9.5 & 200 & 3.5 \\ 
+\\
+%\hline
+CMB Stage IV & 55\% & 1.3 & 100 & 4.0 \\
+\end{tabular}
+\tablecomments{ 
+Key numbers about the planned stage III and IV experiments. 
+The sky coverage percentages are after galactic cuts. 
+Unless otherwise noted,  the Fisher matrix forecasts in this work use these numbers. 
+All forecasts also include beam and calibration uncertainty as noted in the text. 
+} \normalsize
+\end{center}
+\end{table*}
+
+We list the assumed survey areas, noise levels and beam sizes for each experiment in Table~\ref{tab:experiments}. 
+We also assume a 5\% uncertainty on the beam FWHM and a 1\% power calibration uncertainty; we have tested relaxing or tightening the beam and calibration uncertainty and find these calibration terms have a negligible impact on the PMF constraints.
+
+We consider the constraints on PMFs in two cosmologies. 
+In all cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
+Generally, we report constraints on the PMFs as one of several extensions to LCDM:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
+However, in order to illustrate the degree to which parameter degeneracies are limiting the inferred constraints,  we also show constraints from an aggressive model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
 
@@
 
+The experiments that will begin taking data next year will dramatically improve constraints on the PMF power. 
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$, slightly worse than indicated by the upper limits found with the full \planck{} likelihood. 
+The uncertainty falls nearly 400-fold by adding the two stage III experiments in this simplified model. 
+Including all eleven parameters marginally weakens the \planck+\ho{} constraints on \apmf{} by 23\%. 
+Parameter degeneracies degrade the Stage III constraint by a substantial factor (x2.5). 
+Still in this 11-parameter model, the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$180 to  $\sigma(\apmf)=0.0031$. 
+We can expect substantially tighter constraints on PMFs by the end of the decade.
+
 \subsection{Stage IV forecasts}
+
+The primary motivation behind the proposed CMB stage IV experiment is to search for inflationary gravitational waves and neutrino masses, however, the experiment should also enable extremely sensitive searches for PMFs.
+
+ extremely powerful
 

### 2016-10-21 pmf.tex
a

@@
 \newcommand{\neff}{\ensuremath{N_{\rm eff}}}
+\newcommand{\ho}{H\ensuremath{_0}}
 \newcommand{\mnu}{\ensuremath{\sum m|\nu}}
@@
 
+Given that CMB-S4 is still being designed, it is worthwhile to consider how the design decisions might influence the final PMF constraints. 
+We look at four aspects of the experiment design: the telescope size or beam FWHM, the low-$\ell$ noise performance (1/f knee), and the choice of survey area, and how well the beam size and calibration must be known.
+Of these four, we find that the low-$\ell$ noise performance and survey area are important to searches for PMFs
+
+Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefor always improve the PMF constraints. 
+However, larger telescopes are also more expensive to build which means at fixed cost, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
+We find the gains due to resolution at fixed mapping speed to be negligible: a beam size of FWHM=1$^\prime$ yields only a 1\% better limit than a FWHM of 10$^\prime$. 
+This illustrates how important the large angular scales are to the PMF limits. 
+We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin for a FWHM of 1$^\prime$.
+In this quasi-cost-neutral setup, there is a strong preference to go for more detectors over better angular resolution: the uncertainty was a factor of 2.5 times smaller in the coarse case over the FWHM=1$^\prime$ case.
+Raw sensitivity is more important than angular resolution to an experiment's ability to study PMFs.
+
+However, adding more detectors does 
+Of course,
+
+If you don't require cost-
+
+We assume the beam i
+
+ the beam FWHM (i.e. telescope diameter),
+
 \section{Conclusions}

### 2016-10-21 pmf.tex
a

@@
 \newcommand{\ho}{H\ensuremath{_0}}
-\newcommand{\mnu}{\ensuremath{\sum m|\nu}}
+\newcommand{\mnu}{\ensuremath{\sum m_\nu}}
+\newcommand{\ukarcmin}{\ensuremath{\mu}K-arcmin}
+\newcommand{\lknee}{\ensuremath{\ell_{\rm knee}}}
 \newcommand{\fermilat}{\textit{Fermi}-LAT}
@@
 This illustrates how important the large angular scales are to the PMF limits. 
-We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin for a FWHM of 1$^\prime$.
+We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin{} for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin{} for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin{} for a FWHM of 1$^\prime$.
 In this quasi-cost-neutral setup, there is a strong preference to go for more detectors over better angular resolution: the uncertainty was a factor of 2.5 times smaller in the coarse case over the FWHM=1$^\prime$ case.
@@
 
-However, adding more detectors does 
-Of course,
-
-If you don't require cost-
-
-We assume the beam i
-
- the beam FWHM (i.e. telescope diameter),
+Next we turn to the recovery of large angular scales, and the noise performance at low frequencies. 
+We measure the importance by shifting the 1/f knee of the map-space noise in the range $\ell = [50,400]$. 
+Effectively, we are multiplying the noise power, $N_\ell$, which is a constant for white noise,  by a function of angular multipole:
+\be
+f(\ell) = 1 + \left(\frac{\ell_{\rm knee}}{\ell}\right)^{8/3}. 
+\ee 
+The exponent, 8/3, was selected based on a Kolmogorov spectrum of turbulence within a thin plane \citep{lay00}. %lay & halverson 2000. 
+Note that this knob  serves as a placeholder for several effects, including a signal-to-noise hit due to galactic foregrounds or the methods used to clean these foregrounds, atmospheric noise, or actual instrumental 1/f noise.
+We find that increasing \lknee{} from 50 to 100, 200 or 400 expands the uncertainty on \apmf{} by factors of 1.2, 2.1 and 6.3 respectively. 
+Recovering large angular scales is clearly very important to PMF searches. 
+This is consistent with the study of telescope size in the last paragraph - which found extending to smaller angular scales only helped slightly. 
+It is also consistent with the current upper limits, which are dominated by the BICEP2/Keck Array data at low-$\ell$. 
+Fortunately, these large angular scales are also crucial to searches for inflationary gravitational waves, so the needs of the PMF search are well-aligned with one of the key science drivers for CMB-S4.
 

### 2016-10-21 pmf.tex
a

@@
 
+Finally, we consider if searches for PMFs introduce new requirements on the knowledge to which the instrumental beam or overall calibration of the experiments must be known. 
+We parametrize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
+We find negligible ($<$\,1\%) shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
+The PMF constraints are insensitive to beam and calibration uncertainty.
+
 \section{Conclusions}

### 2016-10-21 pmf.tex
a

@@
 
+A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
+As shown in  Fig.~\ref{fig:area}, it is better to go as wide as possible. 
+A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
+With that said, the PMF constraints improve rapidly with sky area up to XX \sqdeg, and improve by another XX\% up to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
+
 Finally, we consider if searches for PMFs introduce new requirements on the knowledge to which the instrumental beam or overall calibration of the experiments must be known. 

### 2016-10-24 pmf.tex
a

@@
 
-We present new limits on the amplitude of any primordial magnetic field (PMF) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce six-fold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.30$ for the combined dataset at 95\% CL. 
-Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
-We also consider future limits from stage III CMB experiments (like \sptnew{},  \advactpol, or the \simons) and a stage IV concept. 
-Stage III experiments will reduce the current limit by an additional factor of \tbd{XX}; this will become a factor of \tbd{XX} for stage IV. 
-\tbd{maybe:} The constraints from a stage IV experiment have the potential to rule out much of the parameter space for PMFs.
-\tbd{really if could rule out them as explanation for galaxy fields...
-is there a lower bound for them to be useful?}
+We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
+We reduce by a factor of 2.5 the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.30$ for the combined dataset at 95\% CL. 
+%Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
+We also forecast the expected future limits from stage III CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB stage IV experiment. 
+Future CMB experiments should dramatically reduce the current uncertainties, by two orders of magnitude for stage III experiments and three orders of magnitude for stage IV. 
+The constraints from a stage IV experiment have the potential to rule out much of the parameter space for PMFs.
 
@@
 Measurements of the cosmic microwave background (CMB) temperature anisotropy have provided some of the most powerful tests of cosmology. 
-With a number of experiments beginning to measure  ``B-modes" in CMB polarization for the first time \citep{XXXX}, we are entering a new era for CMB observations. 
-Precision measurements of cosmic microwave background (CMB) polarization promise new tests of the standard cosmological model. 
+We are now entering a new era as experiments begin to measure  polarized ``B-modes" in the CMB for the first time \citep{XXXX}. 
+Precision measurements of CMB polarization promise new tests of the standard cosmological model. 
 The best known of these tests are the searches for inflationary gravitational waves in B-modes at large angular scales \citep{XXX} and plans to measure the sum of the neutrino masses through the lensing B-modes on small angular scales \citep{XXX}.
 
-CMB B-mode measurements will constrain more exotic models as well, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or a primordial magnetic field (PMF) \citep{kosowsky96, seshadri01}.
-In this work, we present new upper limits from current CMB polarization data on the possibility of a PMF or parity-violating physics. 
-Both effects lead to birefringence and the rotation of E-modes into B-modes. 
+CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or a primordial magnetic field (PMF) \citep{kosowsky96, seshadri01}.
+Both effects lead to cosmic birefringence and the rotation of E-modes into B-modes. 
 By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
 We will therefor simply quote effective limits on a PMF. 
+In this work, we present new upper limits from current CMB polarization data on the possibility of a PMF or parity-violating physics.
 
-Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
+Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
 There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
@@
 Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
-If due to intergalactic magnetic fields, the GeV results set lower limits on the magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
+If due to intergalactic magnetic fields, the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
 
@@
 Of course, this amplification process may have a different initial seed; other ideas include AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
-However, this possibility opens up the intriguing idea that observations of large-scale magnetic fields may offer insights into the physics of the very early Universe.
+However, the possibility of PMFs opens up the intriguing idea that observations of large-scale magnetic fields may offer insights into the physics of the very early Universe.
 
@@
 
-We use  Markov chain Monte Carlo (MCMC) methods to study constraints on the primordial magnetic field. 
+We use  Markov chain Monte Carlo (MCMC) methods to study constraints on PMFs. 
 In this section, we first describe the CMB temperature and polarization anisotropy data used, and then discuss the MCMC implementation.
@@
 We do not however require these consistency between these foreground models since the data don't have identical flux cuts and so on. 
-In the case of an upper limit this treatment is conservative since weaker foreground constraints or residual point source power would only add power and weaken the limit on the PMF.
+In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength.
 
@@
 
-Unless noted, we assume the six parameter spatially flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF. 
+For the real data, unless noted, we assume the six parameter spatially flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF.
 We adopt flat priors on all parameters. 
@@
 
-The density and stress perturbations introduced by PMFs give rise to the vorticity and gravitational waves. 
-The CMB anisotropies created in this photon-baryon plasma inherit two characteristic properties, i.e., vector and tensor modes which can be determined by modified Boltzman equations involving sources from PMFs.
-The PMF filed is assumed to be Gaussian and its power spectrum is given by a power law $Ak^{n_s}$. 
-Here $n_s$ is the spectral index of PMF and $A$ is its amplitude. 
-The rms of the PMF energy can be quantified over a length 1\rm{Mpc} and $B_{\rm{1Mpc}}$ equivalently determines the PMF amplitude. 
-The PMF stress anisotropies can be compensated by neutrinos if neutrinos decoupled too early so it is also important to consider when the PMF was generated and another parameter $\beta=\ln(a_{\nu}/a_{\rm{PMF}})$ is usually adopted.
+The density and stress perturbations introduced by PMFs give rise to vorticity and gravitational waves in the early photon-baryon  plasma, i.e. vector and tensor modes. 
+The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
+We use the CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}  to do this calculation. 
+The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_b k^{n_b}$. 
+Here $n_b$ is the spectral index of PMF and $A_b$ is its amplitude. 
+We can translate the amplitude, $A_b$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
+Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
+The timing is typically parametrized by the ratio of the scale factors at neutrino decoupling and PMF generation, $a_{\nu}/a_{\rm{PMF}}$.
 
-The PMF power spectrum template is computed by a modified code CMBACT\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99} with parameters $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_s$=-2.9 and $a_{\nu}/a_{\rm{PMF}}$=$10^9$.
+Given that we are still in the era of upper limits,  we do not explore the full 3-dimensional PMF parameter space in this work. 
+Instead, we use CMBACT to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$. 
+We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
 We can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:
@@
 
-The sensitivity of CMB experiments is increasing rapidly due to exponentially growing detector counts
+The sensitivity of CMB experiments is increasing rapidly due to the exponential growth in detector counts
 \citet{s4sciencebook} thus defines four stages of CMB experiments. 
@@
 In this section, we forecast the expected constraints from the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
-Finally, CMB stage IV is a planned experiment  with another order of magnitude expansion in detector counts that would (ideally) begin taking data in the early 2020s.
-We examine the likely PMF constraints from such an experiment, and consider which aspects of experimental or survey design are important to realizing these constraints.
+There is also a proposal to build a stage IV experiment, CMB-S4,  that would increase the detector counts by another order of magnitude and hopefully begin taking data in the early 2020s.
+We examine the likely PMF constraints from CMB-S4, and consider which aspects of experimental or survey design are important to maximize the recovered information on PMFs.
 
@@
 Fisher matrices make it easy to combine different experiments and forecast the final parameter constraints \citep{fisher}. 
-According to the Cramer-Rao bound, the Fisher information is the lower bound on the uncertainty
+According to the Cramer-Rao bound, the Fisher information provides a lower bound on the uncertainty.
 
 We include two external datasets in all forecasts. 
-The first are the expected measurements of the  TT, TE and EE spectra from the \planck{} satellite. 
+The first dataset is the expected measurements of the  TT, TE and EE spectra from the \planck{} satellite. 
 We include \planck{} TT information in the multipole range $2\le \ell \le 3000$. 
@@
 We sidestep this issue for the TT or TE spectra, by only using the \planck{} measurements. 
-We do not expect the future experiments to substantially improve upon \planck{} in these spectra. 
-We throw away \planck{} EE data in the overlap region by appropriately increasing the forecast \planck{} EE uncertainties. 
+We do not expect the future experiments to substantially improve upon \planck{} in these spectra which are already cosmic variance limited out to fairly high multipoles. 
+We throw away \planck{} EE data in the overlap region by appropriately increasing the forecasted \planck{} EE uncertainties. 
 The exact increase depends on the assumed stage III or IV survey area.
 We do not include \planck{} BB information in the forecasts. 
-We ignore overlaps between the stage III or IV experiments, with the note that the overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small.
+We ignore overlaps between the stage III  with the note that the overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small.
+We do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints. 
+With these measures, no modes should be double-counted in this analysis.
 

### 2016-10-25 pmf.tex
a

@@
 We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce by a factor of 2.5 the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.30$ for the combined dataset at 95\% CL. 
+We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.68$ from Planck alone to $\apmf < 0.33$ for the combined dataset at 95\% CL. 
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
@@
 
+As a sanity check, we look at the Fisher matrix forecasts for Planck alone as well in both of these cases. 
+For both chains,  we look at the sigma in MCMC with \apmf{} allowed to go negative. 
+While a negative \apmf{} is unphysical, this insulates the analysis against the data preferring negative values, and thereby producing tighter limits. 
+We find for \lcdm{}  + \apmf{}: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
+We find for the 11-parameter model: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
+This degree of consistency is reasonable. \tbd{}
+
 \subsection{Stage III forecasts}
@@
 The experiments that will begin taking data next year will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$, slightly worse than indicated by the upper limits found with the full \planck{} likelihood. 
-The uncertainty falls nearly 400-fold by adding the two stage III experiments in this simplified model. 
-Including all eleven parameters marginally weakens the \planck+\ho{} constraints on \apmf{} by 23\%. 
-Parameter degeneracies degrade the Stage III constraint by a substantial factor (x2.5). 
-Still in this 11-parameter model, the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$180 to  $\sigma(\apmf)=0.0031$. 
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$ as noted before.  
+The uncertainty is forecast to fall nearly 400-fold by adding the two stage III experiments in this simplified model to $\sigma(\apmf)=0.0012$. 
+Including all eleven parameters marginally weakens the \planck+\ho{} constraints on \apmf{} by 23\%, and the stage III constraint by a substantial factor of 2.5. 
+Even so within this 11-parameter model, the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,180 to  $\sigma(\apmf)=0.0031$. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
 The primary motivation behind the proposed CMB stage IV experiment is to search for inflationary gravitational waves and neutrino masses, however, the experiment should also enable extremely sensitive searches for PMFs.
-
- extremely powerful
+We begin by making forecasts for the fiducial CMB-S4 configuration as laid out in Table~\ref{tab:experiments}.
 

### 2016-10-26 pmf.tex
a

@@
 %\documentclass[12pt,preprint]{aastex}
+\graphicspath{{figures/}}
+\DeclareGraphicsExtensions{.jpg,.pdf,.png,.eps,.ps}
 
@@
 The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{pb}. 
-The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < \tbd{4.0}$\,nG. 
+The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < 3.9$\,nG. 
 Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{}.
@@
 
-In addition to the \planck{} data, we use all recent CMB polarization measurements that are publicly available. 
+In addition to the \planck{} data, we use a number of recent CMB polarization measurements. 
 First, we include TE and EE spectrum measurements\citep{crites15} for $\ell \in [500,3000]$ and BB bandpowers covering $\ell \in [500,2000]$ \citep{keisler15} from SPTpol. 
@@
 This latter dataset also places limits on the tensor mode of the PMF due to its coverage of lower multipoles. 
+During the writing of this work, ACTpol polarization power spectra became available \citep{actpol}. 
+We have not included the ACTPol bandpowers; we do not expect adding them to significantly change the PMF limits based on a visual comparison of the current BB bandpowers from different experiments.
 In all chains, we marginalize over the recommended foreground models for each data set. 
@@
 Instead, we use CMBACT to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$. 
+This template is plotted against the current measurements of the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
 We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
@@
 However, if a PMF is detected, this same steep scaling would allow excellent constraints on its properties.
+
+\begin{figure*}[htb]\centering
+\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_knee.pdf}
+  \caption[CMB polarization from PMFs]{
+  Currently dummy plot.
+  Will be plot of BB bandpowers and PMF template.
+      \label{fig:pmf-bb}
+  }
+\end{figure*}
 
@@
 \begin{center}
-\caption{\label{tab:param_all} All parameter constraints}
+\caption{\label{tab:param_all2} All parameter constraints2}
 \tiny
@@
 
+\begin{figure}[htb]\centering
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_knee.pdf}
+  \caption[Map knee dependence]{
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected as the low-frequency map noise decreases.  
+  In particular, achieving a map 1/f knee frequency at or below $\ell = 200$ substantially improves the potential power of CMB-S4 PMF searches. 
+  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
+  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
+  The x-axis is the map noise knee (see eqn.~\ref{eqn:knee}) in angular multipoles $\ell$. 
+  As we expect, reducing low-frequency noise would lead to better PMF constraints. 
+    \label{fig:knee}
+  }
+\end{figure}
+
 Next we turn to the recovery of large angular scales, and the noise performance at low frequencies. 
@@
 Effectively, we are multiplying the noise power, $N_\ell$, which is a constant for white noise,  by a function of angular multipole:
-\be
+\be \label{eqn:knee}
 f(\ell) = 1 + \left(\frac{\ell_{\rm knee}}{\ell}\right)^{8/3}.
@@
 Note that this knob  serves as a placeholder for several effects, including a signal-to-noise hit due to galactic foregrounds or the methods used to clean these foregrounds, atmospheric noise, or actual instrumental 1/f noise.
-We find that increasing \lknee{} from 50 to 100, 200 or 400 expands the uncertainty on \apmf{} by factors of 1.2, 2.1 and 6.3 respectively. 
-Recovering large angular scales is clearly very important to PMF searches. 
+We find the results to be somewhat more sensitive to the 1/f knee in the simple \lcdm{}+\apmf{} model, where dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 6.3.
+However, the knee frequency is still important in the more conservative 11-parameter model, where the same shift reduces the uncertainties by a factor of 2.7. 
+In both cases, as can be seen in Fig.~\ref{fig:knee}, the information loss really accelerates when the 1/f knee goes above $\ell \simeq 200$. 
+For the same 11-parameter model, bringing \lknee{} to 200 from 400 yields a factor of 2 (only modestly worse than the 2.7x improvement for \lknee=50). 
+Recovering large angular scales is clearly important to PMF searches. 
 This is consistent with the study of telescope size in the last paragraph - which found extending to smaller angular scales only helped slightly. 
@@
 
+\begin{figure}[htb]\centering
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
+  \caption[Area dependence]{
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
+  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
+  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
+  In both cases, better limits on PMFs will be achieved with wider surveys.
+    \label{fig:area}
+  }
+\end{figure}
 A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
@@
 A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
-With that said, the PMF constraints improve rapidly with sky area up to XX \sqdeg, and improve by another XX\% up to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
+With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and improve by another factor of 1.4-1.5 by going to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
 
 Finally, we consider if searches for PMFs introduce new requirements on the knowledge to which the instrumental beam or overall calibration of the experiments must be known. 
-We parametrize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
-We find negligible ($<$\,1\%) shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
+We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
+We find negligible, sub-percent shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
 The PMF constraints are insensitive to beam and calibration uncertainty.
@@
 
+In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB polarization data. 
+By adding \bicepkeck{}, \pb, and \sptpol to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < 0.68$ to $\apmf < 0.33$. 
+The biggest contributor to this improvement is the low-$\ell$ data from \bicepkeck{}.
+
+We have also shown that the next generation of experiments have the potential power to dramatically reduce these limits, and potentially detect PMFs for the first time. 
+The so-called stage III experiments, which should begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.0062$ even after marginalizing over a five-parameter extension to \lcdm.
+
+The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
+We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0008$, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.001$, i.e.~ a six-fold improvement over the forecasts for the stage III experiments and a 330-fold improvement over the current limits.
+These experiments will be very exciting probes of PMFs and other sources of cosmic birefringence.
+
 \bibliography{pmf}

### 2016-10-27 pmf.tex
a

@@
 \begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_knee.pdf}
+\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
+  \caption[Current measurements of CMB B-modes]{
+  Current measurements of CMB B-modes. \tbd{Caption to be updated}
+      \label{fig:pmf-experiments}
+  }
+\end{figure*}
+
+\begin{figure*}[htb]\centering
+\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
   \caption[CMB polarization from PMFs]{
-  Currently dummy plot.
-  Will be plot of BB bandpowers and PMF template.
+  The expected contributions to CMB B-modes. 
+  The red line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology. 
+  The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
+  The dashed purple line shows the PMF template used in this work, scaled to \apmf{} = 0.2. 
+  As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal. 
+  However PMFs also produce a vector component that peaks around $\ell \sim 1700$ and allows the discrimination between  the inflationary and PMF explanations. 
       \label{fig:pmf-bb}

### 2016-10-27 pmf.tex
a

@@
   \caption[Current measurements of CMB B-modes]{
-  Current measurements of CMB B-modes. \tbd{Caption to be updated}
+  Current measurements of CMB B-modes. 
+    The black line shows the expected B-mode power in the \planck{} best-fit \lcdm{} cosmology (with the tensor-to-scalar ratio, r set to 0.01). 
+    The B-mode measurements used for the limits in this work are denoted with filled circles; data not used has an open circle. 
+    The data sets are from POLARBEAR (black; \citet{polarbear}); ACTpol (dark green; \citet{actpol});  BICEP2/Keck Array (red; \citet{bicepkeck}); and SPTpol (purple; \citet{sptpol}). 
+      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments is expected to significantly increase the signal-to-noise on the B-mode power spectrum.
            \label{fig:pmf-experiments}

### 2016-10-27 pmf.tex
a

@@
 
+\acknowledgments
+
+We thank XXX for valuable feedback on the manuscript. 
+C. Reichardt is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 
+This research used resources of the National Energy Research Scientific Computing Center, which is supported by the Office of Science of the U.S.
+Department of Energy under Contract No.
+DE-AC02-05CH11231.
+We acknowledge the use of the Legacy Archive for Microwave Background Data Analysis (LAMBDA). Support for LAMBDA is provided by the NASA Office of Space Science.
+
 \bibliography{pmf}

### 2016-10-27 pmf.tex
a

@@
 Measurements of the cosmic microwave background (CMB) temperature anisotropy have provided some of the most powerful tests of cosmology. 
-We are now entering a new era as experiments begin to measure  polarized ``B-modes" in the CMB for the first time \citep{XXXX}. 
+We are now entering a new era as experiments begin to measure  polarized ``B-modes" in the CMB for the first time \citep{hanson13,polarbear14b,bicep2014a,naess14,keisler15,bicepkeck15,louis16}. 
 Precision measurements of CMB polarization promise new tests of the standard cosmological model. 
-The best known of these tests are the searches for inflationary gravitational waves in B-modes at large angular scales \citep{XXX} and plans to measure the sum of the neutrino masses through the lensing B-modes on small angular scales \citep{XXX}.
+The best known of these tests are the searches for inflationary gravitational waves in B-modes at large angular scales and plans to measure the sum of the neutrino masses through the lensing B-modes on small angular scales \citep[for a recent review see,][]{abazajian16}.
 
@@
 
-Primordial magnetic fields would have observational consequences for Big Bang nucleosynthesis \citep[e..,][]{kahniashvili10}, large scale structure \citep[e.g.,][]{battaner97}, the black body spectrum of the CMB \citep[e.g.,][]{kunze14}, as well as the CMB anisotropy.
+Primordial magnetic fields would have observational consequences for Big Bang nucleosynthesis \citep[e.g.,][]{kahniashvili10}, large scale structure \citep[e.g.,][]{battaner97}, ionization history of the Universe \citep{kunze15}, and the black body spectrum of the CMB \citep[e.g.,][]{kunze14},  as well as the CMB anisotropy.
 The CMB anisotropies have yielded some of the strongest constraints on PMFs and are the focus of this work.
@@
 With the CMB power spectrum data that will be the focus of this paper, \citet{planck15-19} find 95\% CL upper limits ranging from $\bpmf < 5.6$\,nG to $<0.7$\,nG depending on the exact model. 
-The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{pb}. 
+The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{polarbear14b}. 
 The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < 3.9$\,nG. 
-Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{}.
+Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{keisler15,bicepkeck15}.
 In this paper, we will combine the data from all four experiments to determine simple limits on the PMF, and then examine Fisher matrix forecasts on PMF models from the stage-III and stage-IV CMB experiments being built or designed right now.
@@
 This latter dataset also places limits on the tensor mode of the PMF due to its coverage of lower multipoles. 
-During the writing of this work, ACTpol polarization power spectra became available \citep{actpol}. 
-We have not included the ACTPol bandpowers; we do not expect adding them to significantly change the PMF limits based on a visual comparison of the current BB bandpowers from different experiments.
+During the writing of this work, ACTpol polarization power spectra became available \citep{naess14,louis16}. 
+We have not included them as the public likelihoods do not include the B-mode power spectrum; we do not expect adding the ACTpol bandpowers to significantly change the PMF limits based on a visual comparison of the current BB bandpowers from different experiments.
 In all chains, we marginalize over the recommended foreground models for each data set. 
@@
     The B-mode measurements used for the limits in this work are denoted with filled circles; data not used has an open circle. 
-    The data sets are from POLARBEAR (black; \citet{polarbear}); ACTpol (dark green; \citet{actpol});  BICEP2/Keck Array (red; \citet{bicepkeck}); and SPTpol (purple; \citet{sptpol}). 
+    The data sets are from POLARBEAR (black; \citet{polarbear14b}); ACTpol (dark green; \citet{naess14});  BICEP2/Keck Array (red; \citet{bicepkeck15}); and SPTpol (purple; \citet{keisler15}). 
       Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments is expected to significantly increase the signal-to-noise on the B-mode power spectrum.
@@
 The sensitivity of CMB experiments is increasing rapidly due to the exponential growth in detector counts
-\citet{s4sciencebook} thus defines four stages of CMB experiments. 
+\citet{abazajian16} thus defines four stages of CMB experiments. 
 The current experiments (i.e.~the ones used for PMF constraints in the last section) are classified as Stage II experiments. 
-Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{spt3g,simonsarray,advactpol} have approximately ten times more detectors, and generically will start collecting data in 2017 and finish in 2020-21.
+Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{benson14,suzuki16,henderson16} have approximately ten times more detectors, and generically will start collecting data in 2017 and finish in 2020-21.
 In this section, we forecast the expected constraints from the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
@@
 We use Fisher matrices to forecast the constraints on PMFs possible from each generation of experiment. 
-Fisher matrices make it easy to combine different experiments and forecast the final parameter constraints \citep{fisher}. 
-According to the Cramer-Rao bound, the Fisher information provides a lower bound on the uncertainty.
+Fisher matrices make it easy to combine different experiments and forecast the final parameter constraints. 
+However, for non-Gaussian likelihoods, there is the potential for Fisher matrix forecasts to significantly underestimate the true uncertainties \citep[see e.g.,][]{wolz12}.
 
@@
 A prior on the optical depth of 0.005 is added to account for the expected optical depth constraint from the missing multipoles. 
-Second, we include a 1\% external measurement of the Hubble constant, such as would be expected from the Taipan experiment \citep{taipan}.
+Second, we include a 1\% external measurement of the Hubble constant, such as would be expected from the Taipan experiment \citep{kuehn14}.
 

### 2016-10-28 pmf.tex
a

@@
 We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.68$ from Planck alone to $\apmf < 0.33$ for the combined dataset at 95\% CL. 
+We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.35$ for the combined dataset at 95\% CL. 
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
@@
 We find the addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement. 
-With Planck alone, the 95\% confidence upper limit is $\apmf <  0.68$ when $\alens$ is allowed to vary; with the ground-based experiments, this limit drops to $\apmf <  0.33$. 
-We test which datasets are important by adding single datasets to the \planck{} set, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  0.36$) and \sptpol{} ($\apmf <  0.42$) B-mode power spectrum measurements.
+With Planck alone, the 95\% confidence upper limit is $\apmf <  0.73$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  0.35$. 
+The limits are slightly better with \alens{} allowed to vary (as a value for \alens{} slightly above unity is preferred). 
+In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  0.68$, dropping to $\apmf <  0.27$ with the ground-based experiments. 
+We test which datasets are important by adding single datasets to the \planck{} set while allowing \alens{} to float, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  0.28$) and \sptpol{} ($\apmf <  0.42$) B-mode power spectrum measurements.
 The other datasets do not have a large impact on the observed limits.
@@
 Due to the scaling with the fourth power, an upper limit with a flat prior on \apmf{} would lead to an apparent `detection' of \bpmf. 
-We therefor importance sample the chains to generate a flat prior on \bpmf. 
-We find a 95\% limit of $\bpmf < XX$\,nG for \planck{} alone, consistent with \citep{planck15-19} with $n$ held fixed as we've done. 
-This is reduced to $\bpmf < XX$\,nG for the combined dataset.
+We therefore importance sample the chains to generate a flat prior on \bpmf. 
+We find a 95\% limit of $\bpmf < 1.97$\,nG for \planck{} alone, completely consistent with \citep{planck15-19} who found $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
+This is slightly reduced to $\bpmf < 1.85$\,nG for the combined dataset. 
+The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks about 1 sigma above zero, whereas the \planck{} only constraints peaks at zero.
 
-\begin{table*}[h]
+\begin{table}[tbh]
 \begin{center}
-\caption{\label{tab:param_all} All parameter constraints}
-\tiny
-\begin{tabular}{l || c c c c c c c | c}
-Chain & $\Omega_b h^2$  & $\Omega_c h^2$  & $\theta$  & $\tau$  & logA  & $n_s$  & $A_{lens}$  & $A_{pmf}$ \\
-lcdm\_alens\_all & $ 0.02240\pm  0.00026$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9696\pm  0.0062$ & $ 1.121 \pm  0.064$ & $< 0.33$ \\
-lcdm\_alens\_nopmf\_all & $ 0.02241\pm  0.00024$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.065\pm  0.016$ & $ 3.059\pm  0.029$ & $ 0.9694\pm  0.0062$ & $ 1.136 \pm  0.063$ & $< 0.00$ \\
-lcdm\_alens\_nopmf\_planck & $ 0.02256\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04121\pm  0.00048$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9721\pm  0.0063$ & $ 1.175 \pm  0.067$ & $< 0.00$ \\
-lcdm\_alens\_planckTT & $ 0.02252\pm  0.00031$ & $ 0.1174\pm  0.0027$ & $ 1.04122\pm  0.00053$ & $ 0.070\pm  0.050$ & $ 3.068\pm  0.098$ & $ 0.9713\pm  0.0080$ & $ 1.155 \pm  0.136$ & $< 1.34$ \\
-lcdm\_alens\_planckTT\_TEB & $ 0.02264\pm  0.00029$ & $ 0.1161\pm  0.0025$ & $ 1.04141\pm  0.00053$ & $ 0.055\pm  0.021$ & $ 3.036\pm  0.042$ & $ 0.9755\pm  0.0072$ & $ 1.241 \pm  0.104$ & $< 0.77$ \\
-lcdm\_alens\_planck & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00046$ & $ 0.068\pm  0.016$ & $ 3.065\pm  0.030$ & $ 0.9723\pm  0.0062$ & $ 1.171 \pm  0.070$ & $< 0.68$ \\
-lcdm\_alens\_planck\_bicep & $ 0.02255\pm  0.00026$ & $ 0.1174\pm  0.0020$ & $ 1.04120\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0063$ & $ 1.177 \pm  0.068$ & $< 0.36$ \\
-lcdm\_alens\_planck\_pb & $ 0.02255\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04119\pm  0.00046$ & $ 0.068\pm  0.017$ & $ 3.066\pm  0.031$ & $ 0.9725\pm  0.0064$ & $ 1.171 \pm  0.068$ & $< 0.63$ \\
-lcdm\_alens\_planck\_sptpolB & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0062$ & $ 1.159 \pm  0.067$ & $< 0.42$ \\
-lcdm\_alens\_planck\_sptpolE & $ 0.02239\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00048$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9698\pm  0.0061$ & $ 1.119 \pm  0.067$ & $< 0.73$ \\
-lcdm\_planck & $ 0.02225\pm  0.00023$ & $ 0.1184\pm  0.0020$ & $ 1.04102\pm  0.00047$ & $ 0.066\pm  0.017$ & $ 3.062\pm  0.030$ & $ 0.9682\pm  0.0060$ & $ 0.000 \pm  0.000$ & $< 0.73$ \\
-lcdm\_r\_alens\_all & $ 0.02240\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.029$ & $ 0.9702\pm  0.0062$ & $ 1.123 \pm  0.063$ & $< 0.27$ \\
+\caption{\label{tab:param_all} Parameter Constraints}
+\small
+\begin{tabular}{l | c c c }
+Model   & $A_{pmf}$ &$A_{lens}$&$r$\\
+\hline
+\lcdm{} + \apmf{} &  $< 0.35$ & - & - \\
+~~~+\alens{} & $< 0.27$ &$ 1.131 \pm  0.061$ &  -\\
+~~~+\alens{}+r&  $< 0.24$&$ 1.133 \pm  0.062$ & $<0.056$\\ 
 \end{tabular}
 \tablecomments{ 
-Summary of results (will be trimmed for paper). 
+In the minimal model, \lcdm{} + \apmf{}, current CMB power spectra data from \planck, POLARBEAR, SPTpol, and \bicepkeck{} place a 95\% CL upper limit on the PMF power of $\apmf < 0.35$. 
+This limit actually tightens slightly if tensor modes are allowed (r), or the amount of lensing is allowed to vary. 
+In the case of r, the tightening is because the observed power at large angular scales is now split between PMFs or inflationary gravitational waves. 
+In the case of \alens, it is because the preferred value for \alens{} is modestly above the predicted value of unity. 
+Recall that the the PMF template is normalized to unity for \bpmf{} = 2.5\,nG.
 } \normalsize
 \end{center}
-\end{table*}
-
-\begin{table*}[h]
-\begin{center}
-\caption{\label{tab:param_all2} All parameter constraints2}
-\tiny
-\begin{tabular}{l || c c c c c c c | c}
-Chain & $\Omega_b h^2$  & $\Omega_c h^2$  & $\theta$  & $\tau$  & logA  & $n_s$  & $A_{lens}$  & $A_{pmf}$ \\
-lcdm\_alens\_all\_bk14 & $ 0.02240\pm  0.00025$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00045$ & $ 0.065\pm  0.017$ & $ 3.058\pm  0.030$ & $ 0.9696\pm  0.0060$ & $ 1.131 \pm  0.061$ & $< 0.27$ \\
-lcdm\_alens\_all\_bk14\_tensor & $ 0.02243\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04110\pm  0.00047$ & $ 0.066\pm  0.017$ & $ 3.060\pm  0.030$ & $ 0.9704\pm  0.0062$ & $ 1.142 \pm  0.060$ & $< 0.29$ \\
-lcdm\_alens\_all\_bk14\_vector & $ 0.02240\pm  0.00025$ & $ 0.1181\pm  0.0019$ & $ 1.04107\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.029$ & $ 0.9687\pm  0.0061$ & $ 1.134 \pm  0.061$ & $< 0.68$ \\
-lcdm\_alens\_nopmf\_all\_bk14 & $ 0.02244\pm  0.00025$ & $ 0.1179\pm  0.0020$ & $ 1.04109\pm  0.00046$ & $ 0.066\pm  0.016$ & $ 3.061\pm  0.029$ & $ 0.9700\pm  0.0060$ & $ 1.145 \pm  0.061$ & $< 0.00$ \\
-lcdm\_alens\_planck\_bk14 & $ 0.02256\pm  0.00027$ & $ 0.1174\pm  0.0020$ & $ 1.04120\pm  0.00048$ & $ 0.069\pm  0.017$ & $ 3.068\pm  0.030$ & $ 0.9723\pm  0.0062$ & $ 1.188 \pm  0.066$ & $< 0.28$ \\
-lcdm\_alens\_planck\_bk14\_tensor & $ 0.02257\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9727\pm  0.0060$ & $ 1.186 \pm  0.065$ & $< 0.29$ \\
-lcdm\_alens\_planck\_bk14\_vector & $ 0.02241\pm  0.00029$ & $ 0.1180\pm  0.0021$ & $ 1.04114\pm  0.00048$ & $ 0.065\pm  0.017$ & $ 3.058\pm  0.030$ & $ 0.9670\pm  0.0074$ & $ 1.149 \pm  0.075$ & $< 4.64$ \\
-lcdm\_all\_bk14 & $ 0.02223\pm  0.00021$ & $ 0.1182\pm  0.0018$ & $ 1.04113\pm  0.00049$ & $ 0.074\pm  0.014$ & $ 3.074\pm  0.024$ & $ 0.9686\pm  0.0055$ & $ 0.000 \pm  0.000$ & $< 0.35$ \\
-lcdm\_all\_bk14\_tensor & $ 0.02220\pm  0.00024$ & $ 0.1186\pm  0.0019$ & $ 1.04100\pm  0.00047$ & $ 0.067\pm  0.016$ & $ 3.063\pm  0.029$ & $ 0.9672\pm  0.0057$ & $ 0.000 \pm  0.000$ & $< 0.31$ \\
-lcdm\_all\_bk14\_vector & $ 0.02215\pm  0.00022$ & $ 0.1188\pm  0.0020$ & $ 1.04088\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.028$ & $ 0.9653\pm  0.0055$ & $ 0.000 \pm  0.000$ & $< 0.83$ \\
-lcdm\_r\_alens\_all\_bk14 & $ 0.02242\pm  0.00025$ & $ 0.1175\pm  0.0021$ & $ 1.04111\pm  0.00048$ & $ 0.068\pm  0.018$ & $ 3.063\pm  0.032$ & $ 0.9710\pm  0.0063$ & $ 1.133 \pm  0.062$ & $< 0.24$ \\
-\end{tabular}
-\tablecomments{ 
-Summary of results (will be trimmed for paper). 
-} \normalsize
-\end{center}
-\end{table*}
+\end{table}
 
@@
 
-\begin{table*}[h]
+\begin{table*}[tbh]
 \begin{center}
@@
 
-As a sanity check, we look at the Fisher matrix forecasts for Planck alone as well in both of these cases. 
-For both chains,  we look at the sigma in MCMC with \apmf{} allowed to go negative. 
-While a negative \apmf{} is unphysical, this insulates the analysis against the data preferring negative values, and thereby producing tighter limits. 
-We find for \lcdm{}  + \apmf{}: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
-We find for the 11-parameter model: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
-This degree of consistency is reasonable. \tbd{}
+%As a sanity check, we look at the Fisher matrix forecasts for Planck alone as well in both of these cases. 
+%For both chains,  we look at the sigma in MCMC with \apmf{} allowed to go negative. 
+%While a negative \apmf{} is unphysical, this insulates the analysis against the data preferring negative values, and thereby producing tighter limits. 
+%We find for \lcdm{}  + \apmf{}: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
+%We find for the 11-parameter model: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
+%This degree of consistency is reasonable. \tbd{}
 

### 2016-10-31 pmf.tex
a

@@
 \newcommand{\wmap}{{\sl WMAP}}
-\newcommand{\bicepkeck}{BICEP2/Keck}
+\newcommand{\bicepkeck}{BICEP2/Keck Array}
 \newcommand{\sptnew}{SPT-3G}
@@
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
-We also forecast the expected future limits from stage III CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB stage IV experiment. 
-Future CMB experiments should dramatically reduce the current uncertainties, by two orders of magnitude for stage III experiments and three orders of magnitude for stage IV. 
-The constraints from a stage IV experiment have the potential to rule out much of the parameter space for PMFs.
+We also forecast the expected future limits from soon-to-deploy CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB-S4 experiment. 
+Future CMB experiments should dramatically reduce the current uncertainties, by two orders of magnitude for the near-term experiments and three orders of magnitude for the CMB-S4 experiment. 
+The constraints from CMB-S4 have the potential to rule out much of the parameter space for PMFs.
 
@@
 By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
-We will therefor simply quote effective limits on a PMF. 
+We will therefore simply quote effective limits on a PMF. 
 In this work, we present new upper limits from current CMB polarization data on the possibility of a PMF or parity-violating physics.
@@
 
-Primordial magnetic fields would have observational consequences for Big Bang nucleosynthesis \citep[e.g.,][]{kahniashvili10}, large scale structure \citep[e.g.,][]{battaner97}, ionization history of the Universe \citep{kunze15}, and the black body spectrum of the CMB \citep[e.g.,][]{kunze14},  as well as the CMB anisotropy.
+PMFs would have observational consequences for Big Bang nucleosynthesis \citep[e.g.,][]{kahniashvili10}, large scale structure \citep[e.g.,][]{battaner97}, the ionization history of the Universe \citep{kunze15}, and the black body spectrum of the CMB \citep[e.g.,][]{kunze14},  as well as the CMB anisotropies.
 The CMB anisotropies have yielded some of the strongest constraints on PMFs and are the focus of this work.
@@
 
-In addition to the \planck{} data, we use a number of recent CMB polarization measurements. 
-First, we include TE and EE spectrum measurements\citep{crites15} for $\ell \in [500,3000]$ and BB bandpowers covering $\ell \in [500,2000]$ \citep{keisler15} from SPTpol. 
+In addition to the \planck{} data, we use a number of recent CMB B-mode polarization measurements. 
+First, we include measurements of the TE, EE and BB power spectra from the \sptpol{} experiment \citep{crites15,keisler15}. 
+The BB bandpowers cover the angular multipoles $\ell \in [500,2000]$. 
 We also add the BB bandpowers from \pb{} that cover the multipoles from 500 to 2500 \citep{polarbear14b}. 
-Both the \sptpol{} and \pb{} bandpowers primary constrain the vector mode of the PMF given the angular scales measured. 
+At these angular scales, both the \sptpol{} and \pb{} bandpowers primary constrain the vector modes of a PMF. 
 Finally, we include the latest BICEP2 and Keck Array  joint analysis \citep{bicepkeck15}. 
-This latter dataset also places limits on the tensor mode of the PMF due to its coverage of lower multipoles. 
+This latter dataset also places limits on the tensor modes of a PMF due to its coverage of lower multipoles. 
 During the writing of this work, ACTpol polarization power spectra became available \citep{naess14,louis16}. 
@@
 In all chains, we marginalize over the recommended foreground models for each data set. 
-We do not however require these consistency between these foreground models since the data don't have identical flux cuts and so on. 
+We do not however require these consistency between these foreground models since the data don't have identical flux cuts for extragalactic sources and so on. 
 In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength.
@@
 \ee
-The calculation of the PMF template, \cpmf, is described later. 
+The calculation of the PMF template, \cpmf, is described in \S\ref{sec:template}. 
 Note that no other effect of the PMF is considered; this is one reason we only consider CMB data.
@@
 In many chains, we also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
-Finally, in some cases, we allow non-zero tensors, parameterized as is normal, by the tensor-to-scalar ratio, r.
+Finally, in some cases, we allow non-zero tensors, parameterized by the tensor-to-scalar ratio, r.
 
 \subsection{Primordial Magnetic Field Template}
+\label{sec:template}
 
@@
   The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
-  The dashed purple line shows the PMF template used in this work, scaled to \apmf{} = 0.2. 
-  As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal. 
-  However PMFs also produce a vector component that peaks around $\ell \sim 1700$ and allows the discrimination between  the inflationary and PMF explanations. 
+  The dashed purple line shows the PMF template used in this work, scaled to \apmf{} = 0.2 to match the gravitational wave signal. 
+  As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
+  However, if excess power on these scales is detected, higher order moments of the map (i.e.~4-point estimators) might be used to discriminate between   the inflationary and PMF explanations. 
       \label{fig:pmf-bb}
@@
 With Planck alone, the 95\% confidence upper limit is $\apmf <  0.73$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  0.35$. 
-The limits are slightly better with \alens{} allowed to vary (as a value for \alens{} slightly above unity is preferred). 
+Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a preference for \alens{} above unity). 
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  0.68$, dropping to $\apmf <  0.27$ with the ground-based experiments. 
@@
 Due to the scaling with the fourth power, an upper limit with a flat prior on \apmf{} would lead to an apparent `detection' of \bpmf. 
-We therefore importance sample the chains to generate a flat prior on \bpmf. 
+We thereforee importance sample the chains to generate a flat prior on \bpmf. 
 We find a 95\% limit of $\bpmf < 1.97$\,nG for \planck{} alone, completely consistent with \citep{planck15-19} who found $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
 This is slightly reduced to $\bpmf < 1.85$\,nG for the combined dataset. 
-The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks about 1 sigma above zero, whereas the \planck{} only constraints peaks at zero.
+The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero.
 
@@
 In the minimal model, \lcdm{} + \apmf{}, current CMB power spectra data from \planck, POLARBEAR, SPTpol, and \bicepkeck{} place a 95\% CL upper limit on the PMF power of $\apmf < 0.35$. 
-This limit actually tightens slightly if tensor modes are allowed (r), or the amount of lensing is allowed to vary. 
+This limit tightens slightly if tensor modes are allowed (r), or the amount of lensing is allowed to vary. 
 In the case of r, the tightening is because the observed power at large angular scales is now split between PMFs or inflationary gravitational waves. 
@@
 
-The sensitivity of CMB experiments is increasing rapidly due to the exponential growth in detector counts
+The sensitivity of CMB experiments is increasing rapidly due to the exponential growth in detector counts. 
 \citet{abazajian16} thus defines four stages of CMB experiments. 
@@
 We use Fisher matrices to forecast the constraints on PMFs possible from each generation of experiment. 
-Fisher matrices make it easy to combine different experiments and forecast the final parameter constraints. 
-However, for non-Gaussian likelihoods, there is the potential for Fisher matrix forecasts to significantly underestimate the true uncertainties \citep[see e.g.,][]{wolz12}.
+While Fisher matrices may underestimate the true uncertainties for non-Gaussian likelihoods \citep[see e.g.,][]{wolz12}, they 
+ make it easy to combine different experiments and estimate the final parameter constraints.
 
@@
 A prior on the optical depth of 0.005 is added to account for the expected optical depth constraint from the missing multipoles. 
-Second, we include a 1\% external measurement of the Hubble constant, such as would be expected from the Taipan experiment \citep{kuehn14}.
+Second, we include a 1\% external measurement of the Hubble constant, such as is expected from the Taipan experiment \citep{kuehn14}.
 
 One concern with combining Fisher matrices from different experiments is double-counting modes due to overlapping sky coverage. 
-We sidestep this issue for the TT or TE spectra, by only using the \planck{} measurements. 
+We avoid this problem in different ways in each of the CMB power spectra. 
+For the TT and TE spectra, we avoid double-counting by only using the \planck{} measurements. 
 We do not expect the future experiments to substantially improve upon \planck{} in these spectra which are already cosmic variance limited out to fairly high multipoles. 
-We throw away \planck{} EE data in the overlap region by appropriately increasing the forecasted \planck{} EE uncertainties. 
-The exact increase depends on the assumed stage III or IV survey area.
-We do not include \planck{} BB information in the forecasts. 
-We ignore overlaps between the stage III  with the note that the overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small.
-We do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints. 
+We do the opposite for the EE and BB spectra. 
+We do not include \planck{} BB information in any forecast, and  we throw away \planck{} EE data in the overlap region by appropriately increasing the forecasted \planck{} EE uncertainties. 
+%The exact increase depends on the assumed stage III or IV survey area.
+We ignore overlaps between the stage III  with the note that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
+The overlapping sky coverage will probably be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
 With these measures, no modes should be double-counted in this analysis.
@@
 Unless otherwise noted,  the Fisher matrix forecasts in this work use these numbers. 
-All forecasts also include beam and calibration uncertainty as noted in the text. 
+All forecasts also include beam and calibration uncertainties as noted in the text. 
 } \normalsize
@@
 We list the assumed survey areas, noise levels and beam sizes for each experiment in Table~\ref{tab:experiments}. 
-We also assume a 5\% uncertainty on the beam FWHM and a 1\% power calibration uncertainty; we have tested relaxing or tightening the beam and calibration uncertainty and find these calibration terms have a negligible impact on the PMF constraints.
+We  assume a 5\% uncertainty on the beam FWHM and a 1\% power calibration uncertainty; we have tested relaxing or tightening the beam and calibration uncertainty and find these calibration terms have a negligible impact on the PMF constraints.
 
 We consider the constraints on PMFs in two cosmologies. 
-In all cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
-Generally, we report constraints on the PMFs as one of several extensions to LCDM:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
-However, in order to illustrate the degree to which parameter degeneracies are limiting the inferred constraints,  we also show constraints from an aggressive model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
+The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
+This 11-parameter model is our default cosmological model for forecasting PMF constraints. 
+Additionally, in order to illustrate the degree to which parameter degeneracies are limiting the inferred constraints,  we show constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
+In both cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources.
+
+In this work, we only forecast the uncertainties due to power spectrum (i.e.~2-point estimators) searches for PMFs. 
+Currently the power spectrum limits from \planck{} or \pb{} are better than the 4-point upper limits. 
+Although outside the scope of this work, it would be interesting to extend this analysis to 4-point estimators for two reasons. 
+First, the 4-point limits should improve faster as the noise level falls, and second, in the case of a detection, the 4-point estimators might discriminate between inflationary gravitational waves and tensor PMFs.
 
@@
 
-The experiments that will begin taking data next year will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$ as noted before.  
-The uncertainty is forecast to fall nearly 400-fold by adding the two stage III experiments in this simplified model to $\sigma(\apmf)=0.0012$. 
+The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$ (this is consistent with, although slightly worse than, the upper limits from the real data).  
+Adding the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty nearly 400-fold in this 7-parameter model to $\sigma(\apmf)=0.0012$. 
 Including all eleven parameters marginally weakens the \planck+\ho{} constraints on \apmf{} by 23\%, and the stage III constraint by a substantial factor of 2.5. 
-Even so within this 11-parameter model, the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,180 to  $\sigma(\apmf)=0.0031$. 
+Even within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,180 to  $\sigma(\apmf)=0.0031$. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
 
-The primary motivation behind the proposed CMB stage IV experiment is to search for inflationary gravitational waves and neutrino masses, however, the experiment should also enable extremely sensitive searches for PMFs.
+The primary motivation behind the proposed CMB stage IV experiment commonly called CMB-S4 is to search for inflationary gravitational waves and neutrino masses, however, the experiment should also enable extremely sensitive searches for PMFs.
 We begin by making forecasts for the fiducial CMB-S4 configuration as laid out in Table~\ref{tab:experiments}.
@@
 
-Given that CMB-S4 is still being designed, it is worthwhile to consider how the design decisions might influence the final PMF constraints. 
-We look at four aspects of the experiment design: the telescope size or beam FWHM, the low-$\ell$ noise performance (1/f knee), and the choice of survey area, and how well the beam size and calibration must be known.
+Given that CMB-S4 is still being designed, it is worthwhile to consider how design decisions will affect the final PMF constraints. 
+We look at four aspects of the experiment design: the telescope size or beam FWHM, the low-$\ell$ noise performance (1/f knee),  the choice of survey area, and how well the beam size and calibration must be known.
 Of these four, we find that the low-$\ell$ noise performance and survey area are important to searches for PMFs
 
-Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefor always improve the PMF constraints. 
+Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
 However, larger telescopes are also more expensive to build which means at fixed cost, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
@@
 Next we turn to the recovery of large angular scales, and the noise performance at low frequencies. 
-We measure the importance by shifting the 1/f knee of the map-space noise in the range $\ell = [50,400]$. 
+We look at the impact of shifting the 1/f knee of the map-space noise. 
 Effectively, we are multiplying the noise power, $N_\ell$, which is a constant for white noise,  by a function of angular multipole:
@@
 However, the knee frequency is still important in the more conservative 11-parameter model, where the same shift reduces the uncertainties by a factor of 2.7. 
-In both cases, as can be seen in Fig.~\ref{fig:knee}, the information loss really accelerates when the 1/f knee goes above $\ell \simeq 200$. 
-For the same 11-parameter model, bringing \lknee{} to 200 from 400 yields a factor of 2 (only modestly worse than the 2.7x improvement for \lknee=50). 
+In both cases, as can be seen in Fig.~\ref{fig:knee}, the information loss accelerates once the 1/f knee goes above $\ell \simeq 200$. 
 Recovering large angular scales is clearly important to PMF searches. 
@@
 It is also consistent with the current upper limits, which are dominated by the BICEP2/Keck Array data at low-$\ell$. 
-Fortunately, these large angular scales are also crucial to searches for inflationary gravitational waves, so the needs of the PMF search are well-aligned with one of the key science drivers for CMB-S4.
+As  these large angular scales are also crucial to searches for inflationary gravitational waves, hitting this target should not place new requirements on CMB-S4. 
+The needs of the PMF search are well-aligned with the search for inflationary gravitational waves.
 
@@
   In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
   The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
@@
 A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-As shown in  Fig.~\ref{fig:area}, it is better to go as wide as possible. 
+As shown in  Fig.~\ref{fig:area}, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
 A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
@@
 
-Finally, we consider if searches for PMFs introduce new requirements on the knowledge to which the instrumental beam or overall calibration of the experiments must be known. 
+Finally, we consider if searches for PMFs introduce new requirements on the accuracy to which the instrumental beam or overall calibration of an experiment must be known. 
 We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
 We find negligible, sub-percent shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
-The PMF constraints are insensitive to beam and calibration uncertainty.
+The PMF constraints are insensitive to the beam and calibration uncertainties.
 
@@
 
-In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB polarization data. 
-By adding \bicepkeck{}, \pb, and \sptpol to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < 0.68$ to $\apmf < 0.33$. 
+In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB B-mode polarization data. 
+By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < 0.73$ to $\apmf < 0.35$. 
 The biggest contributor to this improvement is the low-$\ell$ data from \bicepkeck{}.
 
-We have also shown that the next generation of experiments have the potential power to dramatically reduce these limits, and potentially detect PMFs for the first time. 
-The so-called stage III experiments, which should begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.0062$ even after marginalizing over a five-parameter extension to \lcdm.
+We have also shown that the next generation of experiments should dramatically reduce these limits, and potentially detect PMFs for the first time. 
+These so-called stage III experiments, which will begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.0062$ even after marginalizing over a five-parameter extension to \lcdm.
 

### 2016-11-01 pmf.tex
a

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[apj]{emulateapj}
-\documentclass[preprint]{emulateapj}
+\documentclass[apj]{emulateapj}·
+%\documentclass[preprint2]{aastex61}
 %\documentclass[12pt,preprint]{aastex}
@@
 
-\usepackage[table,usenames,dvipsnames]{xcolor}
-\usepackage{amsmath}
-\usepackage{subfigure}
+%\usepackage[table,usenames,dvipsnames]{xcolor}
+%\usepackage{amsmath}
+%\usepackage{subfigure}
 \usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
 \usepackage{natbib}
-\usepackage{graphicx}
-\usepackage{multirow}
+%\usepackage{natbib}
+\bibliographystyle{fapj}
+%\usepackage{graphicx}
+%\usepackage{multirow}
 
@@
 
-\bibliographystyle{fapj}
+%
 
 % ref to section \S\ref{sec:label}
+
+%\submitjournal{ApJ}
 
@@
 With the CMB power spectrum data that will be the focus of this paper, \citet{planck15-19} find 95\% CL upper limits ranging from $\bpmf < 5.6$\,nG to $<0.7$\,nG depending on the exact model. 
+Here \bpmf{} is the rms field strength on a 1\,Mpc length scale. 
 The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{polarbear14b}. 
@@
 In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength. 
+These data are plotted against the expected B-mode power spectrum for the standard cosmological model in Fig.~\ref{fig:pmf-experiments}.
 
@@
 Instead, we use CMBACT to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$. 
-This template is plotted against the current measurements of the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
+This template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
 We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
@@
 With Planck alone, the 95\% confidence upper limit is $\apmf <  0.73$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  0.35$. 
+We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}. 
 Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a preference for \alens{} above unity). 
@@
 The other datasets do not have a large impact on the observed limits. 
+In short, the reduction in the allowed upper limit on \apmf{} is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
 
@@
 Due to the scaling with the fourth power, an upper limit with a flat prior on \apmf{} would lead to an apparent `detection' of \bpmf. 
-We thereforee importance sample the chains to generate a flat prior on \bpmf. 
+We therefore importance sample the chains to generate a flat prior on \bpmf. 
 We find a 95\% limit of $\bpmf < 1.97$\,nG for \planck{} alone, completely consistent with \citep{planck15-19} who found $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
@@
 Currently the power spectrum limits from \planck{} or \pb{} are better than the 4-point upper limits. 
-Although outside the scope of this work, it would be interesting to extend this analysis to 4-point estimators for two reasons. 
-First, the 4-point limits should improve faster as the noise level falls, and second, in the case of a detection, the 4-point estimators might discriminate between inflationary gravitational waves and tensor PMFs.
+Although outside the scope of this work, it would be interesting to extend this analysis to 4-point estimators for several reasons. 
+First, the 4-point limits should improve faster as the noise level falls. 
+Second, in the case of a detection, the 4-point estimators might discriminate between inflationary gravitational waves and tensor PMFs. 
+Finally, a lensing estimator might be used to `de-lense' the B-mode power spectrum, thereby suppressing the lensed B-mode signal and allowing better limits on PMFs. 
+Such de-lensing techniques have long been proposed for inflationary gravitational wave searches \citep[e.g.][]{knox02,kesden02,seljak04a,simard15} and more recently been demonstrated on real \planck{} data \citep{larsen16}.
 

### 2016-11-01 pmf.tex
a

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[apj]{emulateapj}·
+\documentclass[apj]{emulateapj}
 %\documentclass[preprint2]{aastex61}
@@
 %\submitjournal{ApJ}
-
+\def\Melbourne{1}
+\def\uci{2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \title{Current and future constraints on primordial magnetic fields}
-\author{TBD}
-
+\author{C.~L.~Reichardt\altaffilmark{\Melbourne}, D.~Sutton\altaffilmark{\Melbourne}, and C.~Feng\altaffilmark{\uci}}
+\altaffiltext{\Melbourne}{School of Physics, University of Melbourne, Parkville, VIC 3010, Australia}
+\altaffiltext{\uci}{Department of Physics and Astronomy, University of California, Irvine, CA 92697-4575, USA}
 \email{christian.reichardt@unimelb.edu.au}
@@
 
-We thank XXX for valuable feedback on the manuscript. 
+We thank Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
 C. Reichardt is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 

### 2016-11-03 pmf.tex
a

@@
 Measurements of the cosmic microwave background (CMB) temperature anisotropy have provided some of the most powerful tests of cosmology. 
-We are now entering a new era as experiments begin to measure  polarized ``B-modes" in the CMB for the first time \citep{hanson13,polarbear14b,bicep2014a,naess14,keisler15,bicepkeck15,louis16}. 
+We are now entering a new era as experiments begin to measure  polarized ``B-modes" in the CMB for the first time \citep{hanson13,polarbear14b,bicep14a,naess14,keisler15,bicepkeck15,louis16}. 
 Precision measurements of CMB polarization promise new tests of the standard cosmological model. 
@@
 
-The density and stress perturbations introduced by PMFs give rise to vorticity and gravitational waves in the early photon-baryon  plasma, i.e. vector and tensor modes. 
+The density and stress perturbations introduced by PMFs give rise to vorticity and gravitational waves in the early photon-baryon  plasma, i.e. vector and tensor modes, as well as scalar modes. 
 The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
@@
 Instead, we use CMBACT to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$. 
+This template includes tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
+We expect the missing scalar power to degrade the \planck-only results in this work.
+However the missing scalar power should be  unimportant for the EE and BB spectra that are driving the tightest constraints. 
 This template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
 We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
-We can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:
+For vector modes, we can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:
 \be
@@
 \ee
-An unfortunate consequence of this steep scaling is that substantial reductions in the observationally allowed power lead to only modestly better limits on the magnetic field strength. 
+Note that the situation is more complicated for the tensor PMF modes where this power law scaling has not been demonstrated. 
+An unfortunate consequence of this steep scaling is that substantial reductions in the observationally allowed vector-mode power lead to only modestly better limits on the magnetic field strength. 
 However, if a PMF is detected, this same steep scaling would allow excellent constraints on its properties.
@@
   As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
-  However, if excess power on these scales is detected, higher order moments of the map (i.e.~4-point estimators) might be used to discriminate between   the inflationary and PMF explanations. 
+  %However, if excess power on these scales is detected, higher order moments of the map (i.e.~4-point estimators) might be used to discriminate between   the inflationary and PMF explanations. 
       \label{fig:pmf-bb}
@@
 We propagate these limits on the observed PMF power into limits on the magnetic field strength, \bpmf. 
-Due to the scaling with the fourth power, an upper limit with a flat prior on \apmf{} would lead to an apparent `detection' of \bpmf. 
+We assume the scaling appropriate to the vector modes, i.e. $\apmf \propto \bpmf^4$,  applies to both vector and tensor modes. 
+Given this assumed scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent `detection' of \bpmf. 
 We therefore importance sample the chains to generate a flat prior on \bpmf. 
-We find a 95\% limit of $\bpmf < 1.97$\,nG for \planck{} alone, completely consistent with \citep{planck15-19} who found $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
-This is slightly reduced to $\bpmf < 1.85$\,nG for the combined dataset. 
+We find a 95\% limit of $\bpmf < 2.0$\,nG for \planck{} alone, completely consistent with \citep{planck15-19} who found $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
+This is only slightly reduced to $\bpmf < 1.9$\,nG for the combined dataset. 
 The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero. 
+We also stress that this should not be treated as a robust limit as the tensor PMF modes are crucial to the improvement, and the assumed scaling has not been tested for the tensor PMF. 
+We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
 
@@
 Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{benson14,suzuki16,henderson16} have approximately ten times more detectors, and generically will start collecting data in 2017 and finish in 2020-21.
-In this section, we forecast the expected constraints from the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
+In this section, we forecast the expected constraints from EE and BB power spectrum measurements  of the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
 There is also a proposal to build a stage IV experiment, CMB-S4,  that would increase the detector counts by another order of magnitude and hopefully begin taking data in the early 2020s.
-We examine the likely PMF constraints from CMB-S4, and consider which aspects of experimental or survey design are important to maximize the recovered information on PMFs.
+We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are important to maximize the recovered information on PMFs.
 
@@
 We use Fisher matrices to forecast the constraints on PMFs possible from each generation of experiment. 
-While Fisher matrices may underestimate the true uncertainties for non-Gaussian likelihoods \citep[see e.g.,][]{wolz12}, they 
+The Fisher matrix, $\mathcal{F}_{ij}$, can be defined as:
+\be
+\mathcal{F}_{ij} = \frac{1}{2} \frac{\partial^2 \chi^2}{\partial p_i \partial p_j},
+\ee
+for parameters, p. 
+The inverse of the Fisher matrix will be the covariance matrix for the parameters. 
+While Fisher matrices underestimate the true uncertainties for non-Gaussian likelihoods \citep[see e.g.,][]{wolz12}, they 
  make it easy to combine different experiments and estimate the final parameter constraints.
@@
 This 11-parameter model is our default cosmological model for forecasting PMF constraints. 
-Additionally, in order to illustrate the degree to which parameter degeneracies are limiting the inferred constraints,  we show constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
+We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is with the tensor-to-scalar ratio, r. 
+The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and PMFs is nearly identical. 
+To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
 In both cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources.
@@
 First, the 4-point limits should improve faster as the noise level falls. 
-Second, in the case of a detection, the 4-point estimators might discriminate between inflationary gravitational waves and tensor PMFs. 
+Second, in the case of a detection, the 4-point estimators would almost certainly come into play to learn more about the vector modes of the PMFs. 
+The detection (or non-detection) of the vector PMF signal in the 4-point estimators could also be used to argue for whether it is more likely that any observed tensor power is due to  inflationary gravitational waves or  PMFs.
 Finally, a lensing estimator might be used to `de-lense' the B-mode power spectrum, thereby suppressing the lensed B-mode signal and allowing better limits on PMFs. 
@@
 With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$ (this is consistent with, although slightly worse than, the upper limits from the real data).  
-Adding the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty nearly 400-fold in this 7-parameter model to $\sigma(\apmf)=0.0012$. 
+Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty nearly 400-fold in this 7-parameter model to $\sigma(\apmf)=0.0012$. 
 Including all eleven parameters marginally weakens the \planck+\ho{} constraints on \apmf{} by 23\%, and the stage III constraint by a substantial factor of 2.5. 
@@
 The primary motivation behind the proposed CMB stage IV experiment commonly called CMB-S4 is to search for inflationary gravitational waves and neutrino masses, however, the experiment should also enable extremely sensitive searches for PMFs.
-We begin by making forecasts for the fiducial CMB-S4 configuration as laid out in Table~\ref{tab:experiments}.
+We look at the prospects for these searches using the polarization information (EE and BB power spectra) from CMB-S4. 
+We begin by making forecasts for the fiducial CMB-S4 configuration as laid out in Table~\ref{tab:experiments}, and then consider how changing the experimental design would impact the expected uncertainties.
 
@@
 C. Reichardt is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 
+CF acknowledges support from NASA grants NASA NNX16AJ69G and NASA NNX16AF39G. 
 This research used resources of the National Energy Research Scientific Computing Center, which is supported by the Office of Science of the U.S.

### 2016-11-28 pmf.tex
a
added reference to figure 1 in sectin 2.1

@@
 \title{Current and future constraints on primordial magnetic fields}
-\author{C.~L.~Reichardt\altaffilmark{\Melbourne}, D.~Sutton\altaffilmark{\Melbourne}, and C.~Feng\altaffilmark{\uci}}
+\author{D.~Sutton\altaffilmark{\Melbourne}, C.~Feng\altaffilmark{\uci}, and C.~L.~Reichardt\altaffilmark{\Melbourne}}
 \altaffiltext{\Melbourne}{School of Physics, University of Melbourne, Parkville, VIC 3010, Australia}
@@
 CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or a primordial magnetic field (PMF) \citep{kosowsky96, seshadri01}.
-Both effects lead to cosmic birefringence and the rotation of E-modes into B-modes. 
+Both effects lead to the rotation of E-modes into B-modes. 
 By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
@@
 Here \bpmf{} is the rms field strength on a 1\,Mpc length scale. 
-The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{polarbear14b}. 
+The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{polarbear15}. 
 The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < 3.9$\,nG. 
@@
 The BB bandpowers cover the angular multipoles $\ell \in [500,2000]$. 
-We also add the BB bandpowers from \pb{} that cover the multipoles from 500 to 2500 \citep{polarbear14b}. 
-At these angular scales, both the \sptpol{} and \pb{} bandpowers primary constrain the vector modes of a PMF. 
+We also add the BB bandpowers from \pb{} that cover the multipoles from 500 to 2500 \citep{polarbear15}. 
+At these angular scales, both the \sptpol{} and \pb{} bandpowers primarily constrain the vector modes of a PMF. 
 Finally, we include the latest BICEP2 and Keck Array  joint analysis \citep{bicepkeck15}. 
@@
 During the writing of this work, ACTpol polarization power spectra became available \citep{naess14,louis16}. 
-We have not included them as the public likelihoods do not include the B-mode power spectrum; we do not expect adding the ACTpol bandpowers to significantly change the PMF limits based on a visual comparison of the current BB bandpowers from different experiments.
+We have not included them as the public likelihoods do not include the B-mode power spectrum; we do not expect adding the ACTpol bandpowers to significantly change the PMF limits based on a visual comparison of the current BB bandpowers from different experiments (see Fig.~\ref{fig:pmf-experiments}).
 In all chains, we marginalize over the recommended foreground models for each data set. 
-We do not however require these consistency between these foreground models since the data don't have identical flux cuts for extragalactic sources and so on. 
+We do not however require consistency between these foreground models since the data don't have identical flux cuts for extragalactic sources and so on. 
 In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength. 
@@
 We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
-For vector modes, we can translate the amplitude constraint on this template to a constraint rms magnetic field strength on 1\,Mpc scales , \bpmf, using the expected scaling:
+For vector modes, we can translate the amplitude constraint on this template to a constraint on the rms magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
 \be
@@
 We look at four aspects of the experiment design: the telescope size or beam FWHM, the low-$\ell$ noise performance (1/f knee),  the choice of survey area, and how well the beam size and calibration must be known.
-Of these four, we find that the low-$\ell$ noise performance and survey area are important to searches for PMFs
+Of these four, we find that the low-$\ell$ noise performance and survey area are important to searches for PMFs.
 

### 2016-11-28 pmf.tex
a

@@
 We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
-For vector modes, we can translate the amplitude constraint on this template to a constraint on the rms magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
+We can translate the amplitude constraint on this template to a constraint on the rms magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
 \be
@@
 \ee
-Note that the situation is more complicated for the tensor PMF modes where this power law scaling has not been demonstrated. 
-An unfortunate consequence of this steep scaling is that substantial reductions in the observationally allowed vector-mode power lead to only modestly better limits on the magnetic field strength. 
+Note that the power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, which is not captured in the above expression. 
+An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed vector-mode power lead to only modestly better limits on the magnetic field strength.
 However, if a PMF is detected, this same steep scaling would allow excellent constraints on its properties.

### 2017-01-05 pmf.tex
a

@@
 The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$ (this is consistent with, although slightly worse than, the upper limits from the real data).  
-Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty nearly 400-fold in this 7-parameter model to $\sigma(\apmf)=0.0012$. 
-Including all eleven parameters marginally weakens the \planck+\ho{} constraints on \apmf{} by 23\%, and the stage III constraint by a substantial factor of 2.5. 
-Even within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,180 to  $\sigma(\apmf)=0.0031$. 
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.15$ (\tbd{need to check how this compares}this is consistent with, although slightly worse than, the upper limits from the real data).
+Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty by an order of magnitude in this 7-parameter model to $\sigma(\apmf)=0.015$. 
+Including all eleven parameters substantially weakens the \planck+\ho{} constraints on \apmf{} by a factor of five, and the stage III constraint by a more modest 40\%. 
+Thus within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
   \caption[Map knee dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected as the low-frequency map noise decreases.  
-  In particular, achieving a map 1/f knee frequency at or below $\ell = 200$ substantially improves the potential power of CMB-S4 PMF searches. 
-  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected as the low-frequency map noise decreases for a nearly scale-invariant PMF ($n_b = -2.9$). 
+  In particular, achieving a map 1/f knee frequency at or below $\ell = 200$ substantially improves the potential power of CMB-S4 PMF searches for nearly scale-invariant PMFs. 
+  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model with $n_B = -2.9$. 
   The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
@@
   As we expect, reducing low-frequency noise would lead to better PMF constraints. 
+      Note however, the dependence on the low-frequency noise quickly disappears as $n_b$ increases (not shown); the improvement across this range of knees is small for $n_B=-1$ and negligible for $n_B=2$.
+
     \label{fig:knee}

### 2017-01-18 pmf.tex
dont

--- 2016-11-28 pmf.tex
@@
 
-%\usepackage[table,usenames,dvipsnames]{xcolor}
+\usepackage[table,usenames,dvipsnames]{xcolor}
 %\usepackage{amsmath}
@@
 
-CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or a primordial magnetic field (PMF) \citep{kosowsky96, seshadri01}.
+CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or primordial magnetic fields (PMFs) \citep{kosowsky96, seshadri01}.
 Both effects lead to the rotation of E-modes into B-modes. 
 By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
-We will therefore simply quote effective limits on a PMF. 
+It is therefore common to simply quote effective limits on PMFs. 
 In this work, we present new upper limits from current CMB polarization data on the possibility of a PMF or parity-violating physics.
 
-Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
-There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
+Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for a review, see][]{ryu12, widrow12}. 
+There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although there are alternative explanations \citep{broderick12}. 
 High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
-These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
+These pairs should later annihilate  at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
 Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
@@
 The mechanism to create large-scale magnetic fields, especially in intergalactic space, remains unclear. 
-One popular proposal is that the observed fields are the product of primordial magnetic fields, which are predicted by several theories of the early Universe \citep[e.g.,][]{turner88, grasso98,ichiki06}.
-Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed fields into the stronger fields observed today. 
-Of course, this amplification process may have a different initial seed; other ideas include AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
+One popular proposal is that the observed fields are the product of PMFs, which are predicted by several theories of the early Universe \citep[e.g.,][]{turner88, grasso98,ichiki06}. 
+Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed PMFs into the stronger fields observed today. 
+Of course, this amplification process may be seeded through other means, such as AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
 However, the possibility of PMFs opens up the intriguing idea that observations of large-scale magnetic fields may offer insights into the physics of the very early Universe.
@@
 The CMB anisotropies have yielded some of the strongest constraints on PMFs and are the focus of this work.
-There have been two recent results of note. 
+There have been three recent results of note. 
 \citet{planck15-19} have used the \planck{} 2015 release of temperature and polarization data to set limits on a variety of PMF models. 
@@
 The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < 3.9$\,nG. 
-Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{keisler15,bicepkeck15}.
-In this paper, we will combine the data from all four experiments to determine simple limits on the PMF, and then examine Fisher matrix forecasts on PMF models from the stage-III and stage-IV CMB experiments being built or designed right now.
+Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{keisler15,bicepkeck15}, 
+and \citet{zucca16} reported constraints from the combination of the \planck{}  and \sptpol{} bandpowers. 
+In this paper, we will combine the data from all four experiments to determine upper limits on PMFs, and find that the \bicepkeck{} data in particular improves these upper limits. 
+We then present Fisher matrix forecasts on PMF models for the stage-III and stage-IV CMB experiments being built or designed right now.
 
-The outline of the paper is as follows. 
-In \S\ref{sec:data}, we lay out the data used and the MCMC implementation used to constrain the PMF amplitude. 
+The outline of this paper is as follows. 
+In \S\ref{sec:data}, we lay out the data and how we use the data to put limits on PMFs. 
 We present the results of this analysis on current data in \S\ref{sec:results}. 
-The assumed parameters for future experiments and the resulting Fisher matrix forecasts are described in \S\ref{sec:forecasts}. 
+In \S\ref{sec:forecasts}, we forecast constraints from future experiments using a Fisher matrix formulism. 
 We conclude in \S\ref{sec:conclusions}.
@@
 We do not however require consistency between these foreground models since the data don't have identical flux cuts for extragalactic sources and so on. 
-In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength. 
+%In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength. 
 These data are plotted against the expected B-mode power spectrum for the standard cosmological model in Fig.~\ref{fig:pmf-experiments}.
@@
 
-For the real data, unless noted, we assume the six parameter spatially flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF.
+For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF.
 We adopt flat priors on all parameters. 
@@
 The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
-We use the CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}  to do this calculation. 
-The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_b k^{n_b}$. 
-Here $n_b$ is the spectral index of PMF and $A_b$ is its amplitude. 
-We can translate the amplitude, $A_b$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
+The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_b k^{n_b}$, with $n_b$ the spectral index and $A_b$ the PMF power. 
+We can translate the power, $A_b$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
 Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
@@
 Given that we are still in the era of upper limits,  we do not explore the full 3-dimensional PMF parameter space in this work. 
-Instead, we use CMBACT to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$. 
-This template includes tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
+Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$.
+We also look at $n_b=-1$ and $n_b=2$ in the forecasting section. 
+We have compared calculated templates to the outputs of the earlier CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}, and find excellent agreement as would be hoped.
+The decision to use the  \citet{zucca16} code instead of CMBACT was based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
+The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
 We expect the missing scalar power to degrade the \planck-only results in this work.
-However the missing scalar power should be  unimportant for the EE and BB spectra that are driving the tightest constraints. 
-This template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
-We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
+However the missing scalar power should be  unimportant for the EE and BB spectra that are driving the tightest constraints, particularly when looking at forecasts for the next generation of experiments.
+The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
+In the MCMC, we add a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
 We can translate the amplitude constraint on this template to a constraint on the rms magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
@@
   The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
-  The dashed purple line shows the PMF template used in this work, scaled to \apmf{} = 0.2 to match the gravitational wave signal. 
+  The dashed purple line shows the nearly-scale invariant ($n_b=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
   As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
@@
 \end{figure*}
+
+\begin{figure}[htb]\centering
+\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
+  \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
+  How the expected PMF changes with the spectral index, $n_B$. 
+  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
+  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
+  }
+\end{figure}
 
@@
 We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}. 
-Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a preference for \alens{} above unity). 
+Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity). 
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  0.68$, dropping to $\apmf <  0.27$ with the ground-based experiments. 
@@
 The other datasets do not have a large impact on the observed limits. 
-In short, the reduction in the allowed upper limit on \apmf{} is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
+In short, the reduction in the allowed upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_b=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
 
@@
 The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero. 
-We also stress that this should not be treated as a robust limit as the tensor PMF modes are crucial to the improvement, and the assumed scaling has not been tested for the tensor PMF. 
-We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
+%We also stress that this should not be treated as a robust limit as the tensor PMF modes are crucial to the improvement, and the assumed scaling has not been tested for the tensor PMF. 
+%We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
+These results are inconsistent (being higher) with the equivalent \planck{} + \sptpol{} upper limit quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
 
@@
 
-The sensitivity of CMB experiments is increasing rapidly due to the exponential growth in detector counts. 
+The sensitivity of CMB experiments is increasing rapidly due to the continuing growth in the number of detectors. 
 \citet{abazajian16} thus defines four stages of CMB experiments. 
 The current experiments (i.e.~the ones used for PMF constraints in the last section) are classified as Stage II experiments. 
-Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{benson14,suzuki16,henderson16} have approximately ten times more detectors, and generically will start collecting data in 2017 and finish in 2020-21.
-In this section, we forecast the expected constraints from EE and BB power spectrum measurements  of the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
+Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{benson14,suzuki16,henderson16} have approximately ten times more detectors, and generically will start collecting data around 2017 and finish three to four years later.
+In this section, we forecast the expected constraints from the EE and BB power spectrum measurements  of the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
 There is also a proposal to build a stage IV experiment, CMB-S4,  that would increase the detector counts by another order of magnitude and hopefully begin taking data in the early 2020s.
+A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016. 
 We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are important to maximize the recovered information on PMFs.
@@
 We do the opposite for the EE and BB spectra. 
-We do not include \planck{} BB information in any forecast, and  we throw away \planck{} EE data in the overlap region by appropriately increasing the forecasted \planck{} EE uncertainties. 
+We do not include \planck{} BB information in any forecast, and  we throw away \planck{} EE data in the overlap region by appropriately increasing the \planck{} EE uncertainties. 
 %The exact increase depends on the assumed stage III or IV survey area.
-We ignore overlaps between the stage III  with the note that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
+We ignore overlaps between the stage III  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
 The overlapping sky coverage will probably be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
+This prior is only relevant in practice when the assumed CMB-S4 configuration has a larger beam size than SPT-3G. 
 With these measures, no modes should be double-counted in this analysis.

### 2017-01-18 pmf.tex
edits`:wq

@@
 We ignore overlaps between the stage III  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
-The overlapping sky coverage will probably be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
+This is also why we do not include both Simons Array and AdvACTpol as the two experiments are likely to have substantial sky overlap. 
+The overlapping sky coverage is expected to be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
 This prior is only relevant in practice when the assumed CMB-S4 configuration has a larger beam size than SPT-3G. 
@@
 The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
-This 11-parameter model is our default cosmological model for forecasting PMF constraints. 
+This 11-parameter model is our default cosmological model for forecasting future PMF constraints. 
 We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is with the tensor-to-scalar ratio, r. 
@@
 In both cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
+We assume the galactic foregrounds are removed by a judicious combination of data from multiple frequencies.
 
@@
 The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.15$ (\tbd{need to check how this compares}this is consistent with, although slightly worse than, the upper limits from the real data).
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.15$ for a nearly-scale invariant PMF spectrum (i.e.~$n_b=-2.9).
+(\tbd{need to check how this compares}This is consistent with, although slightly worse than, the upper limits from the real data).
 Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty by an order of magnitude in this 7-parameter model to $\sigma(\apmf)=0.015$. 
-Including all eleven parameters substantially weakens the \planck+\ho{} constraints on \apmf{} by a factor of five, and the stage III constraint by a more modest 40\%. 
+The improvement is larger when including all eleven parameters, as the parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while only weakening the stage III constraint by a  more modest 40\%.
 Thus within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
+The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
+$n_b=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
+The improvement for the CMB-S3 experiments over \planck{} remains impressive at a factor of 17 and 13 respectively. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
 We look at four aspects of the experiment design: the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
-Of these four, we find that the low-$\ell$ noise performance and survey area are important to searches for PMFs.
+Of these four, we find that the first three, the beam FWHM, low-$\ell$ noise performance and survey area, to be potentially important to searches for PMFs. 
+As should be expected, the preferred design depends on the shape of the PMF spectrum ($n_B$) which controls  the relative power between large and small angular scales.
+
+\tbd{got to here}
 

### 2017-01-22 pmf.tex
added numbers from prelim chains,
made file with numbers defined for easy updating later

@@
 
+\include{number_list}
+
 %
@@
 We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.35$ for the combined dataset at 95\% CL. 
+We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < \upperAplk$ from Planck alone to $\apmf < \upperAall$ for the combined dataset at 95\% CL. 
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
@@
 We find the addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement. 
-With Planck alone, the 95\% confidence upper limit is $\apmf <  0.73$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  0.35$. 
+With Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$. 
 We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}. 
 Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity). 
-In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  0.68$, dropping to $\apmf <  0.27$ with the ground-based experiments. 
-We test which datasets are important by adding single datasets to the \planck{} set while allowing \alens{} to float, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  0.28$) and \sptpol{} ($\apmf <  0.42$) B-mode power spectrum measurements.
+In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments. 
+We test which datasets are important by adding single datasets to the \planck{} set while allowing \alens{} to float, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicepalens$) and \sptpol{} ($\apmf <  \upperAsptpolalens$) B-mode power spectrum measurements.
 The other datasets do not have a large impact on the observed limits. 
@@
 We therefore importance sample the chains to generate a flat prior on \bpmf. 
-We find a 95\% limit of $\bpmf < 2.0$\,nG for \planck{} alone, completely consistent with \citep{planck15-19} who found $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
-This is only slightly reduced to $\bpmf < 1.9$\,nG for the combined dataset. 
+We find a 95\% limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
+This is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
+The difference is due to a difference in the calculated tensor PMF power (for the same parameters) between the XXX and YYY codes. 
+Using the YYY code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
+Returning to the XXX code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
 The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero. 
@@
 \hline
-\lcdm{} + \apmf{} &  $< 0.35$ & - & - \\
-~~~+\alens{} & $< 0.27$ &$ 1.131 \pm  0.061$ &  -\\
-~~~+\alens{}+r&  $< 0.24$&$ 1.133 \pm  0.062$ & $<0.056$\\ 
+\lcdm{} + \apmf{} &  $< \upperAall$ & - & - \\
+~~~+\alens{} & $< \upperAallalens$ &$ \medAlensall \pm  \sigmaAlensall$ &  -\\
+~~~+\alens{}+r&  $< \upperAallalensr$&$ \medAlensRall \pm  \sigmaAlensRall$ & $<\upperRall$\\ 
 \end{tabular}
 \tablecomments{ 
-In the minimal model, \lcdm{} + \apmf{}, current CMB power spectra data from \planck, POLARBEAR, SPTpol, and \bicepkeck{} place a 95\% CL upper limit on the PMF power of $\apmf < 0.35$. 
+In the minimal model, \lcdm{} + \apmf{}, current CMB power spectra data from \planck, POLARBEAR, SPTpol, and \bicepkeck{} place a 95\% CL upper limit on the PMF power of $\apmf < \upperAall$. 
 This limit tightens slightly if tensor modes are allowed (r), or the amount of lensing is allowed to vary. 
@@
 The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.15$ for a nearly-scale invariant PMF spectrum (i.e.~$n_b=-2.9).
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_b=-2.9$).
 (\tbd{need to check how this compares}This is consistent with, although slightly worse than, the upper limits from the real data).
@@
 In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB B-mode polarization data. 
-By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < 0.73$ to $\apmf < 0.35$. 
+By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
 The biggest contributor to this improvement is the low-$\ell$ data from \bicepkeck{}.

### 2017-01-23 pmf.tex
work on fihser

@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
+\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
   \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
@@
 With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_b=-2.9$). 
-(\tbd{need to check how this compares}This is consistent with, although slightly worse than, the upper limits from the real data).
+This is consistent with, although somewhat better than, the upper limits from the real data).  
 Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty by an order of magnitude in this 7-parameter model to $\sigma(\apmf)=0.015$. 
@@
 
+Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
+We find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered: a beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
+
+However, larger telescopes are also more expensive to build which means for a fixed experimental budget, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
+We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin{} for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin{} for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin{} for a FWHM of 1$^\prime$.
+We find 
+Improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_b = -2.9, -1, +2$ respectively.
+However the results are close enough that the crudeness of the cost-neutral estimates used here could be a factor, and the preference might flip for more accurately costed setups. 
+In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one would lean towards adding more detectors. 
+Raw sensitivity is important to an experiment's ability to study PMFs.
+
+\begin{figure}[htb]\centering
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
+  \caption[Area dependence]{
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
+  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
+  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
+  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
+  In both cases, better limits on PMFs will be achieved with wider surveys.
+    \label{fig:area}
+  }
+\end{figure}
+A second question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
+As shown in  Fig.~\ref{fig:area}, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
+A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
+With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and improve by another factor of 1.4-1.5 by going to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
+
 \tbd{got to here}
-
-Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
-However, larger telescopes are also more expensive to build which means at fixed cost, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
-We find the gains due to resolution at fixed mapping speed to be negligible: a beam size of FWHM=1$^\prime$ yields only a 1\% better limit than a FWHM of 10$^\prime$. 
-This illustrates how important the large angular scales are to the PMF limits. 
-We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin{} for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin{} for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin{} for a FWHM of 1$^\prime$.
-In this quasi-cost-neutral setup, there is a strong preference to go for more detectors over better angular resolution: the uncertainty was a factor of 2.5 times smaller in the coarse case over the FWHM=1$^\prime$ case.
-Raw sensitivity is more important than angular resolution to an experiment's ability to study PMFs.
 
@@
 
-\begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
-  \caption[Area dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
-  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
-  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
-  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
-  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
-  In both cases, better limits on PMFs will be achieved with wider surveys.
-    \label{fig:area}
-  }
-\end{figure}
-A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-As shown in  Fig.~\ref{fig:area}, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
-A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
-With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and improve by another factor of 1.4-1.5 by going to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
-
 Finally, we consider if searches for PMFs introduce new requirements on the accuracy to which the instrumental beam or overall calibration of an experiment must be known. 
+We find they do not. 
 We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
 We find negligible, sub-percent shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
-The PMF constraints are insensitive to the beam and calibration uncertainties.
+The PMF constraints  for all three power law indices considered are insensitive to the beam and calibration uncertainties.
 

### 2017-01-23 pmf.tex
rnd 1 thru forecasts

@@
 
+\subsubsection{Telescope size}
+
 Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
@@
 
+\subsubsection{Survey Area}
+
 \begin{figure}[htb]\centering
@@
   In both cases, better limits on PMFs will be achieved with wider surveys.
+  \tbd{may change strength of statements; haven't updated figure or caption}
     \label{fig:area}
@@
 \end{figure}
+
+\tbd{may change strength of statements}
 A second question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-As shown in  Fig.~\ref{fig:area}, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
+Unsurprisingly, we find opposing preferences for the scale-invariant $n_b=-2.9$ (which peaks at large scales) and very blue $n_b=2$ spectrum peaking at small scales. 
+We find very little dependence on area for the intermediate case of $n_b=-1$. 
+As shown in  Fig.~\ref{fig:area}, for $n_b=-2.9$, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
 A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
-With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and improve by another factor of 1.4-1.5 by going to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
+With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and are nearly flat (a 6\% improvement) from 25\% to 70\% of the sky (the widest area likely to be possible after galactic cuts).
+Conversely, $n_b=+2$, the optimal survey area is as small as possible. 
+Note however that the minimum is extremely broad with only a 10\% worsening of the expected uncertainty as the survey area is increased from 10\% to 70\% of the  full sky. 
+The optimal survey area for a PMF survey will depend on the targeted PMF models.
 
-\tbd{got to here}
+\subsubsection{Fidelity at large angular scales}
 
@@
 Note that this knob  serves as a placeholder for several effects, including a signal-to-noise hit due to galactic foregrounds or the methods used to clean these foregrounds, atmospheric noise, or actual instrumental 1/f noise.
-We find the results to be somewhat more sensitive to the 1/f knee in the simple \lcdm{}+\apmf{} model, where dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 6.3.
-However, the knee frequency is still important in the more conservative 11-parameter model, where the same shift reduces the uncertainties by a factor of 2.7. 
-In both cases, as can be seen in Fig.~\ref{fig:knee}, the information loss accelerates once the 1/f knee goes above $\ell \simeq 200$. 
-Recovering large angular scales is clearly important to PMF searches. 
-This is consistent with the study of telescope size in the last paragraph - which found extending to smaller angular scales only helped slightly. 
-It is also consistent with the current upper limits, which are dominated by the BICEP2/Keck Array data at low-$\ell$. 
-As  these large angular scales are also crucial to searches for inflationary gravitational waves, hitting this target should not place new requirements on CMB-S4. 
-The needs of the PMF search are well-aligned with the search for inflationary gravitational waves.
+
+We generally find the forecasts to be insensitive to the 1/f knee or galactic foreground removal at the default beam size of 4$^\prime$. 
+It appears that even in the nearly scale-invariant case, the PMF constraint is being driven by smaller angular scales due to the the degeneracy with the tensor-to-scalar ratio at large angular scales.
+Without this degeneracy, i.e. in the simple \lcdm{}+\apmf{} model, dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 3.2 for a nearly scale-invariant PMF. 
+In this case, the degradation accelerates once the 1/f knee goes above $\ell \simeq 200$. 
+This is consistent with the statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
+For the bluer PMF spectra ($n_b=-1$ or 2), the forecasts have nearly zero dependence on the knee frequency. 
+These results are consistent with the study of telescope size in the last section - which found that recovering smaller angular scales with larger telescopes helped (if one didn't consider cost).
+For a conservative 11-parameter model, our ability to separate a PMF from other physics is coming from sub-degree angular scales. 
+An instrument built to precisely measure gravitational lensing of the CMB should do very well at searching for PMFs.
+
+\subsubsection{Beam and calibration uncertainties}
 

### 2017-01-23 pmf.tex
work on knee freq stuff

@@
   \caption[Map knee dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected as the low-frequency map noise decreases for a nearly scale-invariant PMF ($n_b = -2.9$). 
-  In particular, achieving a map 1/f knee frequency at or below $\ell = 200$ substantially improves the potential power of CMB-S4 PMF searches for nearly scale-invariant PMFs. 
-  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model with $n_B = -2.9$. 
-  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
-  The x-axis is the map noise knee (see eqn.~\ref{eqn:knee}) in angular multipoles $\ell$. 
-  As we expect, reducing low-frequency noise would lead to better PMF constraints. 
-      Note however, the dependence on the low-frequency noise quickly disappears as $n_b$ increases (not shown); the improvement across this range of knees is small for $n_B=-1$ and negligible for $n_B=2$.
-
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_b = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, purple line).
+  However,  the achieved map 1/f knee frequency makes no difference to the potential power of CMB-S4 PMF searches in the 11-parameter model (solid, black line). 
+  The change in behavior happens because the 11-parameter model introduces a degeneracy with r that shifts the angular scale of the PMF constraint to sub-degree scales. 
+  The 1/f knee frequency also makes no difference for the bluer PMF templates in either the restricted or full 11-parameter model space (dashed and dash-dotted black lines). 
+   for any value of $n_B$ (black lines). 
     \label{fig:knee}
@@
 Without this degeneracy, i.e. in the simple \lcdm{}+\apmf{} model, dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 3.2 for a nearly scale-invariant PMF. 
-In this case, the degradation accelerates once the 1/f knee goes above $\ell \simeq 200$. 
+In this case, the degradation accelerates once the 1/f knee goes above $\ell \simeq 70$. 
 This is consistent with the statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 

### 2017-01-23 pmf.tex
jk

--- 2017-01-23 pmf.tex
@@
 
-\usepackage[table,usenames,dvipsnames]{xcolor}
+%\usepackage[table,usenames,dvipsnames]{xcolor}
 %\usepackage{amsmath}
@@
 
-\include{number_list}
-
 %
@@
 We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < \upperAplk$ from Planck alone to $\apmf < \upperAall$ for the combined dataset at 95\% CL. 
+We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.35$ for the combined dataset at 95\% CL. 
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
@@
 
-CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or primordial magnetic fields (PMFs) \citep{kosowsky96, seshadri01}.
+CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or a primordial magnetic field (PMF) \citep{kosowsky96, seshadri01}.
 Both effects lead to the rotation of E-modes into B-modes. 
 By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
-It is therefore common to simply quote effective limits on PMFs. 
+We will therefore simply quote effective limits on a PMF. 
 In this work, we present new upper limits from current CMB polarization data on the possibility of a PMF or parity-violating physics.
 
-Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for a review, see][]{ryu12, widrow12}. 
-There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although there are alternative explanations \citep{broderick12}. 
+Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
+There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
 High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
-These pairs should later annihilate  at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
-Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
-If due to intergalactic magnetic fields, the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
+These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
+The missing flux could be explained by the deflection of particles due to intergalactic magnetic fields. 
+If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
 
 The mechanism to create large-scale magnetic fields, especially in intergalactic space, remains unclear. 
-One popular proposal is that the observed fields are the product of PMFs, which are predicted by several theories of the early Universe \citep[e.g.,][]{turner88, grasso98,ichiki06}. 
-Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed PMFs into the stronger fields observed today. 
-Of course, this amplification process may be seeded through other means, such as AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
+One popular proposal is that the observed fields are the product of primordial magnetic fields, which are predicted by several theories of the early Universe \citep[e.g.,][]{turner88, grasso98,ichiki06}.
+Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed fields into the stronger fields observed today. 
+Of course, this amplification process may have a different initial seed; other ideas include AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
 However, the possibility of PMFs opens up the intriguing idea that observations of large-scale magnetic fields may offer insights into the physics of the very early Universe.
@@
 The CMB anisotropies have yielded some of the strongest constraints on PMFs and are the focus of this work.
-There have been three recent results of note. 
+There have been two recent results of note. 
 \citet{planck15-19} have used the \planck{} 2015 release of temperature and polarization data to set limits on a variety of PMF models. 
@@
 The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < 3.9$\,nG. 
-Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{keisler15,bicepkeck15}, 
-and \citet{zucca16} reported constraints from the combination of the \planck{}  and \sptpol{} bandpowers. 
-In this paper, we will combine the data from all four experiments to determine upper limits on PMFs, and find that the \bicepkeck{} data in particular improves these upper limits. 
-We then present Fisher matrix forecasts on PMF models for the stage-III and stage-IV CMB experiments being built or designed right now.
+Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{keisler15,bicepkeck15}.
+In this paper, we will combine the data from all four experiments to determine simple limits on the PMF, and then examine Fisher matrix forecasts on PMF models from the stage-III and stage-IV CMB experiments being built or designed right now.
 
-The outline of this paper is as follows. 
-In \S\ref{sec:data}, we lay out the data and how we use the data to put limits on PMFs. 
+The outline of the paper is as follows. 
+In \S\ref{sec:data}, we lay out the data used and the MCMC implementation used to constrain the PMF amplitude. 
 We present the results of this analysis on current data in \S\ref{sec:results}. 
-In \S\ref{sec:forecasts}, we forecast constraints from future experiments using a Fisher matrix formulism. 
+The assumed parameters for future experiments and the resulting Fisher matrix forecasts are described in \S\ref{sec:forecasts}. 
 We conclude in \S\ref{sec:conclusions}.
@@
 We do not however require consistency between these foreground models since the data don't have identical flux cuts for extragalactic sources and so on. 
-%In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength. 
+In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength. 
 These data are plotted against the expected B-mode power spectrum for the standard cosmological model in Fig.~\ref{fig:pmf-experiments}.
@@
 
-For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF.
+For the real data, unless noted, we assume the six parameter spatially flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF.
 We adopt flat priors on all parameters. 
@@
 The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
-The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_b k^{n_b}$, with $n_b$ the spectral index and $A_b$ the PMF power. 
-We can translate the power, $A_b$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
+We use the CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}  to do this calculation. 
+The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_b k^{n_b}$. 
+Here $n_b$ is the spectral index of PMF and $A_b$ is its amplitude. 
+We can translate the amplitude, $A_b$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
 Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
@@
 Given that we are still in the era of upper limits,  we do not explore the full 3-dimensional PMF parameter space in this work. 
-Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$.
-We also look at $n_b=-1$ and $n_b=2$ in the forecasting section. 
-We have compared calculated templates to the outputs of the earlier CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}, and find excellent agreement as would be hoped.
-The decision to use the  \citet{zucca16} code instead of CMBACT was based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
-The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
+Instead, we use CMBACT to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$. 
+This template includes tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
 We expect the missing scalar power to degrade the \planck-only results in this work.
-However the missing scalar power should be  unimportant for the EE and BB spectra that are driving the tightest constraints, particularly when looking at forecasts for the next generation of experiments.
-The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
-In the MCMC, we add a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
+However the missing scalar power should be  unimportant for the EE and BB spectra that are driving the tightest constraints. 
+This template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
+We fit for a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
 We can translate the amplitude constraint on this template to a constraint on the rms magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
@@
   The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
-  The dashed purple line shows the nearly-scale invariant ($n_b=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
+  The dashed purple line shows the PMF template used in this work, scaled to \apmf{} = 0.2 to match the gravitational wave signal. 
   As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
@@
 
-\begin{figure}[htb]\centering
-\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
-  \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
-  How the expected PMF changes with the spectral index, $n_B$. 
-  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
-  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
-  }
-\end{figure}
-
 \section{Results}
@@
 We find the addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement. 
-With Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$. 
+With Planck alone, the 95\% confidence upper limit is $\apmf <  0.73$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  0.35$. 
 We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}. 
-Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity). 
-In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments. 
-We test which datasets are important by adding single datasets to the \planck{} set while allowing \alens{} to float, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicepalens$) and \sptpol{} ($\apmf <  \upperAsptpolalens$) B-mode power spectrum measurements.
+Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a preference for \alens{} above unity). 
+In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  0.68$, dropping to $\apmf <  0.27$ with the ground-based experiments. 
+We test which datasets are important by adding single datasets to the \planck{} set while allowing \alens{} to float, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  0.28$) and \sptpol{} ($\apmf <  0.42$) B-mode power spectrum measurements.
 The other datasets do not have a large impact on the observed limits. 
-In short, the reduction in the allowed upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_b=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
+In short, the reduction in the allowed upper limit on \apmf{} is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
 
@@
 We therefore importance sample the chains to generate a flat prior on \bpmf. 
-We find a 95\% limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-This is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
-The difference is due to a difference in the calculated tensor PMF power (for the same parameters) between the XXX and YYY codes. 
-Using the YYY code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
-Returning to the XXX code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
+We find a 95\% limit of $\bpmf < 2.0$\,nG for \planck{} alone, completely consistent with \citep{planck15-19} who found $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
+This is only slightly reduced to $\bpmf < 1.9$\,nG for the combined dataset. 
 The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero. 
-%We also stress that this should not be treated as a robust limit as the tensor PMF modes are crucial to the improvement, and the assumed scaling has not been tested for the tensor PMF. 
-%We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
-These results are inconsistent (being higher) with the equivalent \planck{} + \sptpol{} upper limit quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
+We also stress that this should not be treated as a robust limit as the tensor PMF modes are crucial to the improvement, and the assumed scaling has not been tested for the tensor PMF. 
+We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
 
@@
 \hline
-\lcdm{} + \apmf{} &  $< \upperAall$ & - & - \\
-~~~+\alens{} & $< \upperAallalens$ &$ \medAlensall \pm  \sigmaAlensall$ &  -\\
-~~~+\alens{}+r&  $< \upperAallalensr$&$ \medAlensRall \pm  \sigmaAlensRall$ & $<\upperRall$\\ 
+\lcdm{} + \apmf{} &  $< 0.35$ & - & - \\
+~~~+\alens{} & $< 0.27$ &$ 1.131 \pm  0.061$ &  -\\
+~~~+\alens{}+r&  $< 0.24$&$ 1.133 \pm  0.062$ & $<0.056$\\ 
 \end{tabular}
 \tablecomments{ 
-In the minimal model, \lcdm{} + \apmf{}, current CMB power spectra data from \planck, POLARBEAR, SPTpol, and \bicepkeck{} place a 95\% CL upper limit on the PMF power of $\apmf < \upperAall$. 
+In the minimal model, \lcdm{} + \apmf{}, current CMB power spectra data from \planck, POLARBEAR, SPTpol, and \bicepkeck{} place a 95\% CL upper limit on the PMF power of $\apmf < 0.35$. 
 This limit tightens slightly if tensor modes are allowed (r), or the amount of lensing is allowed to vary. 
@@
 
-The sensitivity of CMB experiments is increasing rapidly due to the continuing growth in the number of detectors. 
+The sensitivity of CMB experiments is increasing rapidly due to the exponential growth in detector counts. 
 \citet{abazajian16} thus defines four stages of CMB experiments. 
 The current experiments (i.e.~the ones used for PMF constraints in the last section) are classified as Stage II experiments. 
-Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{benson14,suzuki16,henderson16} have approximately ten times more detectors, and generically will start collecting data around 2017 and finish three to four years later.
-In this section, we forecast the expected constraints from the EE and BB power spectrum measurements  of the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
+Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{benson14,suzuki16,henderson16} have approximately ten times more detectors, and generically will start collecting data in 2017 and finish in 2020-21.
+In this section, we forecast the expected constraints from EE and BB power spectrum measurements  of the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
 There is also a proposal to build a stage IV experiment, CMB-S4,  that would increase the detector counts by another order of magnitude and hopefully begin taking data in the early 2020s.
-A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016. 
 We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are important to maximize the recovered information on PMFs.
@@
 We do the opposite for the EE and BB spectra. 
-We do not include \planck{} BB information in any forecast, and  we throw away \planck{} EE data in the overlap region by appropriately increasing the \planck{} EE uncertainties. 
+We do not include \planck{} BB information in any forecast, and  we throw away \planck{} EE data in the overlap region by appropriately increasing the forecasted \planck{} EE uncertainties. 
 %The exact increase depends on the assumed stage III or IV survey area.
-We ignore overlaps between the stage III  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
-This is also why we do not include both Simons Array and AdvACTpol as the two experiments are likely to have substantial sky overlap. 
-The overlapping sky coverage is expected to be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
-This prior is only relevant in practice when the assumed CMB-S4 configuration has a larger beam size than SPT-3G. 
+We ignore overlaps between the stage III  with the note that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
+The overlapping sky coverage will probably be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
 With these measures, no modes should be double-counted in this analysis.
@@
 The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
-This 11-parameter model is our default cosmological model for forecasting future PMF constraints. 
+This 11-parameter model is our default cosmological model for forecasting PMF constraints. 
 We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is with the tensor-to-scalar ratio, r. 
@@
 In both cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources.
-We assume the galactic foregrounds are removed by a judicious combination of data from multiple frequencies.
 
@@
 The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_b=-2.9$). 
-This is consistent with, although somewhat better than, the upper limits from the real data).  
-Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty by an order of magnitude in this 7-parameter model to $\sigma(\apmf)=0.015$. 
-The improvement is larger when including all eleven parameters, as the parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while only weakening the stage III constraint by a  more modest 40\%.
-Thus within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
-The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
-$n_b=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
-The improvement for the CMB-S3 experiments over \planck{} remains impressive at a factor of 17 and 13 respectively. 
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=0.47$ (this is consistent with, although slightly worse than, the upper limits from the real data).  
+Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty nearly 400-fold in this 7-parameter model to $\sigma(\apmf)=0.0012$. 
+Including all eleven parameters marginally weakens the \planck+\ho{} constraints on \apmf{} by 23\%, and the stage III constraint by a substantial factor of 2.5. 
+Even within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,180 to  $\sigma(\apmf)=0.0031$. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
 We look at four aspects of the experiment design: the telescope size or beam FWHM, the low-$\ell$ noise performance (1/f knee),  the choice of survey area, and how well the beam size and calibration must be known.
-Of these four, we find that the first three, the beam FWHM, low-$\ell$ noise performance and survey area, to be potentially important to searches for PMFs. 
-As should be expected, the preferred design depends on the shape of the PMF spectrum ($n_B$) which controls  the relative power between large and small angular scales.
+Of these four, we find that the low-$\ell$ noise performance and survey area are important to searches for PMFs.
 
 Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
-We find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered: a beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
-
-However, larger telescopes are also more expensive to build which means for a fixed experimental budget, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
+However, larger telescopes are also more expensive to build which means at fixed cost, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
+We find the gains due to resolution at fixed mapping speed to be negligible: a beam size of FWHM=1$^\prime$ yields only a 1\% better limit than a FWHM of 10$^\prime$. 
+This illustrates how important the large angular scales are to the PMF limits. 
 We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin{} for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin{} for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin{} for a FWHM of 1$^\prime$.
-We find 
-Improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_b = -2.9, -1, +2$ respectively.
-However the results are close enough that the crudeness of the cost-neutral estimates used here could be a factor, and the preference might flip for more accurately costed setups. 
-In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one would lean towards adding more detectors. 
-Raw sensitivity is important to an experiment's ability to study PMFs.
-
-\begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
-  \caption[Area dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
-  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
-  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
-  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
-  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
-  In both cases, better limits on PMFs will be achieved with wider surveys.
-    \label{fig:area}
-  }
-\end{figure}
-A second question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-As shown in  Fig.~\ref{fig:area}, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
-A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
-With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and improve by another factor of 1.4-1.5 by going to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
-
-\tbd{got to here}
+In this quasi-cost-neutral setup, there is a strong preference to go for more detectors over better angular resolution: the uncertainty was a factor of 2.5 times smaller in the coarse case over the FWHM=1$^\prime$ case.
+Raw sensitivity is more important than angular resolution to an experiment's ability to study PMFs.
 
@@
   \caption[Map knee dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected as the low-frequency map noise decreases for a nearly scale-invariant PMF ($n_b = -2.9$). 
-  In particular, achieving a map 1/f knee frequency at or below $\ell = 200$ substantially improves the potential power of CMB-S4 PMF searches for nearly scale-invariant PMFs. 
-  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model with $n_B = -2.9$. 
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected as the low-frequency map noise decreases.  
+  In particular, achieving a map 1/f knee frequency at or below $\ell = 200$ substantially improves the potential power of CMB-S4 PMF searches. 
+  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
   The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
@@
   As we expect, reducing low-frequency noise would lead to better PMF constraints. 
-      Note however, the dependence on the low-frequency noise quickly disappears as $n_b$ increases (not shown); the improvement across this range of knees is small for $n_B=-1$ and negligible for $n_B=2$.
-
     \label{fig:knee}
@@
 
+\begin{figure}[htb]\centering
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
+  \caption[Area dependence]{
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
+  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
+  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
+  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
+  In both cases, better limits on PMFs will be achieved with wider surveys.
+    \label{fig:area}
+  }
+\end{figure}
+A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
+As shown in  Fig.~\ref{fig:area}, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
+A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
+With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and improve by another factor of 1.4-1.5 by going to the 70\% of the sky (the widest area likely to be possible after galactic cuts).
+
 Finally, we consider if searches for PMFs introduce new requirements on the accuracy to which the instrumental beam or overall calibration of an experiment must be known. 
-We find they do not. 
 We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
 We find negligible, sub-percent shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
-The PMF constraints  for all three power law indices considered are insensitive to the beam and calibration uncertainties.
+The PMF constraints are insensitive to the beam and calibration uncertainties.
 
@@
 In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB B-mode polarization data. 
-By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
+By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < 0.73$ to $\apmf < 0.35$. 
 The biggest contributor to this improvement is the low-$\ell$ data from \bicepkeck{}.

### 2017-01-23 pmf.tex

--- 2017-01-23 pmf.tex
@@
 High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
-These pairs should later annihilate  at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
-Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
-If due to intergalactic magnetic fields, the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
+These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
+The missing flux could be explained by the deflection of particles due to intergalactic magnetic fields. 
+If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
 

### 2017-01-25 pmf.tex
Added section for number of detectors. Added placeholder figure for number of detectors vs uncertainty on Apmf. Rewrote caption for fsky vs uncertainty on Apmf.

@@
 
+\subsubsection{Number of detectors}
+
+\begin{figure}[htb]\centering
+\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_area.pdf}
+  \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}
+  How the expected PMF changes with the spectral index, $n_B$. 
+  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
+  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
+  }
+\end{figure}
+
 \subsubsection{Telescope size}
@@
   \caption[Area dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
-  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+  The forecasted uncertainty on the PMF power depends on the assumed PMF model.
+  In the scale-invariant $n_b = -2.9$ case, we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches.
+  In contrast, for the cases where $n_b = -1, +2$, we find that observing at least $\sim$\,10\% of the sky produces the best results for PMF searches.
+%However inreasing the survey area from this minimum area gradually reduces precision, but these effects may be negligible.
+%  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
+%  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches.
   Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
@@
   The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
-  In both cases, better limits on PMFs will be achieved with wider surveys.
+  At best, better limits on PMFs will be achieved with widers surveys and at worst wider surveys will have negligible impact on the precision.
+%  In both cases, better limits on PMFs will be achieved with wider surveys.
   \tbd{may change strength of statements; haven't updated figure or caption}

### 2017-01-25 pmf.tex
more fig updates
plot updates

@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
+\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates_nb.pdf}
   \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
   How the expected PMF changes with the spectral index, $n_B$. 
-  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
-  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
+  The lensing B-mode power spectrum (solid, black line) are plotted against the PMF power for $n_B=-2.9$ (solid, purple line), $n_B=-1$ (dashed, green line), and $n_B=+2$ (dotted, red line). 
+  To keep all the curves on the same scale, we adjust the RMS strength of the magnetic field, \bpmf{}, between the three cases as noted in the legend. 
+  At fixed RMS magnetic field strength, increasing $n_B$ greatly increases the expected B-mode power. 
+  There is an inflection point between the nearly-scale-invariant PMF with $n_b=-2.9$ and the bluer PMF spectra ($n_b=-1$ or 2) which shifts power to smaller angular scales. 
   }
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_area.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_sens.pdf}
   \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}

### 2017-01-30 pmf.tex
numbers

@@
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments. 
-We test which datasets are important by adding single datasets to the \planck{} set while allowing \alens{} to float, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicepalens$) and \sptpol{} ($\apmf <  \upperAsptpolalens$) B-mode power spectrum measurements.
+We test which datasets are important by adding single datasets to the \planck{} set in the simple \lcdm{}+\apmf{} cosmology, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicep$) and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements.
 The other datasets do not have a large impact on the observed limits. 

### 2017-01-30 pmf.tex
updated captions

@@
   \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}
-  How the expected PMF changes with the spectral index, $n_B$. 
-  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
-  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
+  How the expected uncertainty on the PMF power scales with the polarized map noise. 
+  Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
+  The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
+  The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the 11-parameter model due a degeneracy with the tensor-to-scalar ratio. 
+  The PMF constraints improve rapidly with lower noise levels in all three cases up to $\sim$\,1\,\ukarcmin. 
     }
@@
   \caption[Area dependence]{
-  The forecasted uncertainty on the PMF power depends on the assumed PMF model.
-  In the scale-invariant $n_b = -2.9$ case, we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches.
-  In contrast, for the cases where $n_b = -1, +2$, we find that observing at least $\sim$\,10\% of the sky produces the best results for PMF searches.
-%However inreasing the survey area from this minimum area gradually reduces precision, but these effects may be negligible.
-%  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
-%  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches.
-  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
-  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
-  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
-  At best, better limits on PMFs will be achieved with widers surveys and at worst wider surveys will have negligible impact on the precision.
-%  In both cases, better limits on PMFs will be achieved with wider surveys.
-  \tbd{may change strength of statements; haven't updated figure or caption}
+  The preferred survey area for PMF searches depends on the PMF spectral index. 
+    In the scale-invariant $n_b = -2.9$ case (solid line), we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+ In contrast, for the cases where $n_b = -1, +2$ (dashed and dot-dashed lines), we find that observing  $\sim$\,10\% of the sky produces the best PMF constraints. 
+   There is essentially no difference to the preferred areas between the 11-parameter cosmological model (black) or the restricted \lcdm{}+\apmf{} 7-parameter model (purple). 
+     Fortunately, the minima for all three templates are relatively broad, and a survey covering 15+\% of the sky will do well for all values of the PMF spectral index. 
     \label{fig:area}
@@
 
-\tbd{may change strength of statements}
 A second question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-Unsurprisingly, we find opposing preferences for the scale-invariant $n_b=-2.9$ (which peaks at large scales) and very blue $n_b=2$ spectrum peaking at small scales. 
-We find very little dependence on area for the intermediate case of $n_b=-1$. 
-As shown in  Fig.~\ref{fig:area}, for $n_b=-2.9$, observing at least 15\% of the sky is very important to a PMF search, and it is best  to cover as much sky as possible. 
+Unsurprisingly, we find opposing preferences for the scale-invariant $n_b=-2.9$ (which peaks at large scales) and the bluer $n_b=-1$ or 2 spectra peaking at small scales. 
+As shown in  Fig.~\ref{fig:area}, for $n_b=-2.9$, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
 A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
 With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and are nearly flat (a 6\% improvement) from 25\% to 70\% of the sky (the widest area likely to be possible after galactic cuts).
-Conversely, $n_b=+2$, the optimal survey area is as small as possible. 
+Conversely, $n_b=+2$, the optimal survey area is smaller at 10\%. 
 Note however that the minimum is extremely broad with only a 10\% worsening of the expected uncertainty as the survey area is increased from 10\% to 70\% of the  full sky. 
-The optimal survey area for a PMF survey will depend on the targeted PMF models.
+A survey of around 25\% of the sky would perform well for all three considered PMF models.
 

### 2017-01-30 pmf.tex
beam plot

@@
 \includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_sens.pdf}
-  \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}
+  \caption[]{ \label{fig:ndetector}
   How the expected uncertainty on the PMF power scales with the polarized map noise. 
@@
 
+\begin{figure}[htb]\centering
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_beam.pdf}
+  \caption[]{ \label{fig:beam}
+ Larger telescopes (and smaller beams) will improve limits on the PMF power. 
+ Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
+  The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
+  The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
+    }
+\end{figure}
+
 Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
-We find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered: a beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
+As shown in Fig.~\ref{fig:beam}, we find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered.
+ A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
 
@@
 In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB B-mode polarization data. 
-By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
+By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
 The biggest contributor to this improvement is the low-$\ell$ data from \bicepkeck{}.
@@
 We have also shown that the next generation of experiments should dramatically reduce these limits, and potentially detect PMFs for the first time. 
-These so-called stage III experiments, which will begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.0062$ even after marginalizing over a five-parameter extension to \lcdm.
+These so-called stage III experiments, which will begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a five-parameter extension to \lcdm.
 
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0008$, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.001$, i.e.~ a six-fold improvement over the forecasts for the stage III experiments and a 330-fold improvement over the current limits.
-These experiments will be very exciting probes of PMFs and other sources of cosmic birefringence.
+We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.00025$, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.006$, i.e.~ a three-fold improvement over the forecasts for the stage III experiments and a 37-fold improvement over the current limits.
+We consider how the design of these experiments will impact the resulting PMF limits -- the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties -- and find sensitivity followed by telescope size to be the most important factors in predicting the PMF limits.
+CMB-S4 will be a very exciting probe of PMFs and other sources of cosmic birefringence.
 

### 2017-01-30 pmf.tex
noise section

@@
 Given that CMB-S4 is still being designed, it is worthwhile to consider how design decisions will affect the final PMF constraints. 
-We look at four aspects of the experiment design: the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
-Of these four, we find that the first three, the beam FWHM, low-$\ell$ noise performance and survey area, to be potentially important to searches for PMFs. 
+We look at five aspects of the experiment design: the instrumental sensitivity (as reflect by the map noise level), the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
+Of these five, we find that the first two to be very important and the second two to be somewhat important when optimizing for searches for PMFs. 
 As should be expected, the preferred design depends on the shape of the PMF spectrum ($n_B$) which controls  the relative power between large and small angular scales.
 
-\subsubsection{Number of detectors}
+\subsubsection{Instrumental sensitivity (map noise levels)}
+
+We naturally expect more sensitive instruments to do a better job of constraining PMF models. 
+The goal of this section is to quantify that statement for the three PMF templates considered in the 11 or 7-parameter cosmological models. 
+Our results are shown in Fig.~\ref{fig:sensitivity}. 
+For this figure, we have fixed the rest of the experimental configuration (i.e.~everything except the polarized noise levels) to the values of the CMB-S4 row in Table~\ref{tab:experiments}. 
+Clearly, continuing to improve the sensitivity of CMB experiments to CMB-S4 and beyond will be a boon to PMF searches. 
+In the general, 11-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered till the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
 
@@
 \includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_sens.pdf}
-  \caption[]{ \label{fig:ndetector}
+  \caption[]{ \label{fig:sensitivity}
   How the expected uncertainty on the PMF power scales with the polarized map noise. 
@@
 
-\subsubsection{Telescope size}
+\subsubsection{Size of Telescope }
 
@@
 
-\subsubsection{Fidelity at large angular scales}
+\subsubsection{Noise performance at large angular scales}
 

### 2017-01-30 pmf.tex
beam section

@@
   The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
+  The plateau near 4$^\prime$ for $n_B=-1, +2$ is where the gain from the $\ell\sim3000$ peak is saturated, but the resolution isn't yet adequate to pick up the next peak at $\ell > 8000$ (see  Fig.~\ref{fig:pmf-nb}).
     }
@@
 As shown in Fig.~\ref{fig:beam}, we find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered. 
+We find a local plateau between FWHMs of 4$^\prime$ to 6$^\prime$; improving the angular resolution in this range does not aid PMF searches. 
+We can understand this plateau by looking on the predicted PMF power in Fig.~\ref{fig:pmf-nb}. 
+All three templates have two peaks across this range of angular multiples, and we would expect such a plateau when, for instance, the resolution is adequate to resolve the first peak, but not yet sufficient to resolve the second peak.
+The observed plateau positions are consistent with this hypothesis. 
  A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
+   The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant.
 

### 2017-01-30 pmf.tex
started sec 4.4.1

--- 2017-01-30 pmf.tex
@@
 
+Between each stage of ground-based CMB experiment, the number of detectors increases by an order of magnitude.
+Adding detectors will always reduce the noise in the instrument, making it easier to isolate the PMF signal, thereby reducing the uncertainty on PMF measurements.
+When quantifying the effects of the number of detectors it is more informative to use polarisation noise, as detector count relies on knowing the individual sensitivity of each detector.
+As such, we give our result in terms of polarisation noise, noting that polarisation noise scales with detector count as $\sqrt{N_{detectors}}$
+
+We find that
+
 \begin{figure}[htb]\centering
 \includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_sens.pdf}
-  \caption[]{ \label{fig:ndetector}
+  \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}
   How the expected uncertainty on the PMF power scales with the polarized map noise. 
@@
 
-\begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_beam.pdf}
-  \caption[]{ \label{fig:beam}
- Larger telescopes (and smaller beams) will improve limits on the PMF power. 
- Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
-  The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
-  The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
-    }
-\end{figure}
-
 Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
-As shown in Fig.~\ref{fig:beam}, we find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered.
- A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
+We find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered: a beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
 
@@
 In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB B-mode polarization data. 
-By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
+By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
 The biggest contributor to this improvement is the low-$\ell$ data from \bicepkeck{}.
@@
 We have also shown that the next generation of experiments should dramatically reduce these limits, and potentially detect PMFs for the first time. 
-These so-called stage III experiments, which will begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a five-parameter extension to \lcdm.
+These so-called stage III experiments, which will begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.0062$ even after marginalizing over a five-parameter extension to \lcdm.
 
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.00025$, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.006$, i.e.~ a three-fold improvement over the forecasts for the stage III experiments and a 37-fold improvement over the current limits.
-We consider how the design of these experiments will impact the resulting PMF limits -- the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties -- and find sensitivity followed by telescope size to be the most important factors in predicting the PMF limits.
-CMB-S4 will be a very exciting probe of PMFs and other sources of cosmic birefringence.
+We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0008$, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.001$, i.e.~ a six-fold improvement over the forecasts for the stage III experiments and a 330-fold improvement over the current limits.
+These experiments will be very exciting probes of PMFs and other sources of cosmic birefringence.
 

### 2017-01-30 pmf.tex

--- 2017-01-30 pmf.tex
@@
 
+Between each stage of ground-based CMB experiment, the number of detectors increases by an order of magnitude.
+Adding detectors will always reduce the noise in the instrument, making it easier to isolate the PMF signal, thereby reducing the uncertainty on PMF measurements.
+When quantifying the effects of the number of detectors it is more informative to use polarisation noise, as detector count relies on knowing the individual sensitivity of each detector.
+As such, we give our result in terms of polarisation noise, noting that polarisation noise scales with detector count as $\sqrt{N_{detectors}}$
+
+We find that
+
 \begin{figure}[htb]\centering

### 2017-01-30 pmf.tex
commited edits

--- 2017-01-30 pmf.tex
@@
 We also forecast the expected future limits from soon-to-deploy CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB-S4 experiment. 
-Future CMB experiments should dramatically reduce the current uncertainties, by two orders of magnitude for the near-term experiments and three orders of magnitude for the CMB-S4 experiment. 
+Future CMB experiments should dramatically reduce the current uncertainties, by one order of magnitude for the near-term experiments and two orders of magnitude for the CMB-S4 experiment. 
 The constraints from CMB-S4 have the potential to rule out much of the parameter space for PMFs.
@@
 One popular proposal is that the observed fields are the product of PMFs, which are predicted by several theories of the early Universe \citep[e.g.,][]{turner88, grasso98,ichiki06}. 
-Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed PMFs into the stronger fields observed today. 
+Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed PMFs into the stronger magnetic fields observed today. 
 Of course, this amplification process may be seeded through other means, such as AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
@@
 The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
-The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_b k^{n_b}$, with $n_b$ the spectral index and $A_b$ the PMF power. 
-We can translate the power, $A_b$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
+The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_B k^{n_B}$, with $n_B$ the spectral index and $A_B$ the PMF power normalization. 
+We can translate the power, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
 Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
@@
 Given that we are still in the era of upper limits,  we do not explore the full 3-dimensional PMF parameter space in this work. 
-Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$.
-We also look at $n_b=-1$ and $n_b=2$ in the forecasting section. 
-We have compared calculated templates to the outputs of the earlier CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}, and find excellent agreement as would be hoped.
-The decision to use the  \citet{zucca16} code instead of CMBACT was based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
+Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_B$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$.
+We also look at $n_B=-1$ and $n_B=2$ in the forecasting section. 
+We have compared calculated templates to the outputs of the earlier CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
+We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
+The decision to use the  \citet{zucca16} code instead of CMBACT is based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
-We expect the missing scalar power to degrade the \planck-only results in this work.
-However the missing scalar power should be  unimportant for the EE and BB spectra that are driving the tightest constraints, particularly when looking at forecasts for the next generation of experiments.
+The lack of scalar terms should only matter for constraints primarily from the temperature spectrum, i.e. the \planck-only results. 
+These temperature results are not the main focus of this work, and we find our results consistent with the \planck{} results from \citet{planck15-19} suggesting the impact is minor. 
 The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
@@
     The data sets are from POLARBEAR (black; \citet{polarbear14b}); ACTpol (dark green; \citet{naess14});  BICEP2/Keck Array (red; \citet{bicepkeck15}); and SPTpol (purple; \citet{keisler15}). 
-      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments is expected to significantly increase the signal-to-noise on the B-mode power spectrum.
+      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments will significantly increase the signal-to-noise on the B-mode power spectrum. 
            \label{fig:pmf-experiments}
@@
   The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
-  The dashed purple line shows the nearly-scale invariant ($n_b=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
+  The dashed purple line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
   As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
@@
   At fixed RMS magnetic field strength, increasing $n_B$ greatly increases the expected B-mode power. 
-  There is an inflection point between the nearly-scale-invariant PMF with $n_b=-2.9$ and the bluer PMF spectra ($n_b=-1$ or 2) which shifts power to smaller angular scales. 
+  There is an inflection point between the nearly-scale-invariant PMF with $n_B=-2.9$ and the bluer PMF spectra ($n_B=-1$ or 2) which shifts power to smaller angular scales and eliminates the peak at $\ell \lesssim 200$.
   }
@@
 The other datasets do not have a large impact on the observed limits. 
-In short, the reduction in the allowed upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_b=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
+In short, the reduction in the allowed upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
 
@@
 This is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
-The difference is due to a difference in the calculated tensor PMF power (for the same parameters) between the XXX and YYY codes. 
-Using the YYY code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
-Returning to the XXX code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
+The difference is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT and \citet{zucca16} codes. 
+Using the CMBACT code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
+Returning to the  \citet{zucca16} code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
 The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero. 
@@
 
+\tbd{Add other nb cases???}
+
 \section{Forecasts}
@@
 
-The sensitivity of CMB experiments is increasing rapidly due to the continuing growth in the number of detectors. 
+The sensitivity of CMB experiments is increasing rapidly due to the continued growth in the number of detectors. 
 \citet{abazajian16} thus defines four stages of CMB experiments. 
@@
 A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016. 
-We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are important to maximize the recovered information on PMFs.
+We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are most important to PMF searches.
 
@@
 
-We use Fisher matrices to forecast the constraints on PMFs possible from each generation of experiment. 
+We use Fisher matrices to forecast the potential constraints on PMFs possible for each generation of experiments. 
 The Fisher matrix, $\mathcal{F}_{ij}$, can be defined as:
@@
 for parameters, p. 
-The inverse of the Fisher matrix will be the covariance matrix for the parameters. 
+The inverse of the Fisher matrix is the covariance matrix for the parameters for Gaussian likelihoods. 
 While Fisher matrices underestimate the true uncertainties for non-Gaussian likelihoods \citep[see e.g.,][]{wolz12}, they 
@@
 %The exact increase depends on the assumed stage III or IV survey area.
-We ignore overlaps between the stage III  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
+We ignore overlaps between the stage-III experiments  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
 This is also why we do not include both Simons Array and AdvACTpol as the two experiments are likely to have substantial sky overlap. 
@@
 This prior is only relevant in practice when the assumed CMB-S4 configuration has a larger beam size than SPT-3G. 
-With these measures, no modes should be double-counted in this analysis.
+With these measures in place, this analysis should not double-count any modes.
 
@@
 The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
+Here, r is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species. 
 This 11-parameter model is our default cosmological model for forecasting future PMF constraints. 
-We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is with the tensor-to-scalar ratio, r. 
-The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and PMFs is nearly identical. 
+We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B=-2.9$ case with the tensor-to-scalar ratio, r. 
+The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B=-2.9$ is nearly identical. 
 To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
@@
 The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_b=-2.9$). 
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_B=-2.9$). 
 This is consistent with, although somewhat better than, the upper limits from the real data).  
@@
 The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
-$n_b=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
+$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
 The improvement for the CMB-S3 experiments over \planck{} remains impressive at a factor of 17 and 13 respectively. 
@@
 
-The primary motivation behind the proposed CMB stage IV experiment commonly called CMB-S4 is to search for inflationary gravitational waves and neutrino masses, however, the experiment should also enable extremely sensitive searches for PMFs.
-We look at the prospects for these searches using the polarization information (EE and BB power spectra) from CMB-S4. 
-We begin by making forecasts for the fiducial CMB-S4 configuration as laid out in Table~\ref{tab:experiments}, and then consider how changing the experimental design would impact the expected uncertainties.
+The primary motivation behind the proposed CMB stage-IV experiment commonly called CMB-S4 is to search for inflationary gravitational waves and neutrino masses.
+However, CMB-S4 would also enable extremely sensitive searches for PMFs. 
+We begin by considering our fiducial CMB-S4 configuration, as laid out in Table~\ref{tab:experiments}. 
+For this fiducial configuration, we expect \tbd{add numbers}.
 
-\subsection{Survey considerations for Stage IV}
-
-Given that CMB-S4 is still being designed, it is worthwhile to consider how design decisions will affect the final PMF constraints. 
-We look at five aspects of the experiment design: the instrumental sensitivity (as reflect by the map noise level), the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
+Given that CMB-S4 is currently in the design phase, it is worthwhile to consider how design decisions will affect the final PMF constraints. 
+We look at five aspects of the experiment design: the instrumental sensitivity (as reflected by the map noise level), the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
 Of these five, we find that the first two to be very important and the second two to be somewhat important when optimizing for searches for PMFs. 
@@
 \subsubsection{Instrumental sensitivity (map noise levels)}
+
+\tbd{I found this awkward text, will rewrite}
 
@@
   The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the 11-parameter model due a degeneracy with the tensor-to-scalar ratio. 
-  The PMF constraints improve rapidly with lower noise levels in all three cases up to $\sim$\,1\,\ukarcmin. 
+  The PMF constraints improve rapidly with lower noise levels in all three cases up to $\sim$\,1\,\ukarcmin, which is close to the  fiducial CMB-S4 noise levels. 
     }
@@
   The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
-  The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
+  The cosmological model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
   The plateau near 4$^\prime$ for $n_B=-1, +2$ is where the gain from the $\ell\sim3000$ peak is saturated, but the resolution isn't yet adequate to pick up the next peak at $\ell > 8000$ (see  Fig.~\ref{fig:pmf-nb}).
@@
 The observed plateau positions are consistent with this hypothesis. 
- A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
+ A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_B=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
    The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant.
@@
 We find 
-Improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_b = -2.9, -1, +2$ respectively.
+Improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_B = -2.9, -1, +2$ respectively.
 However the results are close enough that the crudeness of the cost-neutral estimates used here could be a factor, and the preference might flip for more accurately costed setups. 
-In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one would lean towards adding more detectors. 
-Raw sensitivity is important to an experiment's ability to study PMFs.
+In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one would likely lean towards adding more detectors. 
+%Raw sensitivity is important to an experiment's ability to study PMFs.
 
@@
   The preferred survey area for PMF searches depends on the PMF spectral index. 
-    In the scale-invariant $n_b = -2.9$ case (solid line), we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
- In contrast, for the cases where $n_b = -1, +2$ (dashed and dot-dashed lines), we find that observing  $\sim$\,10\% of the sky produces the best PMF constraints. 
+    In the scale-invariant $n_B = -2.9$ case (solid line), we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+ In contrast, for the cases where $n_B = -1, +2$ (dashed and dot-dashed lines), we find that observing  $\sim$\,10\% of the sky produces the best PMF constraints. 
    There is essentially no difference to the preferred areas between the 11-parameter cosmological model (black) or the restricted \lcdm{}+\apmf{} 7-parameter model (purple). 
@@
 
-A second question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-Unsurprisingly, we find opposing preferences for the scale-invariant $n_b=-2.9$ (which peaks at large scales) and the bluer $n_b=-1$ or 2 spectra peaking at small scales. 
-As shown in  Fig.~\ref{fig:area}, for $n_b=-2.9$, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
+A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
+Unsurprisingly, we find opposing preferences for the scale-invariant $n_B=-2.9$ (which peaks at large angular scales) and the bluer $n_B=-1$ or 2 spectra which peak at small scales. 
+As shown in  Fig.~\ref{fig:area}, for $n_B=-2.9$, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
 A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
 With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and are nearly flat (a 6\% improvement) from 25\% to 70\% of the sky (the widest area likely to be possible after galactic cuts).
-Conversely, $n_b=+2$, the optimal survey area is smaller at 10\%. 
+Conversely, $n_B=-1$or +2, the optimal survey area is smaller at 10\% of the full sky. 
 Note however that the minimum is extremely broad with only a 10\% worsening of the expected uncertainty as the survey area is increased from 10\% to 70\% of the  full sky. 
@@
   \caption[Map knee dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_b = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, purple line).
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, purple line).
   However,  the achieved map 1/f knee frequency makes no difference to the potential power of CMB-S4 PMF searches in the 11-parameter model (solid, black line). 
@@
 The exponent, 8/3, was selected based on a Kolmogorov spectrum of turbulence within a thin plane \citep{lay00}. %lay & halverson 2000. 
-Note that this knob  serves as a placeholder for several effects, including a signal-to-noise hit due to galactic foregrounds or the methods used to clean these foregrounds, atmospheric noise, or actual instrumental 1/f noise.
+Note that this knob  serves as a placeholder for several effects, including a signal-to-noise hit due to galactic foregrounds or the methods used to clean these foregrounds, atmospheric noise, or actual instrumental low frequency noise.
 
@@
 In this case, the degradation accelerates once the 1/f knee goes above $\ell \simeq 70$. 
-This is consistent with the statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
-For the bluer PMF spectra ($n_b=-1$ or 2), the forecasts have nearly zero dependence on the knee frequency. 
+This is consistent with the earlier statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
+For the bluer PMF spectra ($n_B=-1$ or 2), the forecasts have essentially no dependence on the knee frequency. 
 These results are consistent with the study of telescope size in the last section - which found that recovering smaller angular scales with larger telescopes helped (if one didn't consider cost).
 For a conservative 11-parameter model, our ability to separate a PMF from other physics is coming from sub-degree angular scales. 
-An instrument built to precisely measure gravitational lensing of the CMB should do very well at searching for PMFs.
+%An instrument built to precisely measure gravitational lensing of the CMB should do very well at searching for PMFs. 
+The low frequency noise performance of CMB-S4 is not crucial to PMF searches.
 
@@
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.00025$, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.006$, i.e.~ a three-fold improvement over the forecasts for the stage III experiments and a 37-fold improvement over the current limits.
+We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$ \tbd{check these numbers}, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.006$, i.e.~ a three-fold improvement over the forecasts for the stage III experiments and a 37-fold improvement over the current limits.
 We consider how the design of these experiments will impact the resulting PMF limits -- the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties -- and find sensitivity followed by telescope size to be the most important factors in predicting the PMF limits.

### 2017-01-31 pmf.tex
Added description of plasma instabilities...
as an alternative to loss of GeV flux, as an alternative to pmfs.

@@
 Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for a review, see][]{ryu12, widrow12}. 
-There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although there are alternative explanations \citep{broderick12}. 
+There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}.
 High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
@@
 If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
+There are, however, alternative explanations involving plasma instabilities which may result in positron-electron pairs instead depositing their energy into the IGM as heat \citep{broderick12}.
 

### 2017-01-31 pmf.tex
updated experiment plot

--- 2017-01-30 pmf.tex
@@
 We also forecast the expected future limits from soon-to-deploy CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB-S4 experiment. 
-Future CMB experiments should dramatically reduce the current uncertainties, by one order of magnitude for the near-term experiments and two orders of magnitude for the CMB-S4 experiment. 
+Future CMB experiments should dramatically reduce the current uncertainties, by two orders of magnitude for the near-term experiments and three orders of magnitude for the CMB-S4 experiment. 
 The constraints from CMB-S4 have the potential to rule out much of the parameter space for PMFs.
@@
 One popular proposal is that the observed fields are the product of PMFs, which are predicted by several theories of the early Universe \citep[e.g.,][]{turner88, grasso98,ichiki06}. 
-Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed PMFs into the stronger magnetic fields observed today. 
+Adiabatic compression and turbulent shocks during later structure formation amplify these initial seed PMFs into the stronger fields observed today. 
 Of course, this amplification process may be seeded through other means, such as AGN or galactic dynamos \citep[for a review, see][]{giovannini04}. 
@@
 The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
-The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_B k^{n_B}$, with $n_B$ the spectral index and $A_B$ the PMF power normalization. 
-We can translate the power, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
+The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_b k^{n_b}$, with $n_b$ the spectral index and $A_b$ the PMF power. 
+We can translate the power, $A_b$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
 Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
@@
 Given that we are still in the era of upper limits,  we do not explore the full 3-dimensional PMF parameter space in this work. 
-Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_B$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$.
-We also look at $n_B=-1$ and $n_B=2$ in the forecasting section. 
-We have compared calculated templates to the outputs of the earlier CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
-We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
-The decision to use the  \citet{zucca16} code instead of CMBACT is based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
+Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_b$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$.
+We also look at $n_b=-1$ and $n_b=2$ in the forecasting section. 
+We have compared calculated templates to the outputs of the earlier CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}, and find excellent agreement as would be hoped.
+The decision to use the  \citet{zucca16} code instead of CMBACT was based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
-The lack of scalar terms should only matter for constraints primarily from the temperature spectrum, i.e. the \planck-only results. 
-These temperature results are not the main focus of this work, and we find our results consistent with the \planck{} results from \citet{planck15-19} suggesting the impact is minor. 
+We expect the missing scalar power to degrade the \planck-only results in this work.
+However the missing scalar power should be  unimportant for the EE and BB spectra that are driving the tightest constraints, particularly when looking at forecasts for the next generation of experiments.
 The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}. 
@@
     The B-mode measurements used for the limits in this work are denoted with filled circles; data not used has an open circle. 
-    The data sets are from POLARBEAR (black; \citet{polarbear14b}); ACTpol (dark green; \citet{naess14});  BICEP2/Keck Array (red; \citet{bicepkeck15}); and SPTpol (purple; \citet{keisler15}). 
-      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments will significantly increase the signal-to-noise on the B-mode power spectrum. 
+    The data sets are from POLARBEAR (black circles; \citet{polarbear14b}); ACTpol (dark green triangles; \citet{naess14});  BICEP2/Keck Array (red diamonds; \citet{bicepkeck15}); and SPTpol (purple squares; \citet{keisler15}).
+      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments is expected to significantly increase the signal-to-noise on the B-mode power spectrum.
            \label{fig:pmf-experiments}
@@
   The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
-  The dashed purple line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
+  The dashed purple line shows the nearly-scale invariant ($n_b=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
   As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
@@
   At fixed RMS magnetic field strength, increasing $n_B$ greatly increases the expected B-mode power. 
-  There is an inflection point between the nearly-scale-invariant PMF with $n_B=-2.9$ and the bluer PMF spectra ($n_B=-1$ or 2) which shifts power to smaller angular scales and eliminates the peak at $\ell \lesssim 200$.
+  There is an inflection point between the nearly-scale-invariant PMF with $n_b=-2.9$ and the bluer PMF spectra ($n_b=-1$ or 2) which shifts power to smaller angular scales. 
   }
@@
 The other datasets do not have a large impact on the observed limits. 
-In short, the reduction in the allowed upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
+In short, the reduction in the allowed upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_b=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
 
@@
 This is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
-The difference is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT and \citet{zucca16} codes. 
-Using the CMBACT code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
-Returning to the  \citet{zucca16} code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
+The difference is due to a difference in the calculated tensor PMF power (for the same parameters) between the XXX and YYY codes. 
+Using the YYY code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
+Returning to the XXX code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
 The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero. 
@@
 
-\tbd{Add other nb cases???}
-
 \section{Forecasts}
@@
 
-The sensitivity of CMB experiments is increasing rapidly due to the continued growth in the number of detectors. 
+The sensitivity of CMB experiments is increasing rapidly due to the continuing growth in the number of detectors. 
 \citet{abazajian16} thus defines four stages of CMB experiments. 
@@
 A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016. 
-We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are most important to PMF searches.
+We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are important to maximize the recovered information on PMFs.
 
@@
 
-We use Fisher matrices to forecast the potential constraints on PMFs possible for each generation of experiments. 
+We use Fisher matrices to forecast the constraints on PMFs possible from each generation of experiment. 
 The Fisher matrix, $\mathcal{F}_{ij}$, can be defined as:
@@
 for parameters, p. 
-The inverse of the Fisher matrix is the covariance matrix for the parameters for Gaussian likelihoods. 
+The inverse of the Fisher matrix will be the covariance matrix for the parameters. 
 While Fisher matrices underestimate the true uncertainties for non-Gaussian likelihoods \citep[see e.g.,][]{wolz12}, they 
@@
 %The exact increase depends on the assumed stage III or IV survey area.
-We ignore overlaps between the stage-III experiments  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
+We ignore overlaps between the stage III  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
 This is also why we do not include both Simons Array and AdvACTpol as the two experiments are likely to have substantial sky overlap. 
@@
 This prior is only relevant in practice when the assumed CMB-S4 configuration has a larger beam size than SPT-3G. 
-With these measures in place, this analysis should not double-count any modes.
+With these measures, no modes should be double-counted in this analysis.
 
@@
 The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
-Here, r is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species. 
 This 11-parameter model is our default cosmological model for forecasting future PMF constraints. 
-We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B=-2.9$ case with the tensor-to-scalar ratio, r. 
-The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B=-2.9$ is nearly identical. 
+We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is with the tensor-to-scalar ratio, r. 
+The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and PMFs is nearly identical. 
 To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
@@
 The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_B=-2.9$). 
+With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_b=-2.9$). 
 This is consistent with, although somewhat better than, the upper limits from the real data).  
@@
 The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
-$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
+$n_b=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
 The improvement for the CMB-S3 experiments over \planck{} remains impressive at a factor of 17 and 13 respectively. 
@@
 
-The primary motivation behind the proposed CMB stage-IV experiment commonly called CMB-S4 is to search for inflationary gravitational waves and neutrino masses.
-However, CMB-S4 would also enable extremely sensitive searches for PMFs. 
-We begin by considering our fiducial CMB-S4 configuration, as laid out in Table~\ref{tab:experiments}. 
-For this fiducial configuration, we expect \tbd{add numbers}.
+The primary motivation behind the proposed CMB stage IV experiment commonly called CMB-S4 is to search for inflationary gravitational waves and neutrino masses, however, the experiment should also enable extremely sensitive searches for PMFs.
+We look at the prospects for these searches using the polarization information (EE and BB power spectra) from CMB-S4. 
+We begin by making forecasts for the fiducial CMB-S4 configuration as laid out in Table~\ref{tab:experiments}, and then consider how changing the experimental design would impact the expected uncertainties.
 
-Given that CMB-S4 is currently in the design phase, it is worthwhile to consider how design decisions will affect the final PMF constraints. 
-We look at five aspects of the experiment design: the instrumental sensitivity (as reflected by the map noise level), the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
+\subsection{Survey considerations for Stage IV}
+
+Given that CMB-S4 is still being designed, it is worthwhile to consider how design decisions will affect the final PMF constraints. 
+We look at five aspects of the experiment design: the instrumental sensitivity (as reflect by the map noise level), the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
 Of these five, we find that the first two to be very important and the second two to be somewhat important when optimizing for searches for PMFs. 
@@
 \subsubsection{Instrumental sensitivity (map noise levels)}
-
-\tbd{I found this awkward text, will rewrite}
 
@@
   The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the 11-parameter model due a degeneracy with the tensor-to-scalar ratio. 
-  The PMF constraints improve rapidly with lower noise levels in all three cases up to $\sim$\,1\,\ukarcmin, which is close to the  fiducial CMB-S4 noise levels. 
+  The PMF constraints improve rapidly with lower noise levels in all three cases up to $\sim$\,1\,\ukarcmin. 
     }
@@
   The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
-  The cosmological model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
-  The plateau near 4$^\prime$ for $n_B=-1, +2$ is where the gain from the $\ell\sim3000$ peak is saturated, but the resolution isn't yet adequate to pick up the next peak at $\ell > 8000$ (see  Fig.~\ref{fig:pmf-nb}).
+  The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
     }
@@
 As shown in Fig.~\ref{fig:beam}, we find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered.
-We find a local plateau between FWHMs of 4$^\prime$ to 6$^\prime$; improving the angular resolution in this range does not aid PMF searches. 
-We can understand this plateau by looking on the predicted PMF power in Fig.~\ref{fig:pmf-nb}. 
-All three templates have two peaks across this range of angular multiples, and we would expect such a plateau when, for instance, the resolution is adequate to resolve the first peak, but not yet sufficient to resolve the second peak.
-The observed plateau positions are consistent with this hypothesis. 
- A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_B=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
-   The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant.
+ A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
 
@@
 We find 
-Improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_B = -2.9, -1, +2$ respectively.
+Improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_b = -2.9, -1, +2$ respectively.
 However the results are close enough that the crudeness of the cost-neutral estimates used here could be a factor, and the preference might flip for more accurately costed setups. 
-In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one would likely lean towards adding more detectors. 
-%Raw sensitivity is important to an experiment's ability to study PMFs.
+In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one would lean towards adding more detectors. 
+Raw sensitivity is important to an experiment's ability to study PMFs.
 
@@
   The preferred survey area for PMF searches depends on the PMF spectral index. 
-    In the scale-invariant $n_B = -2.9$ case (solid line), we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
- In contrast, for the cases where $n_B = -1, +2$ (dashed and dot-dashed lines), we find that observing  $\sim$\,10\% of the sky produces the best PMF constraints. 
+    In the scale-invariant $n_b = -2.9$ case (solid line), we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+ In contrast, for the cases where $n_b = -1, +2$ (dashed and dot-dashed lines), we find that observing  $\sim$\,10\% of the sky produces the best PMF constraints. 
    There is essentially no difference to the preferred areas between the 11-parameter cosmological model (black) or the restricted \lcdm{}+\apmf{} 7-parameter model (purple). 
@@
 
-A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-Unsurprisingly, we find opposing preferences for the scale-invariant $n_B=-2.9$ (which peaks at large angular scales) and the bluer $n_B=-1$ or 2 spectra which peak at small scales. 
-As shown in  Fig.~\ref{fig:area}, for $n_B=-2.9$, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
+A second question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
+Unsurprisingly, we find opposing preferences for the scale-invariant $n_b=-2.9$ (which peaks at large scales) and the bluer $n_b=-1$ or 2 spectra peaking at small scales. 
+As shown in  Fig.~\ref{fig:area}, for $n_b=-2.9$, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
 A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
 With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and are nearly flat (a 6\% improvement) from 25\% to 70\% of the sky (the widest area likely to be possible after galactic cuts).
-Conversely, $n_B=-1$or +2, the optimal survey area is smaller at 10\% of the full sky. 
+Conversely, $n_b=+2$, the optimal survey area is smaller at 10\%. 
 Note however that the minimum is extremely broad with only a 10\% worsening of the expected uncertainty as the survey area is increased from 10\% to 70\% of the  full sky. 
@@
   \caption[Map knee dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, purple line).
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_b = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, purple line).
   However,  the achieved map 1/f knee frequency makes no difference to the potential power of CMB-S4 PMF searches in the 11-parameter model (solid, black line). 
@@
 The exponent, 8/3, was selected based on a Kolmogorov spectrum of turbulence within a thin plane \citep{lay00}. %lay & halverson 2000. 
-Note that this knob  serves as a placeholder for several effects, including a signal-to-noise hit due to galactic foregrounds or the methods used to clean these foregrounds, atmospheric noise, or actual instrumental low frequency noise.
+Note that this knob  serves as a placeholder for several effects, including a signal-to-noise hit due to galactic foregrounds or the methods used to clean these foregrounds, atmospheric noise, or actual instrumental 1/f noise.
 
@@
 In this case, the degradation accelerates once the 1/f knee goes above $\ell \simeq 70$. 
-This is consistent with the earlier statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
-For the bluer PMF spectra ($n_B=-1$ or 2), the forecasts have essentially no dependence on the knee frequency. 
+This is consistent with the statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
+For the bluer PMF spectra ($n_b=-1$ or 2), the forecasts have nearly zero dependence on the knee frequency. 
 These results are consistent with the study of telescope size in the last section - which found that recovering smaller angular scales with larger telescopes helped (if one didn't consider cost).
 For a conservative 11-parameter model, our ability to separate a PMF from other physics is coming from sub-degree angular scales. 
-%An instrument built to precisely measure gravitational lensing of the CMB should do very well at searching for PMFs. 
-The low frequency noise performance of CMB-S4 is not crucial to PMF searches.
+An instrument built to precisely measure gravitational lensing of the CMB should do very well at searching for PMFs.
 
@@
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$ \tbd{check these numbers}, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.006$, i.e.~ a three-fold improvement over the forecasts for the stage III experiments and a 37-fold improvement over the current limits.
+We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.00025$, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.006$, i.e.~ a three-fold improvement over the forecasts for the stage III experiments and a 37-fold improvement over the current limits.
 We consider how the design of these experiments will impact the resulting PMF limits -- the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties -- and find sensitivity followed by telescope size to be the most important factors in predicting the PMF limits.

### 2017-01-31 pmf.tex
figre update4s

--- 2017-01-31 pmf.tex
@@
     The B-mode measurements used for the limits in this work are denoted with filled circles; data not used has an open circle. 
-    The data sets are from POLARBEAR (black; \citet{polarbear14b}); ACTpol (dark green; \citet{naess14});  BICEP2/Keck Array (red; \citet{bicepkeck15}); and SPTpol (purple; \citet{keisler15}). 
+  The data sets are from POLARBEAR (black circles; \citet{polarbear14b}); ACTpol (dark green triangles; \citet{naess14});  BICEP2/Keck Array (red diamonds; \citet{bicepkeck15}); and SPTpol (purple squares; \citet{keisler15}).
       Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments will significantly increase the signal-to-noise on the B-mode power spectrum. 
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates_nb.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.cm 5.5cm 4cm}]{pmf_templates_nb.pdf}
   \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}

### 2017-01-31 pmf.tex
Some text edits

--- 2017-01-31 pmf.tex
@@
 %\usepackage{multirow}
+\usepackage{soul}
 
@@
 \newcommand{\clpp}{\ensuremath{C_{L}^{\phi\phi}}}
-\newcommand{\cpmf}{\ensuremath{C_{\ell}^{\rm pmf}}}
-\newcommand{\apmf}{\ensuremath{A_{\rm pmf}}}
+\newcommand{\cpmf}{\ensuremath{C_{\ell}^{\rm PMF}}}
+\newcommand{\apmf}{\ensuremath{A_{\rm PMF}}}
 \newcommand{\bpmf}{\ensuremath{B_{\rm 1\,Mpc}}}
@@
 \title{Current and future constraints on primordial magnetic fields}
-\author{D.~Sutton\altaffilmark{\Melbourne}, C.~Feng\altaffilmark{\uci}, and C.~L.~Reichardt\altaffilmark{\Melbourne}}
+\author{Dylan Sutton\altaffilmark{\Melbourne}, Chang Feng\altaffilmark{\uci}, and Christian Reichardt\altaffilmark{\Melbourne}}
 \altaffiltext{\Melbourne}{School of Physics, University of Melbourne, Parkville, VIC 3010, Australia}
@@
 Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for a review, see][]{ryu12, widrow12}. 
-There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}.
+There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although there are alternative explanations \citep{broderick12}. 
 High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
@@
 If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
-There are, however, alternative explanations involving plasma instabilities which may result in positron-electron pairs instead depositing their energy into the IGM as heat \citep{broderick12}.
 
@@
 We use \planck{} data from the 2015 release to constrain the TT, TE, EE and lensing power spectra. 
-Specifically, these are the ``plik\_dx11dr21\_HM\_v18\_TT", ``lowTEB" and ``lensing" \planck{} likelihood modules.
+Specifically, these are the ``plik\_dx11dr21\_HM\_v18\_TT", ``lowTEB" and ``lensing" \planck{} likelihood modules. \textbf{\textcolor{magenta}{CF: why do you use lensing?}}
 
@@
 \be
-C_\ell = C_\ell (CAMB) + \apmf \cpmf
+C_\ell = C_\ell^{\rm{CAMB}} + \apmf \cpmf
 \ee
@@
 
-The density and stress perturbations introduced by PMFs give rise to vorticity and gravitational waves in the early photon-baryon  plasma, i.e. vector and tensor modes, as well as scalar modes. 
+The density and stress perturbations introduced by PMFs give rise to vorticity and gravitational waves in the early photon-baryon  plasma, i.e., vector and tensor modes, as well as scalar modes. 
 The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
-The PMF anisotropy is assumed to be drawn from a Gaussian distribution with a power law power spectrum, $A_B k^{n_B}$, with $n_B$ the spectral index and $A_B$ the PMF power normalization. 
-We can translate the power, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\rm{Mpc}, thereby defining $B_{\rm{1Mpc}}$. 
+The primary PMF anisotropy is assumed to be a Gaussian distribution with a power law power spectrum, $A_B k^{n_B}$, with $n_B$ the spectral index and $A_B$ the PMF power normalization. 
+We can translate the power, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1 \rm{Mpc}, thereby defining \bpmf. 
 Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
@@
 Given that we are still in the era of upper limits,  we do not explore the full 3-dimensional PMF parameter space in this work. 
-Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_B$=-2.9 and $a_{\nu}/a_{\rm{PMF}}=10^9$.
-We also look at $n_B=-1$ and $n_B=2$ in the forecasting section. 
-We have compared calculated templates to the outputs of the earlier CMBACT code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
+Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5 \rm{nG}, $n_B$ = -2.9 and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
+We also look at $n_B\,=\,-1$ and $n_B\,=\,2$ in the forecasting section. 
+We have compared calculated templates to the outputs of the earlier CMBACT-type code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
 We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
-The decision to use the  \citet{zucca16} code instead of CMBACT is based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
+The decision to use the  \citet{zucca16} code instead of CMBACT-type is based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
@@
 In the MCMC, we add a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
-We can translate the amplitude constraint on this template to a constraint on the rms magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
+We can translate the amplitude constraint on this template to a constraint on the \textit{r.m.s.} magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
 \be
@@
 An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed vector-mode power lead to only modestly better limits on the magnetic field strength.
-However, if a PMF is detected, this same steep scaling would allow excellent constraints on its properties.
+\textbf{However, if a PMF is detected, this same steep scaling would allow excellent constraints on its properties.}\textbf{\textcolor{magenta}{CF: confusing}}
 
-\begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
+\begin{figure}[htb]\centering
+\includegraphics[width=13cm,height=12cm]{pmf_experiments.pdf}
   \caption[Current measurements of CMB B-modes]{
-  Current measurements of CMB B-modes. 
+  Current measurements of CMB B-modes. \textbf{\textcolor{magenta}{CF: the markers can be different. ``B-mode power spectrum" as it is and move other legends down}}
     The black line shows the expected B-mode power in the \planck{} best-fit \lcdm{} cosmology (with the tensor-to-scalar ratio, r set to 0.01). 
@@
   }
-\end{figure*}
+\end{figure}
 
@@
   \caption[CMB polarization from PMFs]{
-  The expected contributions to CMB B-modes. 
+  The expected contributions to CMB B-modes. \textbf{\textcolor{magenta}{CF: log y should show the degeneracy better}}
   The red line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology. 
@@
 
-We find the addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement. 
-With Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$. 
+We run the MCMC procedure to sample the PMF parameter space and find that with Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$.
+The addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement.
 We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}.
-Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity). 
+Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (the is due to the fact that the lensing B-modes now also account for partial B-mode budget thus the PMF contribution is reduced).
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments.
+\textbf{\textcolor{magenta}{CF: should we only compare it to Planck with varying $r$.}}
 We test which datasets are important by adding single datasets to the \planck{} set in the simple \lcdm{}+\apmf{} cosmology, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicep$) and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements.
@@
 We propagate these limits on the observed PMF power into limits on the magnetic field strength, \bpmf. 
-We assume the scaling appropriate to the vector modes, i.e. $\apmf \propto \bpmf^4$,  applies to both vector and tensor modes. 
-Given this assumed scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent `detection' of \bpmf. 
+We have validated that the scaling appropriate to the vector modes, i.e. $\apmf \propto \bpmf^4$,  applies to both vector and tensor modes. 
+Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
 We therefore importance sample the chains to generate a flat prior on \bpmf. 
 We find a 95\% limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-This is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we've done. 
-The difference is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT and \citet{zucca16} codes. 
-Using the CMBACT code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
+this is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done.
+This is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-type and \citet{zucca16} codes.
+Using the CMBACT-type code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG.
 Returning to the  \citet{zucca16} code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
@@
 %We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
-These results are inconsistent (being higher) with the equivalent \planck{} + \sptpol{} upper limit quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
+\textbf{These results are inconsistent (being higher) with the equivalent \planck{} + \sptpol{} upper limit quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.}  \textbf{\textcolor{magenta}{CF: we have to rephrase this better}}
 
@@
 \begin{tabular}{l | c c c }
-Model   & $A_{pmf}$ &$A_{lens}$&$r$\\
+Model   & \apmf &\alens&$r$\\
 \hline
-\lcdm{} + \apmf{} &  $< \upperAall$ & - & - \\
-~~~+\alens{} & $< \upperAallalens$ &$ \medAlensall \pm  \sigmaAlensall$ &  -\\
-~~~+\alens{}+r&  $< \upperAallalensr$&$ \medAlensRall \pm  \sigmaAlensRall$ & $<\upperRall$\\ 
+\lcdm{} + \apmf{} &  $< \upperAall$ & \mbox{--} & \mbox{--} \\
+\lcdm{} + \alens{} & $< \upperAallalens$ &$ \medAlensall \pm  \sigmaAlensall$ &  \mbox{--}\\
+\lcdm{} + \alens{} + $r$&  $< \upperAallalensr$&$ \medAlensRall \pm  \sigmaAlensRall$ & $<\upperRall$\\ 
 \end{tabular}
@@
 In the minimal model, \lcdm{} + \apmf{}, current CMB power spectra data from \planck, POLARBEAR, SPTpol, and \bicepkeck{} place a 95\% CL upper limit on the PMF power of $\apmf < \upperAall$. 
-This limit tightens slightly if tensor modes are allowed (r), or the amount of lensing is allowed to vary. 
-In the case of r, the tightening is because the observed power at large angular scales is now split between PMFs or inflationary gravitational waves. 
+This limit tightens slightly if tensor modes ($r$) are allowed, or the amount of lensing is allowed to vary. 
+In the case of $r$, the tightening is because the observed power at large angular scales is now split between PMFs or inflationary gravitational waves. 
 In the case of \alens, it is because the preferred value for \alens{} is modestly above the predicted value of unity. 
@@
 
-\tbd{Add other nb cases???}
+\tbd{Add other nb cases???}  \textbf{\textcolor{magenta}{CF: It is not necessary since the scale-invariant case is the most motivated one. Adding more would just be confusing.}}
 
@@
 There is also a proposal to build a stage IV experiment, CMB-S4, that would increase the detector counts by another order of magnitude and hopefully begin taking data in the early 2020s.
-A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016. 
+\textbf{A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016.} \textbf{\textcolor{magenta}{CF: either delete it or add something}}
 We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are most important to PMF searches.
@@
 \ee
-for parameters, p. 
+for parameters \textbf{p}, and the $\chi^2$ is
+\begin{equation}
+\chi^2(\{\textbf{p}\})=\displaystyle\sum_{\rm{XY}}\displaystyle\sum_l\Big(\frac{C^{\rm{obs,XY}}_{\ell}-\hat C^{\rm{XY}}_{\ell}(\{\textbf{p}\})}{\Delta^{\rm{XY}}_{\ell}}\Big)^2,
+\end{equation}
+where $XY$ can be $TT$, $TE$, $EE$ and $BB$ power spectra of different experiments.
 The inverse of the Fisher matrix is the covariance matrix for the parameters for Gaussian likelihoods. 
@@
 We do not expect the future experiments to substantially improve upon \planck{} in these spectra which are already cosmic variance limited out to fairly high multipoles. 
-We do the opposite for the EE and BB spectra. 
-We do not include \planck{} BB information in any forecast, and  we throw away \planck{} EE data in the overlap region by appropriately increasing the \planck{} EE uncertainties. 
+\st{We do the opposite for the EE and BB spectra. }
+We do not include \planck{} BB information in any forecast, and we throw away \planck{} EE data in the overlap region \textbf{\textcolor{magenta}{CF: with stage-III experiments?}} by appropriately increasing the \planck{} EE uncertainties.
 %The exact increase depends on the assumed stage III or IV survey area.
@@
 \begin{tabular}{l || c c c c c }
-Experiment & Sky coverage & Polarized Noise level  & 1/f knee & Beam FWHM \\
+Experiment & Sky coverage & Polarized Noise level  & 1/$f$ knee & Beam FWHM \\
 & &($\mu$K-arcmin)&&(arcmin.)\\
 \hline
-Stage III: & & & & \\
+Stage III & & & & \\
 
-~~~~SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
-~~~~Simons Array & 36\% & 9.5 & 200 & 3.5 \\ 
-\\
-%\hline
+\mbox{--}SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
+\mbox{--}Simons Array & 36\% & 9.5 & 200 & 3.5 \\
+
+\hline
 CMB Stage IV & 55\% & 1.3 & 100 & 4.0 \\
@@
 We consider the constraints on PMFs in two cosmologies. 
-The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  \lcdm{}  +r + \nrun{} + \neff{} + \mnu{}+ \apmf. 
-Here, r is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species. 
+The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  $\textbf{p}^{(11)}$=\{$\textbf{p}^{\rm{\lcdm{}}}$, $r$, \nrun{}, \neff{}, \mnu{}, \apmf\}. 
+Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species. 
 This 11-parameter model is our default cosmological model for forecasting future PMF constraints. 
-We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B=-2.9$ case with the tensor-to-scalar ratio, r. 
-The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B=-2.9$ is nearly identical. 
-To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{}  + \apmf.
+We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the \st{only} strong degeneracy is in the $n_B\,=\,-2.9$ case with the tensor-to-scalar ratio, $r$. 
+The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B\,=\,-2.9$ is nearly identical.
+To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  $\textbf{p}^{(7)}$=\{$\textbf{p}^{\rm{\lcdm{}}}$, \apmf\}.
 In both cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
@@
 
-\subsection{Stage III forecasts}
+\subsection{Stage III forecasts}\textbf{\textcolor{magenta}{CF: why do you use $\sigma$ not upper bounds in this section?}}
 
 The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-sigma forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_B=-2.9$). 
+With the minimal cosmological model, the 1-$\sigma$ forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_B=-2.9$). 
 This is consistent with, although somewhat better than, the upper limits from the real data).  
-Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty by an order of magnitude in this 7-parameter model to $\sigma(\apmf)=0.015$. 
+Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty by an order of magnitude in the 7-parameter model to $\sigma(\apmf)=0.015$. 
 The improvement is larger when including all eleven parameters, as the parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while only weakening the stage III constraint by a  more modest 40\%.
@@
 $n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
-The improvement for the CMB-S3 experiments over \planck{} remains impressive at a factor of 17 and 13 respectively. 
+The improvement for the \textbf{CMB-S3 ?} experiments over \planck{} remains impressive at a factor of 17 and 13 respectively. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
 
-Between each stage of ground-based CMB experiment, the number of detectors increases by an order of magnitude.
-Adding detectors will always reduce the noise in the instrument, making it easier to isolate the PMF signal, thereby reducing the uncertainty on PMF measurements.
-When quantifying the effects of the number of detectors it is more informative to use polarisation noise, as detector count relies on knowing the individual sensitivity of each detector.
-As such, we give our result in terms of polarisation noise, noting that polarisation noise scales with detector count as $\sqrt{N_{detectors}}$
-
-We find that
-
 \begin{figure}[htb]\centering
@@
   \caption[]{ \label{fig:sensitivity}
-  How the expected uncertainty on the PMF power scales with the polarized map noise. 
+  How the expected uncertainty on the PMF power scales with the polarized map noise. \textbf{\textcolor{magenta}{CF: explain what ($\times10^5$) means. Same to other plots.}}
   Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
@@
 With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and are nearly flat (a 6\% improvement) from 25\% to 70\% of the sky (the widest area likely to be possible after galactic cuts).
-Conversely, $n_B=-1$or +2, the optimal survey area is smaller at 10\% of the full sky. 
+Conversely, $n_B=-1$ or +2, the optimal survey area is smaller at 10\% of the full sky. 
 Note however that the minimum is extremely broad with only a 10\% worsening of the expected uncertainty as the survey area is increased from 10\% to 70\% of the  full sky. 

### 2017-01-31 pmf.tex
expanded alternative explanation from broderick et al. 2012

@@
 If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
+There are, however, alternative explanations involving instabilities in the electron-positron plasma leading pairs to deposit their energy in the intergalactic medium in the form of heat \citep{broderick12}.
 

### 2017-02-01 pmf.tex
added comma

@@
 If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
-There are, however, alternative explanations involving instabilities in the electron-positron plasma leading pairs to deposit their energy in the intergalactic medium in the form of heat \citep{broderick12}.
+There are, however, alternative explanations involving instabilities in the electron-positron plasma, leading pairs to deposit their energy in the intergalactic medium in the form of heat \citep{broderick12}.
 

### 2017-02-01 pmf.tex
figs and edits

--- 2017-01-31 pmf.tex
@@
 \title{Current and future constraints on primordial magnetic fields}
-\author{Dylan Sutton\altaffilmark{\Melbourne}, Chang Feng\altaffilmark{\uci}, and Christian Reichardt\altaffilmark{\Melbourne}}
+\author{D.~Sutton\altaffilmark{\Melbourne}, C.~Feng\altaffilmark{\uci}, and C.~L.~Reichardt\altaffilmark{\Melbourne}}
 \altaffiltext{\Melbourne}{School of Physics, University of Melbourne, Parkville, VIC 3010, Australia}
@@
 We use \planck{} data from the 2015 release to constrain the TT, TE, EE and lensing power spectra. 
-Specifically, these are the ``plik\_dx11dr21\_HM\_v18\_TT", ``lowTEB" and ``lensing" \planck{} likelihood modules. \textbf{\textcolor{magenta}{CF: why do you use lensing?}}
+Specifically, these are the ``plik\_dx11dr21\_HM\_v18\_TT", ``lowTEB" and ``lensing" \planck{} likelihood modules.
 
@@
 The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
-The primary PMF anisotropy is assumed to be a Gaussian distribution with a power law power spectrum, $A_B k^{n_B}$, with $n_B$ the spectral index and $A_B$ the PMF power normalization. 
-We can translate the power, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1 \rm{Mpc}, thereby defining \bpmf. 
+The primary PMF anisotropy is assumed to be Gaussian distributed with a power law power spectrum, $A_B k^{n_B}$, with $n_B$ the spectral index and $A_B$ the PMF power normalization. 
+We can translate the power, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\,Mpc, thereby defining \bpmf. 
 Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
@@
 Given that we are still in the era of upper limits,  we do not explore the full 3-dimensional PMF parameter space in this work. 
-Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5 \rm{nG}, $n_B$ = -2.9 and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
+Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG, $n_B = -2.9$ and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
 We also look at $n_B\,=\,-1$ and $n_B\,=\,2$ in the forecasting section. 
@@
 In the MCMC, we add a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
-We can translate the amplitude constraint on this template to a constraint on the \textit{r.m.s.} magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
-\be
+We can translate the amplitude constraint on this template to a constraint on the r.m.s. magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
+\be \label{eqn:scaling}
 \apmf \propto \bpmf^4.
@@
 An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed vector-mode power lead to only modestly better limits on the magnetic field strength.
-\textbf{However, if a PMF is detected, this same steep scaling would allow excellent constraints on its properties.}\textbf{\textcolor{magenta}{CF: confusing}}
+However, if a PMF is detected, the steep scaling between \bpmf{} and the observed would allow excellent constraints on the PMF properties.
 
-\begin{figure}[htb]\centering
-\includegraphics[width=13cm,height=12cm]{pmf_experiments.pdf}
+\begin{figure*}[htb]\centering
+\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
   \caption[Current measurements of CMB B-modes]{
-  Current measurements of CMB B-modes. \textbf{\textcolor{magenta}{CF: the markers can be different. ``B-mode power spectrum" as it is and move other legends down}}
+  Current measurements of CMB B-modes. 
     The black line shows the expected B-mode power in the \planck{} best-fit \lcdm{} cosmology (with the tensor-to-scalar ratio, r set to 0.01). 
@@
   }
-\end{figure}
+\end{figure*}
 
 \begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
+\includegraphics[width=0.9\textwidth,clip,trim={2.cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
   \caption[CMB polarization from PMFs]{
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.cm 5.5cm 4cm}]{pmf_templates_nb.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={2.cm 12.cm 5.5cm 4cm}]{pmf_templates_nb.pdf}
   \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
   How the expected PMF changes with the spectral index, $n_B$. 
-  The lensing B-mode power spectrum (solid, black line) are plotted against the PMF power for $n_B=-2.9$ (solid, purple line), $n_B=-1$ (dashed, green line), and $n_B=+2$ (dotted, red line). 
+  The lensing B-mode power spectrum (solid, black line) are plotted against the PMF power for $n_B=-2.9$ (solid, blue line), $n_B=-1$ (dashed, green line), and $n_B=+2$ (dotted, red line). 
   To keep all the curves on the same scale, we adjust the RMS strength of the magnetic field, \bpmf{}, between the three cases as noted in the legend. 
@@
 
-We run the MCMC procedure to sample the PMF parameter space and find that with Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$.
-The addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement.
+We find the addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement. 
+With Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$. 
 We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}. 
-Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (the is due to the fact that the lensing B-modes now also account for partial B-mode budget thus the PMF contribution is reduced).
+Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity). 
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments. 
-\textbf{\textcolor{magenta}{CF: should we only compare it to Planck with varying $r$.}}
 We test which datasets are important by adding single datasets to the \planck{} set in the simple \lcdm{}+\apmf{} cosmology, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicep$) and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements.
@@
 We propagate these limits on the observed PMF power into limits on the magnetic field strength, \bpmf. 
-We have validated that the scaling appropriate to the vector modes, i.e. $\apmf \propto \bpmf^4$,  applies to both vector and tensor modes. 
+We do this using the scaling from Eqn.~\ref{eqn:scaling}, $\apmf \propto \bpmf^4$. 
 Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
@@
 \hline
-\lcdm{} + \apmf{} &  $< \upperAall$ & \mbox{--} & \mbox{--} \\
-\lcdm{} + \alens{} & $< \upperAallalens$ &$ \medAlensall \pm  \sigmaAlensall$ &  \mbox{--}\\
-\lcdm{} + \alens{} + $r$&  $< \upperAallalensr$&$ \medAlensRall \pm  \sigmaAlensRall$ & $<\upperRall$\\ 
+\lcdm{}&&&\\
+~~~+ \apmf{} &  $< \upperAall$ & \mbox{--} & \mbox{--} \\
+~~~+ \apmf{} + \alens{} & $< \upperAallalens$ &$ \medAlensall \pm  \sigmaAlensall$ &  \mbox{--}\\
+~~~+ \apmf{} + \alens{} + $r$&  $< \upperAallalensr$&$ \medAlensRall \pm  \sigmaAlensRall$ & $<\upperRall$\\ 
 \end{tabular}
@@
 This limit tightens slightly if tensor modes ($r$) are allowed, or the amount of lensing is allowed to vary. 
-In the case of $r$, the tightening is because the observed power at large angular scales is now split between PMFs or inflationary gravitational waves. 
+In the case of $r$, the tightening is because the observed power at large angular scales is now split between PMFs and inflationary gravitational waves. 
 In the case of \alens, it is because the preferred value for \alens{} is modestly above the predicted value of unity. 
@@
 There is also a proposal to build a stage IV experiment, CMB-S4, that would increase the detector counts by another order of magnitude and hopefully begin taking data in the early 2020s. 
-\textbf{A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016.} \textbf{\textcolor{magenta}{CF: either delete it or add something}}
+A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016.
 We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are most important to PMF searches.
@@
 \ee
-for parameters \textbf{p}, and the $\chi^2$ is
-\begin{equation}
-\chi^2(\{\textbf{p}\})=\displaystyle\sum_{\rm{XY}}\displaystyle\sum_l\Big(\frac{C^{\rm{obs,XY}}_{\ell}-\hat C^{\rm{XY}}_{\ell}(\{\textbf{p}\})}{\Delta^{\rm{XY}}_{\ell}}\Big)^2,
-\end{equation}
-where $XY$ can be $TT$, $TE$, $EE$ and $BB$ power spectra of different experiments.
+for model parameters \textbf{p}. 
 The inverse of the Fisher matrix is the covariance matrix for the parameters for Gaussian likelihoods. 
@@
 We do not expect the future experiments to substantially improve upon \planck{} in these spectra which are already cosmic variance limited out to fairly high multipoles. 
-\st{We do the opposite for the EE and BB spectra. }
-We do not include \planck{} BB information in any forecast, and we throw away \planck{} EE data in the overlap region \textbf{\textcolor{magenta}{CF: with stage-III experiments?}} by appropriately increasing the \planck{} EE uncertainties.
+We do the opposite for the EE and BB spectra. 
+We do not include \planck{} BB information in any forecast, and we throw away \planck{} EE data in the overlap region by appropriately increasing the \planck{} EE uncertainties. 
 %The exact increase depends on the assumed stage III or IV survey area.
@@
 \hline
-Stage III & & & & \\
+CMB Stage III & & & & \\
 
-\mbox{--}SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
-\mbox{--}Simons Array & 36\% & 9.5 & 200 & 3.5 \\
-
-\hline
+~~~~~SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
+~~~~~Simons Array & 36\% & 9.5 & 200 & 3.5 \\ 
+\\
+%\hline
 CMB Stage IV & 55\% & 1.3 & 100 & 4.0 \\
@@
 We consider the constraints on PMFs in two cosmologies. 
-The first is a 11-parameter model that extends \lcdm{} with 5 commonly considered extensions:  $\textbf{p}^{(11)}$=\{$\textbf{p}^{\rm{\lcdm{}}}$, $r$, \nrun{}, \neff{}, \mnu{}, \apmf\}. 
+The first is a 11-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf. 
 Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species. 
 This 11-parameter model is our default cosmological model for forecasting future PMF constraints. 
-We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the \st{only} strong degeneracy is in the $n_B\,=\,-2.9$ case with the tensor-to-scalar ratio, $r$. 
+We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case with the tensor-to-scalar ratio, $r$. 
 The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B\,=\,-2.9$ is nearly identical.
-To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  $\textbf{p}^{(7)}$=\{$\textbf{p}^{\rm{\lcdm{}}}$, \apmf\}.
+To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf.
 In both cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
@@
 
-\subsection{Stage III forecasts}\textbf{\textcolor{magenta}{CF: why do you use $\sigma$ not upper bounds in this section?}}
+\subsection{Stage III forecasts}
 
@@
 $n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
-The improvement for the \textbf{CMB-S3 ?} experiments over \planck{} remains impressive at a factor of 17 and 13 respectively. 
+The improvement from adding the SPT-3G and Simons Array experiments to \planck{} remains impressive at a factor of 17 and 13 respectively. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_sens.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={2.cm 12.5cm 11cm 7.5cm}]{pmf_sens.pdf}
   \caption[]{ \label{fig:sensitivity}
-  How the expected uncertainty on the PMF power scales with the polarized map noise. \textbf{\textcolor{magenta}{CF: explain what ($\times10^5$) means. Same to other plots.}}
+  How the expected uncertainty on the PMF power scales with the polarized map noise. 
   Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
-  The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
+  In the case of $n_B=2$, the uncertainties have been multiplied by a factor of $10^5$ to allow them to be plotted on the same scale. 
+  The black lines are for the conservative 11-parameter model, while the light blue lines are for the simple \lcdm{}+\apmf{} model. 
   The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the 11-parameter model due a degeneracy with the tensor-to-scalar ratio. 
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_beam.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={2.cm 12.5cm 11cm 7.5cm}]{pmf_beam.pdf}
   \caption[]{ \label{fig:beam}
@@
  Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
-  The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
+   In the $n_B=2$ case, the uncertainties have been multiplied by a factor of $10^5$ to allow them to be plotted on the same scale. 
+  The black lines are for the conservative 11-parameter model, while the light blue lines are for the simple \lcdm{}+\apmf{} model. 
   The cosmological model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={2.cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
   \caption[Area dependence]{
@@
  In contrast, for the cases where $n_B = -1, +2$ (dashed and dot-dashed lines), we find that observing  $\sim$\,10\% of the sky produces the best PMF constraints. 
-   There is essentially no difference to the preferred areas between the 11-parameter cosmological model (black) or the restricted \lcdm{}+\apmf{} 7-parameter model (purple). 
+   Note that in the case of $n_B=2$, the uncertainties have been multiplied by a factor of $10^5$ for plotting purposes. 
+   There is essentially no difference to the preferred areas between the 11-parameter cosmological model (black) or the restricted \lcdm{}+\apmf{} 7-parameter model (light blue). 
      Fortunately, the minima for all three templates are relatively broad, and a survey covering 15+\% of the sky will do well for all values of the PMF spectral index. 
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_knee.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={2.cm 12.5cm 11cm 7.5cm}]{pmf_knee.pdf}
   \caption[Map knee dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, purple line).
+  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, light blue line).
   However,  the achieved map 1/f knee frequency makes no difference to the potential power of CMB-S4 PMF searches in the 11-parameter model (solid, black line). 
   The change in behavior happens because the 11-parameter model introduces a degeneracy with r that shifts the angular scale of the PMF constraint to sub-degree scales. 
-  The 1/f knee frequency also makes no difference for the bluer PMF templates in either the restricted or full 11-parameter model space (dashed and dash-dotted black lines). 
-   for any value of $n_B$ (black lines). 
+  The 1/f knee frequency also makes no difference for the bluer PMF templates  (dashed and dash-dotted black lines) in either the restricted (light blue) or full 11-parameter (black) model space. 
+     Note that in the case of $n_B=2$, the forecasts have been multiplied by a factor of $10^5$ for plotting purposes. 
     \label{fig:knee}

### 2017-02-01 pmf.tex
small edits

@@
 \begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={2.cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
+\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5.5cm 4cm}]{pmf_templates.pdf}
   \caption[CMB polarization from PMFs]{
@@
 \begin{figure}[htb]\centering
-\includegraphics[width=0.45\textwidth,clip,trim={2.cm 12.cm 5.5cm 4cm}]{pmf_templates_nb.pdf}
+\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.cm 5.5cm 4cm}]{pmf_templates_nb.pdf}
   \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
@@
 Second, we include a 1\% external measurement of the Hubble constant, such as is expected from the Taipan experiment \citep{kuehn14}.
+
+To calculate the Fisher matrix for a CMB experiment, we need to calculate partial derivatives of the CMB spectra and the bandpower covariance matrix. 
+The partial derivatives are calculated numerically from CAMB spectra  \citep{lewis00}. 
+We calculate the bandpower covariance matrix using the Knox formula \citep{knox97} for the survey parameters in Table~\ref{tab:experiments}. 
+The sample variance contribution is calculated assuming the \planck{} best-fit \lcdm{} cosmology with a small gravitational wave contribution  ($r=0.01$) added. 
+This is the black line in Fig.~\ref{fig:pmf-experiments}. 
+We use a bandpower bin size of $\Delta\ell=50$. 
+We also add calibration and beam uncertainties to bandpower covariance matrix.
 

### 2017-02-01 pmf.tex
ifi2 edits

@@
 \begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5.5cm 4cm}]{pmf_templates.pdf}
+\includegraphics[width=0.9\textwidth,clip,trim={1.cm 12.cm 6cm 5cm}]{pmf_templates.pdf}
   \caption[CMB polarization from PMFs]{
-  The expected contributions to CMB B-modes. \textbf{\textcolor{magenta}{CF: log y should show the degeneracy better}}
+  The expected contributions to CMB B-modes.
   The red line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology. 

### 2017-02-02 pmf.tex
moved alternative explanation

@@
 The missing flux could be explained by the deflection of particles due to intergalactic magnetic fields. 
-If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
 There are, however, alternative explanations involving instabilities in the electron-positron plasma, leading pairs to deposit their energy in the intergalactic medium in the form of heat \citep{broderick12}.
+If the loss of flux is indeed due to magnetic fields, then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.
 

### 2017-02-02 pmf.tex
a

@@
 We also look at $n_B\,=\,-1$ and $n_B\,=\,2$ in the forecasting section. 
-We have compared calculated templates to the outputs of the earlier CMBACT-type code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
+We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
 We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
-The decision to use the  \citet{zucca16} code instead of CMBACT-type is based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
+The decision to use the  \citet{zucca16} code instead of CMBACT-derived code is based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
@@
 this is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-This is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-type and \citet{zucca16} codes.
-Using the CMBACT-type code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG.
-Returning to the  \citet{zucca16} code, the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
-The improvement from adding more data is somewhat less than one might predict because the combined likelihood peaks somewhat above zero, whereas the \planck{}-only constraints peaks at zero. 
+This is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16} codes. 
+Using the CMBACT-derived code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
+Returning to the  \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
+The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero. 
 %We also stress that this should not be treated as a robust limit as the tensor PMF modes are crucial to the improvement, and the assumed scaling has not been tested for the tensor PMF. 
 %We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
-\textbf{These results are inconsistent (being higher) with the equivalent \planck{} + \sptpol{} upper limit quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.}  \textbf{\textcolor{magenta}{CF: we have to rephrase this better}}
+These results are higher and inconsistent with the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
 
@@
 \end{table}
-
-\tbd{Add other nb cases???}  \textbf{\textcolor{magenta}{CF: It is not necessary since the scale-invariant case is the most motivated one. Adding more would just be confusing.}}
 

### 2017-02-02 pmf.tex
adding numbers

@@
 $n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
-The improvement from adding the SPT-3G and Simons Array experiments to \planck{} remains impressive at a factor of 17 and 13 respectively. 
+The improvement from adding the SPT-3G and Simons Array experiments to \planck{} remains impressive.
+For the 11-parameter model and $n_B=-1$, adding SPT-3G and Simons Array to \planck{} leads to a 17-fold reduction in $\sigma(\apmf)$ from \fisherAlooseNbOneplk{} to \fisherAlooseNbOneSThree{}.
+For $n_B=2$, there is a 20-fold reduction from $\sigma(\apmf) = \fisherAlooseNbTwoplk$ to  \fisherAlooseNbTwoSThree. 
 We can expect substantially tighter constraints on PMFs by the end of the decade.
@@
 
-\tbd{I found this awkward text, will rewrite}
-
-We naturally expect more sensitive instruments to do a better job of constraining PMF models. 
-The goal of this section is to quantify that statement for the three PMF templates considered in the 11 or 7-parameter cosmological models. 
-Our results are shown in Fig.~\ref{fig:sensitivity}. 
+Reducing the noise in CMB maps should always improve the derived constraints. 
+The goal of this section is to quantify the magnitude of that improvement: has the information gain saturated, or will further reductions in noise substantially improve PMF searches. 
+Figure~\ref{fig:sensitivity} shows the uncertainty on \apmf{} as a function of the map noise level for the three PMF templates in either the 11 or 7-parameter cosmological models. 
 For this figure, we have fixed the rest of the experimental configuration (i.e.~everything except the polarized noise levels) to the values of the CMB-S4 row in Table~\ref{tab:experiments}. 

### 2017-02-02 pmf.tex
nb=-2.9 just

@@
 
-We find the addition of ground-based CMB polarization data to \planck{} data substantially improves the upper limits on the allowed power due to a PMF, leading to a factor of two improvement. 
+We investigate how the addition of ground-based CMB polarization data to \planck{} data affects the PMF limits, focusing on the most theoretically motivated scenario of an approximately scale-invariant spectrum for the PMFs ($n_B=-2.9$).
+The ground-based CMB polarization data  substantially improves the upper limits on the allowed PMF power, leading to a factor of two improvement over \planck{} alone. 
 With Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$. 
@@
 We begin by considering our fiducial CMB-S4 configuration, as laid out in Table~\ref{tab:experiments}. 
-For this fiducial configuration, we expect \tbd{add numbers}.
+For this fiducial configuration and the 11-parameter model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes. 
+The exact values are $\sigma(\apmf^{n_B=-2.9}) =   \fisherAlooseSFour$, $\sigma(\apmf^{n_B=-1}) =   \fisherAlooseNbOneSFour$, and $\sigma(\apmf^{n_B=2}) =   \fisherAlooseNbTwoSFour$. 
+These represent more than a 50-fold improvement on current limits.
 
-Given that CMB-S4 is currently in the design phase, it is worthwhile to consider how design decisions will affect the final PMF constraints. 
+Given that CMB-S4 is currently in the design phase, it is also worthwhile to consider how design decisions will affect the final PMF constraints. 
 We look at five aspects of the experiment design: the instrumental sensitivity (as reflected by the map noise level), the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
@@
 As should be expected, the preferred design depends on the shape of the PMF spectrum ($n_B$) which controls  the relative power between large and small angular scales. 
+However, as was discussed in \S\ref{sec:template},  there are theoretical reasons to expect the PMF spectrum to be close to a scale-invariant spectra, as opposed to, e.g., $n_B=2$.
 

### 2017-02-03 pmf.tex
edits up t 3

@@
 We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce twofold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < \upperAplk$ from Planck alone to $\apmf < \upperAall$ for the combined dataset at 95\% CL. 
+We reduce twofold the 95\% CL upper limit on the CMB anisotropy power due to a PMF, from $\apmf < \upperAplk$ for Planck alone to $\apmf < \upperAall$ for the combined dataset . 
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
-We also forecast the expected future limits from soon-to-deploy CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB-S4 experiment. 
+We also forecast the expected  limits from soon-to-deploy CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB-S4 experiment. 
 Future CMB experiments should dramatically reduce the current uncertainties, by one order of magnitude for the near-term experiments and two orders of magnitude for the CMB-S4 experiment. 
@@
 
-In addition to the \planck{} data, we use a number of recent CMB B-mode polarization measurements. 
+In addition to the \planck{} data, we use a number of ground-based CMB B-mode polarization measurements. 
 First, we include measurements of the TE, EE and BB power spectra from the \sptpol{} experiment \citep{crites15,keisler15}. 
@@
 In all chains, we marginalize over the recommended foreground models for each data set. 
-We do not however require consistency between these foreground models since the data don't have identical flux cuts for extragalactic sources and so on. 
+We do not however require consistency between these foreground models as the data don't have identical flux cuts for extragalactic sources and so on. 
 %In the case of an upper limit this treatment is conservative since wider foreground priors should only weaken the limit on the PMF strength. 
@@
 CosmoMC invokes  CAMB\footnote{http://camb.info}  \citep{lewis00} to calculate the CMB power spectrum for each set of cosmological parameters. 
-Although CosmoMC and CAMB have a partial implementation of PMF, we choose to adopt a simpler, fast template-based calculation for the PMF power. 
+Although CosmoMC and CAMB have a partial implementation of PMFs, we choose to adopt a simpler, fast template-based calculation for the PMF-sourced power. 
 We have adapted CosmoMC to add a scaled version of the template to all four CMB power spectra: TT, TE, EE, and BB, where the scale factor is \apmf. 
@@
 The calculation of the PMF template, \cpmf, is described in \S\ref{sec:template}. 
-Note that no other effect of the PMF is considered; this is one reason we only consider CMB data.
+Note that no other effect of  PMFs is considered; this is one reason we only consider CMB data.
 
-For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to the PMF.
+For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to PMFs. 
 We adopt flat priors on all parameters. 
 In particular, note that this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
-In many chains, we also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
+We sometimes also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
 Finally, in some cases, we allow non-zero tensors, parameterized by the tensor-to-scalar ratio, r.
@@
 The density and stress perturbations introduced by PMFs give rise to vorticity and gravitational waves in the early photon-baryon  plasma, i.e., vector and tensor modes, as well as scalar modes. 
-The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to includes sources due to the PMFs. 
-The primary PMF anisotropy is assumed to be Gaussian distributed with a power law power spectrum, $A_B k^{n_B}$, with $n_B$ the spectral index and $A_B$ the PMF power normalization. 
-We can translate the power, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\,Mpc, thereby defining \bpmf. 
-Finally, the timing of when the PMFs are generated matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
+The exact amplitude of these modes can be calculated by modifying the normal Boltzmann equations to include sources due to the PMFs. 
+The primary PMF anisotropy is assumed to be Gaussian distributed with a power law power spectrum, $A_B k^{n_B}$, where $n_B$ is the spectral index and $A_B$ is the PMF power normalization. 
+We can translate the normalization, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\,Mpc, which we will call \bpmf. 
+Finally, the timing of when PMFs are generated relative to neutrino decoupling matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
 The timing is typically parametrized by the ratio of the scale factors at neutrino decoupling and PMF generation, $a_{\nu}/a_{\rm{PMF}}$.
@@
 Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG, $n_B = -2.9$ and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
+\tbd{somewhere around here add arguments for $nb=-2.9$beinbg preferred} 
 We also look at $n_B\,=\,-1$ and $n_B\,=\,2$ in the forecasting section. 
@@
 We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
-The decision to use the  \citet{zucca16} code instead of CMBACT-derived code is based on the need to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
+The origin of the difference is unclear. 
+We have chosen to use the  more recent \citet{zucca16} code instead of CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
-The lack of scalar terms should only matter for constraints primarily from the temperature spectrum, i.e. the \planck-only results. 
-These temperature results are not the main focus of this work, and we find our results consistent with the \planck{} results from \citet{planck15-19} suggesting the impact is minor. 
+The lack of scalar terms should not matter for CMB polarization data. 
+Temperature data is not the main focus of this work, and  and we find our \planck{} results  to be consistent with \citet{planck15-19}, suggesting the impact of the scalar terms is minor. 
 The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}.
-In the MCMC, we add a new scaling parameter, $A_{pmf}$, that rescales the PMF power spectrum template. 
+
+In the MCMC, we add a new scaling parameter, \apmf{}, that rescales the PMF power spectrum template. 
 We can translate the amplitude constraint on this template to a constraint on the r.m.s. magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
@@
 An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed vector-mode power lead to only modestly better limits on the magnetic field strength.
-However, if a PMF is detected, the steep scaling between \bpmf{} and the observed would allow excellent constraints on the PMF properties.
+However, if a PMF is detected, the steep scaling between \bpmf{} and the observed CMB B-mode power spectrum would allow excellent constraints on the PMF properties.
 
@@
 
-We investigate how the addition of ground-based CMB polarization data to \planck{} data affects the PMF limits, focusing on the most theoretically motivated scenario of an approximately scale-invariant spectrum for the PMFs ($n_B=-2.9$).
-The ground-based CMB polarization data  substantially improves the upper limits on the allowed PMF power, leading to a factor of two improvement over \planck{} alone. 
-With Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}; with the ground-based experiments, this limit drops to $\apmf <  \upperAall$. 
+We begin by investigating how the addition of ground-based CMB polarization data to \planck{} data affects the limits on PMFs. 
+For the real data, we focus on the most theoretically motivated scenario of an approximately scale-invariant spectrum for the PMFs ($n_B=-2.9$), although we will consider other scenarios in the forecasts of the next section.
+The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \planck{} alone in the simple 7-parameter model. 
+The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}. 
+Adding the ground-based experiments brings this limit to $\apmf <  \upperAall$. 
+We test which datasets are important by adding single datasets to the \planck{} data, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicep$) and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements.
+The other datasets do not have a large impact on the observed limits. 
+In short, the factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
+
+We next look at the model dependence of these upper limits. 
 We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}. 
@@
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments. 
-We test which datasets are important by adding single datasets to the \planck{} set in the simple \lcdm{}+\apmf{} cosmology, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicep$) and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements.
-The other datasets do not have a large impact on the observed limits. 
-In short, the reduction in the allowed upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
+The 95\% CL upper limit on \apmf{} also drops when tensor modes are introduced, as parameterized by the tensor-to-scalar ratio r. 
+This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms, r or \apmf{}.
 
-We propagate these limits on the observed PMF power into limits on the magnetic field strength, \bpmf. 
-We do this using the scaling from Eqn.~\ref{eqn:scaling}, $\apmf \propto \bpmf^4$. 
+We also propagate the limits on the observed PMF power into limits on the magnetic field strength, \bpmf. 
+We do this using the scaling of Eqn.~\ref{eqn:scaling}, $\apmf \propto \bpmf^4$. 
 Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
-We therefore importance sample the chains to generate a flat prior on \bpmf. 
+We therefore importance sample the chains to apply a flat prior on \bpmf. 
 We find a 95\% limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
 this is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-This is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16} codes. 
-Using the CMBACT-derived code that \citet{planck15-19} used, we find a completely consistent upper limit of $\bpmf < 1.9$\,nG. 
-Returning to the  \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is only slightly reduced to $\bpmf < \upperBall$\,nG for the combined dataset. 
+The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16} codes. 
+Using the CMBACT-derived code that \citet{planck15-19} used, we find a consistent upper limit of $\bpmf < 1.9$\,nG. 
+Returning to the  \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is  reduced only slightly to $\bpmf < \upperBall$\,nG. 
 The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero. 
@@
 %We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
-These results are higher and inconsistent with the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
+These results are higher than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
 

### 2017-02-03 pmf.tex
iup to 4.2

@@
     The black line shows the expected B-mode power in the \planck{} best-fit \lcdm{} cosmology (with the tensor-to-scalar ratio, r set to 0.01). 
+  The data sets are from POLARBEAR (black circles; \citet{polarbear14b}); ACTpol (dark green triangles; \citet{naess14});  BICEP2/Keck Array (red diamonds; \citet{bicepkeck15}); and SPTpol (purple squares; \citet{keisler15}).
       The B-mode measurements used for the limits in this work are denoted with filled circles; data not used has an open circle. 
-  The data sets are from POLARBEAR (black circles; \citet{polarbear14b}); ACTpol (dark green triangles; \citet{naess14});  BICEP2/Keck Array (red diamonds; \citet{bicepkeck15}); and SPTpol (purple squares; \citet{keisler15}).
       Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments will significantly increase the signal-to-noise on the B-mode power spectrum. 
@@
   \caption[CMB polarization from PMFs]{
-  The expected contributions to CMB B-modes.
-  The red line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology. 
-  The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
-  The dashed purple line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
-  As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
-  %However, if excess power on these scales is detected, higher order moments of the map (i.e.~4-point estimators) might be used to discriminate between   the inflationary and PMF explanations. 
+  The expected sources of CMB B-modes.
+  The black line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology, while the red line corresponds to the B-modes due to inflationary gravitational waves for $r=0.05$.
+  The dashed blue line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
+  At $\ell < 200$, the tensor contribution from PMFs closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate on these angular scales in a power spectrum (2-point) analysis.
       \label{fig:pmf-bb}
@@
   \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
-  How the expected PMF changes with the spectral index, $n_B$. 
-  The lensing B-mode power spectrum (solid, black line) are plotted against the PMF power for $n_B=-2.9$ (solid, blue line), $n_B=-1$ (dashed, green line), and $n_B=+2$ (dotted, red line). 
+  How the expected B-mode power due to PMFs changes with the spectral index, $n_B$. 
+  The lensing B-mode power spectrum (solid, black line) is plotted against the PMF power for $n_B=-2.9$ (solid, blue line), $n_B=-1$ (dashed, green line), and $n_B=+2$ (dotted, red line). 
   To keep all the curves on the same scale, we adjust the RMS strength of the magnetic field, \bpmf{}, between the three cases as noted in the legend. 
-  At fixed RMS magnetic field strength, increasing $n_B$ greatly increases the expected B-mode power. 
+  For a fixed RMS magnetic field strength, increasing $n_B$ greatly increases the expected B-mode power. 
   There is an inflection point between the nearly-scale-invariant PMF with $n_B=-2.9$ and the bluer PMF spectra ($n_B=-1$ or 2) which shifts power to smaller angular scales and eliminates the peak at $\ell \lesssim 200$.
@@
 We list the limits for the combined dataset  with different parameter sets in Table~\ref{tab:param_all}. 
-Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity). 
+First, we vary the largest source of  B-mode power, gravitational lensing, by allowing \alens{} to float. 
+Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power). 
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments. 
-The 95\% CL upper limit on \apmf{} also drops when tensor modes are introduced, as parameterized by the tensor-to-scalar ratio r. 
+Next we introduce inflationary gravitational waves, as parameterized by the tensor-to-scalar ratio r. 
+The 95\% CL upper limit on \apmf{} drops slightly again.  
 This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms, r or \apmf{}.
@@
 The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero. 
-%We also stress that this should not be treated as a robust limit as the tensor PMF modes are crucial to the improvement, and the assumed scaling has not been tested for the tensor PMF. 
-%We quote it nonetheless to illustrate that with a steep power law scaling, the relative improvement to \bpmf{} will be slower than the improvement to \apmf{} as more data is added.
 These results are higher than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
@@
 \citet{abazajian16} thus defines four stages of CMB experiments. 
-The current experiments (i.e.~the ones used for PMF constraints in the last section) are classified as Stage II experiments. 
+Current experiments are called stage II. 
+The B-mode measurements from these stage II experiments were  used for PMF constraints in the last section and are plotted in Fig.~\ref{fig:pmf-experiments}. 
 Stage III experiments such as SPT-3G, the Simons Array, or AdvACTPol \citep{benson14,suzuki16,henderson16} have approximately ten times more detectors, and generically will start collecting data around 2017 and finish three to four years later.
-In this section, we forecast the expected constraints from the EE and BB power spectrum measurements  of the Stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
+In this section, we forecast the expected constraints from the EE and BB power spectrum measurements  of the stage III experiments by combining forecasts for SPT-3G and the Simons Array. 
 There is also a proposal to build a stage IV experiment, CMB-S4, that would increase the detector counts by another order of magnitude and hopefully begin taking data in the early 2020s. 
 A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016.
-We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and consider which aspects of experimental or survey design are most important to PMF searches.
+We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and look at how to design CMB-S4 to maximize PMF searches.
 
@@
 for model parameters \textbf{p}. 
-The inverse of the Fisher matrix is the covariance matrix for the parameters for Gaussian likelihoods. 
-While Fisher matrices underestimate the true uncertainties for non-Gaussian likelihoods \citep[see e.g.,][]{wolz12}, they 
- make it easy to combine different experiments and estimate the final parameter constraints.
+The inverse of the Fisher matrix is the covariance matrix of the parameters for Gaussian likelihoods. 
+While Fisher matrices can underestimate the true uncertainties for non-Gaussian likelihoods \citep[see e.g.,][]{wolz12}, they 
+ make it easy to combine information from different experiments and estimate the final parameter constraints.
 
@@
 Due to the importance of galactic foreground removal at large scales in polarization, we only use TE and EE information starting from $\ell = 30$. 
-A prior on the optical depth of 0.005 is added to account for the expected optical depth constraint from the missing multipoles. 
+A prior on the optical depth of 0.005 is added to account for the optical depth constraint expected from the missing multipoles. 
 Second, we include a 1\% external measurement of the Hubble constant, such as is expected from the Taipan experiment \citep{kuehn14}.
@@
 We use a bandpower bin size of $\Delta\ell=50$. 
-We also add calibration and beam uncertainties to bandpower covariance matrix.
+We  assume a 5\% uncertainty on the beam FWHM and a 1\% power calibration uncertainty.
+In \S\ref{subsec:beamcal}, we test relaxing or tightening the beam and calibration uncertainty and find the beam and calibration uncertainties have a negligible impact on the PMF constraints.
 
@@
 We avoid this problem in different ways in each of the CMB power spectra. 
-For the TT and TE spectra, we avoid double-counting by only using the \planck{} measurements. 
+For the TT and TE spectra, we only use the \planck{} measurements. 
 We do not expect the future experiments to substantially improve upon \planck{} in these spectra which are already cosmic variance limited out to fairly high multipoles. 
 We do the opposite for the EE and BB spectra. 
-We do not include \planck{} BB information in any forecast, and we throw away \planck{} EE data in the overlap region by appropriately increasing the \planck{} EE uncertainties. 
+We do not include \planck{} BB information in any forecast, and we throw away \planck{} EE data in the overlap region by appropriately scaling the \planck{} EE uncertainties. 
 %The exact increase depends on the assumed stage III or IV survey area.
-We ignore overlaps between the stage-III experiments  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G should be small. 
-This is also why we do not include both Simons Array and AdvACTpol as the two experiments are likely to have substantial sky overlap. 
-The overlapping sky coverage is expected to be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
+We ignore overlaps between the stage-III experiments  on the basis that the sky overlap between a Chilean experiment like the Simons Array and South Pole experiment like SPT-3G will be small. 
+The overlap issue is also the rationale behind using only one of the Simons Array and AdvACTpol as the two experiments are likely to have substantial sky overlap. 
+The overlap in sky coverage will almost certainly be substantial between stage III and IV experiments, thus we do not include the stage III experiments, except as a prior on the polarized Poisson power, in the CMB-S4 constraints.
 This prior is only relevant in practice when the assumed CMB-S4 configuration has a larger beam size than SPT-3G. 
@@
 \hline
+\tiny \\ \small
 CMB Stage III & & & & \\
-
 ~~~~~SPT-3G & 6\% & 3.0 & 200 & 1.2 \\
 ~~~~~Simons Array & 36\% & 9.5 & 200 & 3.5 \\ 
-\\
+\tiny \\ \small
 %\hline
@@
 Unless otherwise noted,  the Fisher matrix forecasts in this work use these numbers. 
-All forecasts also include beam and calibration uncertainties as noted in the text. 
+All forecasts also allow for beam and calibration uncertainties as noted in the text. 
 } \normalsize
@@
 
-We list the assumed survey areas, noise levels and beam sizes for each experiment in Table~\ref{tab:experiments}. 
-We  assume a 5\% uncertainty on the beam FWHM and a 1\% power calibration uncertainty; we have tested relaxing or tightening the beam and calibration uncertainty and find these calibration terms have a negligible impact on the PMF constraints.
-
 We consider the constraints on PMFs in two cosmologies. 
-The first is a 11-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf. 
+Our fiducial cosmology is a 11-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf. 
 Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species. 
-This 11-parameter model is our default cosmological model for forecasting future PMF constraints. 
-We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case with the tensor-to-scalar ratio, $r$. 
-The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B\,=\,-2.9$ is nearly identical.
-To illustrate the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf.
-In both cases, we also marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
+This 11-parameter model is our default cosmological model when forecasting future PMF constraints as these extensions are all well-motivated theoretically. 
+We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case and is with the tensor-to-scalar ratio, $r$. 
+The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B\,=\,-2.9$ is nearly identical on large angular scales.
+To test the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf.
+In both cases, we always marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
 We assume the galactic foregrounds are removed by a judicious combination of data from multiple frequencies.
 
-In this work, we only forecast the uncertainties due to power spectrum (i.e.~2-point estimators) searches for PMFs. 
+In this work, we restrict ourselves to power spectrum (i.e.~2-point estimators) searches for PMFs. 
 Currently the power spectrum limits from \planck{} or \pb{} are better than the 4-point upper limits. 
-Although outside the scope of this work, it would be interesting to extend this analysis to 4-point estimators for several reasons. 
+Although outside the scope of this work, it would be interesting to extend this analysis to 4-point estimators in the future. 
 First, the 4-point limits should improve faster as the noise level falls. 
@@
 \subsubsection{Beam and calibration uncertainties}
+\label{subsec:beamcal}
 

### 2017-02-03 pmf.tex
to 4.3.2

@@
 \newcommand{\mnu}{\ensuremath{\sum m_\nu}}
-\newcommand{\ukarcmin}{\ensuremath{\mu}K-arcmin}
+\newcommand{\ukarcmin}{\ensuremath{\mu}{\rm K-arcmin}}
 \newcommand{\lknee}{\ensuremath{\ell_{\rm knee}}}
@@
 
-The experiments that will begin taking data in 2017 will dramatically improve constraints on the PMF power. 
-With the minimal cosmological model, the 1-$\sigma$ forecasts for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a nearly-scale invariant PMF spectrum (i.e.~$n_B=-2.9$). 
-This is consistent with, although somewhat better than, the upper limits from the real data).  
-Adding the EE and BB bandpowers from the two stage III experiments (\sptnew{} and \simons{}) reduces the uncertainty by an order of magnitude in the 7-parameter model to $\sigma(\apmf)=0.015$. 
-The improvement is larger when including all eleven parameters, as the parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while only weakening the stage III constraint by a  more modest 40\%.
+The experiments that will begin taking data in 2017 will dramatically improve our knowledge of PMFs. 
+In the minimal cosmological model, the 1-$\sigma$ forecast for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a best-motivated, nearly-scale invariant PMF spectrum (i.e.~$n_B=-2.9$). 
+This is on-par with, although 30\% better than, the actual upper limit from the \planck{} data.  
+Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the 7-parameter model to $\sigma(\apmf)=0.015$. 
+The relative improvement is larger in the more realistic 11-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
 Thus within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
@@
 $n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
-The improvement from adding the SPT-3G and Simons Array experiments to \planck{} remains impressive.
+The improvement from adding the SPT-3G and Simons Array experiments to \planck{} remains impressive for these values of $n_B$.
 For the 11-parameter model and $n_B=-1$, adding SPT-3G and Simons Array to \planck{} leads to a 17-fold reduction in $\sigma(\apmf)$ from \fisherAlooseNbOneplk{} to \fisherAlooseNbOneSThree{}.
@@
 
-The primary motivation behind the proposed CMB stage-IV experiment commonly called CMB-S4 is to search for inflationary gravitational waves and neutrino masses.
+The primary motivations behind the proposed CMB-S4 experiments are to search for inflationary gravitational waves and to measure the neutrino masses.
 However, CMB-S4 would also enable extremely sensitive searches for PMFs. 
@@
 For this fiducial configuration and the 11-parameter model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes. 
-The exact values are $\sigma(\apmf^{n_B=-2.9}) =   \fisherAlooseSFour$, $\sigma(\apmf^{n_B=-1}) =   \fisherAlooseNbOneSFour$, and $\sigma(\apmf^{n_B=2}) =   \fisherAlooseNbTwoSFour$. 
+The expected uncertainties for CMB-S4 are $\sigma(\apmf^{n_B=-2.9}) =   \fisherAlooseSFour$, $\sigma(\apmf^{n_B=-1}) =   \fisherAlooseNbOneSFour$, and $\sigma(\apmf^{n_B=2}) =   \fisherAlooseNbTwoSFour$.
 These represent more than a 50-fold improvement on current limits.
 
-Given that CMB-S4 is currently in the design phase, it is also worthwhile to consider how design decisions will affect the final PMF constraints. 
-We look at five aspects of the experiment design: the instrumental sensitivity (as reflected by the map noise level), the telescope size or beam FWHM,  the low-$\ell$ noise performance (1/f knee), the choice of survey area,  and how well the beam size and calibration must be known.
-Of these five, we find that the first two to be very important and the second two to be somewhat important when optimizing for searches for PMFs. 
-As should be expected, the preferred design depends on the shape of the PMF spectrum ($n_B$) which controls  the relative power between large and small angular scales. 
-However, as was discussed in \S\ref{sec:template},  there are theoretical reasons to expect the PMF spectrum to be close to a scale-invariant spectra, as opposed to, e.g., $n_B=2$.
+Given that CMB-S4 is being designed, it is worth considering how design decisions would affect the final PMF constraints. 
+We look at five aspects of the experiment: the instrumental sensitivity (as reflected by the final noise level in the maps), the telescope size or beam FWHM,  the low-$\ell$ noise performance, the amount of sky surveyed,  and how well the beam shape and calibration must be known.
+Of these five aspects, we find the first two to be very important to PMF searches and the second two to be somewhat important. 
+As might be expected, in some cases the optimal design depends on the shape of the PMF spectrum ($n_B$) as this sets  the relative power between large and small angular scales.  
+However, as was discussed in \S\ref{sec:template},  there are theoretical reasons to expect the PMF spectrum to be close to a scale-invariant spectra. 
+While for completeness we present results for three values of $n_B$, we recommend favoring the optimum for $n_B=-2.9$.
 
@@
 
-Reducing the noise in CMB maps should always improve the derived constraints. 
+Reducing the noise in CMB maps will monotonically improve power spectrum measurements. 
 The goal of this section is to quantify the magnitude of that improvement: has the information gain saturated, or will further reductions in noise substantially improve PMF searches. 
@@
 For this figure, we have fixed the rest of the experimental configuration (i.e.~everything except the polarized noise levels) to the values of the CMB-S4 row in Table~\ref{tab:experiments}. 
-Clearly, continuing to improve the sensitivity of CMB experiments to CMB-S4 and beyond will be a boon to PMF searches. 
+Clearly, continuing to improve the sensitivity of CMB experiments to CMB-S4 and beyond will be a major boon to PMF searches. 
 In the general, 11-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered till the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
@@
   \caption[]{ \label{fig:sensitivity}
-  How the expected uncertainty on the PMF power scales with the polarized map noise. 
-  Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
+  How the PMF uncertainty  scales with the polarized map noise. 
+  Forecasts are shown as a function of the map noise in \ukarcmin{} for each of the three PMF spectral indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
   In the case of $n_B=2$, the uncertainties have been multiplied by a factor of $10^5$ to allow them to be plotted on the same scale. 
-  The black lines are for the conservative 11-parameter model, while the light blue lines are for the simple \lcdm{}+\apmf{} model. 
+  The black lines are for the fiducial 11-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
   The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the 11-parameter model due a degeneracy with the tensor-to-scalar ratio. 
-  The PMF constraints improve rapidly with lower noise levels in all three cases up to $\sim$\,1\,\ukarcmin, which is close to the  fiducial CMB-S4 noise levels. 
+  The PMF constraints improve rapidly with lower noise levels in all six cases up to $\sim$\,1\,\ukarcmin, which is close to the  fiducial CMB-S4 noise levels. 
     }
@@
   \caption[]{ \label{fig:beam}
- Larger telescopes (and smaller beams) will improve limits on the PMF power. 
- Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
-   In the $n_B=2$ case, the uncertainties have been multiplied by a factor of $10^5$ to allow them to be plotted on the same scale. 
-  The black lines are for the conservative 11-parameter model, while the light blue lines are for the simple \lcdm{}+\apmf{} model. 
+ Larger telescopes (and thus smaller beams) improve limits on the PMF power. 
+ Forecasts are shown as a function of the beam FWHM in arcminutes for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
+   In the $n_B=2$ case, the uncertainties have been multiplied by a factor of $10^5$ for plotting purposes. 
+  The black lines are for the fiducial 11-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
   The cosmological model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
@@
 
-Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
+Larger telescopes can recover more modes on the sky, and should therefore always improve the PMF constraints. 
 As shown in Fig.~\ref{fig:beam}, we find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered. 
-We find a local plateau between FWHMs of 4$^\prime$ to 6$^\prime$; improving the angular resolution in this range does not aid PMF searches. 
+We see a local plateau between FWHMs of 4$^\prime$ to 6$^\prime$; improving the angular resolution in this range does little to aid PMF searches. 
 We can understand this plateau by looking on the predicted PMF power in Fig.~\ref{fig:pmf-nb}. 
-All three templates have two peaks across this range of angular multiples, and we would expect such a plateau when, for instance, the resolution is adequate to resolve the first peak, but not yet sufficient to resolve the second peak.
+All three templates have two peaks across this range of angular multiples, and we would expect to see such a plateau when, for instance, the resolution is adequate to resolve the first peak, but not yet sufficient to resolve the second peak.
 The observed plateau positions are consistent with this hypothesis. 
- A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_B=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
+ Overall, a beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_B=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.
    The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant.
 
-However, larger telescopes are also more expensive to build which means for a fixed experimental budget, they would necessitate less ambitious focal planes and lower instantaneous mapping speed. 
+However, larger telescopes are also more expensive to build which means for a fixed experimental budget, they would necessitate less ambitious focal planes and lower instantaneous mapping speeds. 
 We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin{} for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin{} for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin{} for a FWHM of 1$^\prime$.
-We find 
-Improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_B = -2.9, -1, +2$ respectively.
+We find that 
+improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_B = -2.9, -1, +2$ respectively.
 However the results are close enough that the crudeness of the cost-neutral estimates used here could be a factor, and the preference might flip for more accurately costed setups. 
-In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one would likely lean towards adding more detectors. 
+In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one might lean towards adding more detectors. 
 %Raw sensitivity is important to an experiment's ability to study PMFs.

### 2017-02-03 pmf.tex
finished text (still figs)

@@
   The preferred survey area for PMF searches depends on the PMF spectral index. 
-    In the scale-invariant $n_B = -2.9$ case (solid line), we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
+    In the best-motivated, nearly scale-invariant $n_B = -2.9$ case (solid line), we find PMF searches should observe more than $\sim$\,15\%. 
  In contrast, for the cases where $n_B = -1, +2$ (dashed and dot-dashed lines), we find that observing  $\sim$\,10\% of the sky produces the best PMF constraints. 
@@
 
-A third question is whether it is better to integrate deeply on a small patch of sky or observe a wide area. 
-Unsurprisingly, we find opposing preferences for the scale-invariant $n_B=-2.9$ (which peaks at large angular scales) and the bluer $n_B=-1$ or 2 spectra which peak at small scales. 
+A third question is how much sky to observe with CMB-S4. 
+Unsurprisingly, we find opposing preferences for the nearly scale-invariant $n_B=-2.9$ (which peaks at large angular scales) and the bluer $n_B=-1$ or 2 spectra which peak at small scales. 
 As shown in  Fig.~\ref{fig:area}, for $n_B=-2.9$, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
@@
   \caption[Map knee dependence]{
-  The forecasted uncertainty on the PMF power, \apmf{}, falls as expected with decreasing low-frequency map noise for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, light blue line).
-  However,  the achieved map 1/f knee frequency makes no difference to the potential power of CMB-S4 PMF searches in the 11-parameter model (solid, black line). 
-  The change in behavior happens because the 11-parameter model introduces a degeneracy with r that shifts the angular scale of the PMF constraint to sub-degree scales. 
+  Recovering large angular scales is only important for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, light blue line). 
+The achieved map 1/f knee frequency makes no difference to CMB-S4 PMF searches in the 11-parameter model (black lines). 
+  For $n_B=-2.9$, this transition occurs because the 11-parameter model introduces a degeneracy with r on the large angular scales impacted by the map 1/f knee. 
   The 1/f knee frequency also makes no difference for the bluer PMF templates  (dashed and dash-dotted black lines) in either the restricted (light blue) or full 11-parameter (black) model space. 
@@
 
-Next we turn to the recovery of large angular scales, and the noise performance at low frequencies. 
-We look at the impact of shifting the 1/f knee of the map-space noise. 
-Effectively, we are multiplying the noise power, $N_\ell$, which is a constant for white noise,  by a function of angular multipole:
+Next we turn to the recovery of large angular scales on the sky, and the required noise performance at these low frequencies. 
+For this, we look at the impact of shifting the 1/f knee of the map-space noise. 
+Specifically, we are multiplying the noise power, $N_\ell$, which is a constant for white noise,  by a function of angular multipole:
 \be \label{eqn:knee}
@@
 This is consistent with the earlier statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
-For the bluer PMF spectra ($n_B=-1$ or 2), the forecasts have essentially no dependence on the knee frequency. 
-These results are consistent with the study of telescope size in the last section - which found that recovering smaller angular scales with larger telescopes helped (if one didn't consider cost).
-For a conservative 11-parameter model, our ability to separate a PMF from other physics is coming from sub-degree angular scales. 
+For the bluer PMF spectra ($n_B=-1$ or 2), the forecasts show no dependence on the knee frequency. 
+For the fiducial 11-parameter model, our ability to separate a PMF from other physics is coming from sub-degree angular scales. 
 %An instrument built to precisely measure gravitational lensing of the CMB should do very well at searching for PMFs. 
@@
 
-Finally, we consider if searches for PMFs introduce new requirements on the accuracy to which the instrumental beam or overall calibration of an experiment must be known. 
+Finally, we consider if searches for PMFs introduce new requirements on the accuracy to which the beam or  calibration of an experiment must be known. 
 We find they do not. 
@@
 
-In this work, we have improved the current upper limits on the strength of any primordial magnetic fields by including more CMB B-mode polarization data. 
+In this work, we have improved the current upper limits on the strength of   primordial magnetic fields by including more CMB B-mode polarization data. 
 By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
@@
 
-We have also shown that the next generation of experiments should dramatically reduce these limits, and potentially detect PMFs for the first time. 
-These so-called stage III experiments, which will begin taking data in 2017, expect to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a five-parameter extension to \lcdm.
+We have also shown that the next generation of experiments should dramatically reduce these limits, with the potential to detect PMFs for the first time. 
+These so-called stage III experiments, which will begin taking data in 2017, can be expected to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a five-parameter extension to \lcdm{} and foregrounds.
 
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$ \tbd{check these numbers}, and even non-ideal versions can easily set upper limits on order of $\apmf < 0.006$, i.e.~ a three-fold improvement over the forecasts for the stage III experiments and a 37-fold improvement over the current limits.
-We consider how the design of these experiments will impact the resulting PMF limits -- the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties -- and find sensitivity followed by telescope size to be the most important factors in predicting the PMF limits.
+We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$, and less optimistic versions can still set upper limits on order of $\apmf < 0.006$ in a 11-parameter cosmological model with  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf.
+This represents a three-fold improvement over the forecasts for the stage III experiments and a more than 100-fold improvement over the current limits. 
+We consider how the design of these experiments will impact the PMF limits, looking at the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties.
+We find experiment's sensitivity followed by telescope size to be the most important factors in predicting the PMF limits. 
 CMB-S4 will be a very exciting probe of PMFs and other sources of cosmic birefringence.

### 2017-02-04 pmf.tex
Scale-invariant spectrum

@@
 Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG, $n_B = -2.9$ and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
-\tbd{somewhere around here add arguments for $nb=-2.9$beinbg preferred} 
+\textcolor{red}{During the inflation, the quantum-mechanical zero-point fluctuations can generate a scale-invariant PMF with spectral index $n_B = -3$.
+This case is of particular interest because it is connected to the inflation, whereas other casual PMFs with bluer spectra are generated after inflation.}
 We also look at $n_B\,=\,-1$ and $n_B\,=\,2$ in the forecasting section. 

### 2017-02-06 pmf.tex
nb2.9 expos

--- 2017-02-03 pmf.tex
@@
 Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG, $n_B = -2.9$ and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
-\tbd{somewhere around here add arguments for $nb=-2.9$beinbg preferred} 
-We also look at $n_B\,=\,-1$ and $n_B\,=\,2$ in the forecasting section. 
+We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}. 
+We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{XXX}. 
+In contrast, \tbd{casual} PMFs with bluer spectra are generated by new physics after inflation \citep[e.g.,][]{YYY}. 
 We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 

### 2017-02-06 pmf.tex
figure clean up
minor text changes up to 4@

@@
 We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce twofold the 95\% CL upper limit on the CMB anisotropy power due to a PMF, from $\apmf < \upperAplk$ for Planck alone to $\apmf < \upperAall$ for the combined dataset . 
+We reduce twofold the 95\% CL upper limit on the CMB anisotropy power due to PMFs, from $\apmf < \upperAplk$ for \planck{} alone to $\apmf < \upperAall$ for the combined dataset. 
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
@@
 It is therefore common to simply quote effective limits on PMFs. 
-In this work, we present new upper limits from current CMB polarization data on the possibility of a PMF or parity-violating physics.
+In this work, we present new upper limits from current CMB polarization data on the possibility of PMFs or parity-violating physics.
 
@@
 High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
-These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
+These pairs should later annihilate at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
 The missing flux could be explained by the deflection of particles due to intergalactic magnetic fields. 
@@
 Here \bpmf{} is the rms field strength on a 1\,Mpc length scale. 
-The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{polarbear15}. 
+The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement \citep{polarbear15}. 
 The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < 3.9$\,nG. 
-Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{keisler15,bicepkeck15}, 
+Two other experiments, \sptpol{} and \bicepkeck{}, have also reported B-mode power spectrum measurements \citep{keisler15,bicepkeck15}, 
 and \citet{zucca16} reported constraints from the combination of the \planck{}  and \sptpol{} bandpowers. 
@@
 
+\begin{figure*}[htb]\centering
+\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
+  \caption[Current measurements of CMB B-modes]{
+  Current measurements of the CMB B-mode power spectrum. 
+    The black line shows the expected B-mode power spectrum in the \planck{} best-fit \lcdm{} cosmology (with the tensor-to-scalar ratio, r set to 0.01). 
+  The data sets are from POLARBEAR (black circles; \citet{polarbear14b}); ACTpol (dark green triangles; \citet{naess14});  BICEP2/Keck Array (red diamonds; \citet{bicepkeck15}); and SPTpol (purple squares; \citet{keisler15}).
+      The B-mode measurements used for the limits in this work are denoted with filled symbols. 
+      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments will significantly increase the signal-to-noise on the B-mode power spectrum. 
+           \label{fig:pmf-experiments}
+  }
+\end{figure*}
+
 We use a compendium of current measurements of the CMB temperature and polarization anisotropies from ground-based and satellite experiments. 
@@
 Finally, we include the latest BICEP2 and Keck Array  joint analysis \citep{bicepkeck15}. 
-This latter dataset also places limits on the tensor modes of a PMF due to its coverage of lower multipoles. 
+This last dataset also places limits on the tensor modes of a PMF due to its coverage of lower multipoles. 
 During the writing of this work, ACTpol polarization power spectra became available \citep{naess14,louis16}. 
@@
 CosmoMC invokes  CAMB\footnote{http://camb.info}  \citep{lewis00} to calculate the CMB power spectrum for each set of cosmological parameters. 
-Although CosmoMC and CAMB have a partial implementation of PMFs, we choose to adopt a simpler, fast template-based calculation for the PMF-sourced power. 
-We have adapted CosmoMC to add a scaled version of the template to all four CMB power spectra: TT, TE, EE, and BB, where the scale factor is \apmf. 
+Although CosmoMC and CAMB have a partial implementation of PMFs, we choose to adopt a simpler, fast, template-based calculation for the PMF-sourced power. 
+We have adapted CosmoMC to add a scaled version of a PMF template to all four CMB power spectra: TT, TE, EE, and BB, where the scale factor is \apmf. 
 \be
@@
 The calculation of the PMF template, \cpmf, is described in \S\ref{sec:template}. 
-Note that no other effect of  PMFs is considered; this is one reason we only consider CMB data.
+Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.
 
@@
 We sometimes also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
-Finally, in some cases, we allow non-zero tensors, parameterized by the tensor-to-scalar ratio, r.
+Finally, we sometimes allow non-zero tensors, parameterized by the tensor-to-scalar ratio, r.
 
@@
 \label{sec:template}
+
+\begin{figure*}[htb]\centering
+\includegraphics[width=0.9\textwidth,clip,trim={.5cm 12.cm 6cm 5cm}]{pmf_templates.pdf}
+  \caption[CMB polarization from PMFs]{
+  The expected sources of CMB B-modes.
+  The black line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology, while the red line corresponds to the B-modes due to inflationary gravitational waves for $r=0.05$.
+  The dashed blue line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
+  At $\ell < 200$, the tensor contribution from PMFs closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate on these angular scales in a power spectrum (2-point) analysis.
+      \label{fig:pmf-bb}
+  }
+\end{figure*}
 
@@
 Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{XXX}. 
-In contrast, \tbd{casual} PMFs with bluer spectra are generated by new physics after inflation \citep[e.g.,][]{YYY}. 
+In contrast, \tbd{casual} PMFs with bluer spectra require new physics after inflation \citep[e.g.,][]{YYY}. 
 We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
@@
 
-In the MCMC, we add a new scaling parameter, \apmf{}, that rescales the PMF power spectrum template. 
+As noted in the last section, the MCMC includes a  scaling parameter, \apmf{}, for the PMF power spectrum template. 
 We can translate the amplitude constraint on this template to a constraint on the r.m.s. magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
@@
 Note that the power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, which is not captured in the above expression. 
-An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed vector-mode power lead to only modestly better limits on the magnetic field strength.
+An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed power lead to only modestly better limits on the magnetic field strength. 
 However, if a PMF is detected, the steep scaling between \bpmf{} and the observed CMB B-mode power spectrum would allow excellent constraints on the PMF properties.
-
-\begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
-  \caption[Current measurements of CMB B-modes]{
-  Current measurements of CMB B-modes. 
-    The black line shows the expected B-mode power in the \planck{} best-fit \lcdm{} cosmology (with the tensor-to-scalar ratio, r set to 0.01). 
-  The data sets are from POLARBEAR (black circles; \citet{polarbear14b}); ACTpol (dark green triangles; \citet{naess14});  BICEP2/Keck Array (red diamonds; \citet{bicepkeck15}); and SPTpol (purple squares; \citet{keisler15}).
-      The B-mode measurements used for the limits in this work are denoted with filled circles; data not used has an open circle. 
-      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments will significantly increase the signal-to-noise on the B-mode power spectrum. 
-           \label{fig:pmf-experiments}
-  }
-\end{figure*}
-
-\begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.cm 12.cm 6cm 5cm}]{pmf_templates.pdf}
-  \caption[CMB polarization from PMFs]{
-  The expected sources of CMB B-modes.
-  The black line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology, while the red line corresponds to the B-modes due to inflationary gravitational waves for $r=0.05$.
-  The dashed blue line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
-  At $\ell < 200$, the tensor contribution from PMFs closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate on these angular scales in a power spectrum (2-point) analysis.
-      \label{fig:pmf-bb}
-  }
-\end{figure*}
 
@@
 Adding the ground-based experiments brings this limit to $\apmf <  \upperAall$. 
-We test which datasets are important by adding single datasets to the \planck{} data, and find that the majority of this improvement is due to the \bicepkeck{} ($\apmf <  \upperAbicep$) and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements.
+We test which datasets are important by adding single datasets to the \planck{} data, and find that the majority of this improvement is due to the \bicepkeck{}  
+B-mode power spectrum measurements: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$. 
+%and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements. 
 The other datasets do not have a large impact on the observed limits. 
@@
 The 95\% CL upper limit on \apmf{} drops slightly again.  
-This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms, r or \apmf{}.
+This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms, r and \apmf{}.
 
@@
 A pathfinder to CMB-S4, the Simons Observatory, was funded in 2016.
-We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and look at how to design CMB-S4 to maximize PMF searches.
+We examine the likely PMF constraints from the EE and BB power spectrum measurements with CMB-S4, and look at how to design CMB-S4 to maximize its potential for PMF searches.
 

### 2017-02-06 pmf.tex
ready to go!

@@
 
-To calculate the Fisher matrix for a CMB experiment, we need to calculate partial derivatives of the CMB spectra and the bandpower covariance matrix. 
+To calculate the Fisher matrix for a CMB experiment, we need the bandpower covariance matrix and partial derivatives of the CMB spectra. 
 The partial derivatives are calculated numerically from CAMB spectra  \citep{lewis00}. 
@@
 Second, in the case of a detection, the 4-point estimators would almost certainly come into play to learn more about the vector modes of the PMFs. 
-The detection (or non-detection) of the vector PMF signal in the 4-point estimators could also be used to argue for whether it is more likely that any observed tensor power is due to  inflationary gravitational waves or  PMFs.
+The detection (or non-detection) of the vector PMF signal in the 4-point estimators could then be used to argue for whether it is more likely that any observed tensor power is due to  inflationary gravitational waves or  PMFs.
 Finally, a lensing estimator might be used to `de-lense' the B-mode power spectrum, thereby suppressing the lensed B-mode signal and allowing better limits on PMFs. 
@@
 The relative improvement is larger in the more realistic 11-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
-Thus within the 11-parameter model however,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
+Thus within the 11-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
 The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
@@
 
-The primary motivations behind the proposed CMB-S4 experiments are to search for inflationary gravitational waves and to measure the neutrino masses.
+The primary motivations behind the proposed CMB-S4 experiment are to search for inflationary gravitational waves and to measure the neutrino masses.
 However, CMB-S4 would also enable extremely sensitive searches for PMFs. 
 We begin by considering our fiducial CMB-S4 configuration, as laid out in Table~\ref{tab:experiments}. 
-For this fiducial configuration and the 11-parameter model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes. 
+For this fiducial configuration and the 11-parameter cosmological model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes. 
 The expected uncertainties for CMB-S4 are $\sigma(\apmf^{n_B=-2.9}) =   \fisherAlooseSFour$, $\sigma(\apmf^{n_B=-1}) =   \fisherAlooseNbOneSFour$, and $\sigma(\apmf^{n_B=2}) =   \fisherAlooseNbTwoSFour$.
@@
 However, as was discussed in \S\ref{sec:template},  there are theoretical reasons to expect the PMF spectrum to be close to a scale-invariant spectra. 
-While for completeness we present results for three values of $n_B$, we recommend favoring the optimum for $n_B=-2.9$.
+While for completeness we present results for three values of $n_B$, we recommend favoring the optima for $n_B=-2.9$.
 
@@
   The black lines are for the fiducial 11-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
-  The cosmological model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
+  The cosmological model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size becomes less important. 
   The plateau near 4$^\prime$ for $n_B=-1, +2$ is where the gain from the $\ell\sim3000$ peak is saturated, but the resolution isn't yet adequate to pick up the next peak at $\ell > 8000$ (see  Fig.~\ref{fig:pmf-nb}).
@@
 improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_B = -2.9, -1, +2$ respectively.
-However the results are close enough that the crudeness of the cost-neutral estimates used here could be a factor, and the preference might flip for more accurately costed setups. 
+However the results are close enough that the crudeness of the cost-neutral estimates used here is a worry, and the preference might flip for more accurately costed setups. 
 In short,  the tradeoff between larger telescopes or more detectors is largely a wash, although one might lean towards adding more detectors. 
@@
 A third question is how much sky to observe with CMB-S4. 
-Unsurprisingly, we find opposing preferences for the nearly scale-invariant $n_B=-2.9$ (which peaks at large angular scales) and the bluer $n_B=-1$ or 2 spectra which peak at small scales. 
-As shown in  Fig.~\ref{fig:area}, for $n_B=-2.9$, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
+Unsurprisingly, we find opposing preferences for the nearly scale-invariant $n_B=-2.9$ (which peaks at large angular scales) and the bluer $n_B=-1$ or 2 spectra which peak at smaller scales. 
+As shown in  Fig.~\ref{fig:area}, observing at least 15\% of the sky is very important to a search for nearly scale-invariant PMFs, and it is best  to cover as much sky as possible. 
 A caveat to this analysis is that it is likely easier to remove galactic foregrounds to a specified level on targeted, `clean' patches as opposed to a substantial fraction of the sky, and we would expect galactic foregrounds to be important for the large angular scales.
 With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and are nearly flat (a 6\% improvement) from 25\% to 70\% of the sky (the widest area likely to be possible after galactic cuts).
-Conversely, $n_B=-1$ or +2, the optimal survey area is smaller at 10\% of the full sky. 
+Conversely for $n_B=-1$ or +2, the optimal survey area is smaller at 10\% of the full sky. 
 Note however that the minimum is extremely broad with only a 10\% worsening of the expected uncertainty as the survey area is increased from 10\% to 70\% of the  full sky. 
@@
 We generally find the forecasts to be insensitive to the 1/f knee or galactic foreground removal at the default beam size of 4$^\prime$. 
-It appears that even in the nearly scale-invariant case, the PMF constraint is being driven by smaller angular scales due to the the degeneracy with the tensor-to-scalar ratio at large angular scales.
+It appears that even in the nearly scale-invariant case, the PMF constraint is coming primarily from smaller angular scales due to the the degeneracy with the tensor-to-scalar ratio at large angular scales.
 Without this degeneracy, i.e. in the simple \lcdm{}+\apmf{} model, dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 3.2 for a nearly scale-invariant PMF. 
-In this case, the degradation accelerates once the 1/f knee goes above $\ell \simeq 70$. 
+In this case, the degradation accelerates once the 1/f knee rises to $\lknee{} \gtrsim 70$. 
 This is consistent with the earlier statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
@@
 We find they do not. 
-We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
-We find negligible, sub-percent shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
+We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of s Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
+We find negligible, sub-percent shifts in the forecasted PMF uncertainties for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
 The PMF constraints  for all three power law indices considered are insensitive to the beam and calibration uncertainties.
@@
 In this work, we have improved the current upper limits on the strength of   primordial magnetic fields by including more CMB B-mode polarization data. 
-By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we find the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
-The biggest contributor to this improvement is the low-$\ell$ data from \bicepkeck{}.
+By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we have found the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
+The biggest contributor to this improvement is the low-$\ell$ B-mode data from \bicepkeck{}.
 
 We have also shown that the next generation of experiments should dramatically reduce these limits, with the potential to detect PMFs for the first time. 
-These so-called stage III experiments, which will begin taking data in 2017, can be expected to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a five-parameter extension to \lcdm{} and foregrounds.
+The so-called stage III experiments, which will begin taking data in 2017, can be expected to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a five-parameter extension to \lcdm{} and foregrounds.
 
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We show that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$, and less optimistic versions can still set upper limits on order of $\apmf < 0.006$ in a 11-parameter cosmological model with  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf.
-This represents a three-fold improvement over the forecasts for the stage III experiments and a more than 100-fold improvement over the current limits. 
-We consider how the design of these experiments will impact the PMF limits, looking at the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties.
-We find experiment's sensitivity followed by telescope size to be the most important factors in predicting the PMF limits. 
+We have shown that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$, and less optimistic versions can still set upper limits on order of $\apmf < 0.006$ in a 11-parameter cosmological model with  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf.
+This represents a three-fold improvement over the forecasts for the stage III experiments and a more than 100-fold improvement over the current limits for this cosmological model. 
+We have considered how the design of future experiments will impact the resulting PMF limits, looking at the experimental sensitivity, angular resolution, survey area, low-frequency noise performance, and beam or calibration uncertainties.
+We have found an experiment's sensitivity followed by telescope size to be the most important factors in predicting the PMF limits. 
 CMB-S4 will be a very exciting probe of PMFs and other sources of cosmic birefringence.

### 2017-02-06 pmf.tex
added source for scale invariant spectral index

--- 2017-02-06 pmf.tex
@@
 We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
-Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{XXX}. 
-In contrast, \tbd{casual} PMFs with bluer spectra are generated by new physics after inflation \citep[e.g.,][]{YYY}. 
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep{Mack:2001gc}. 
+In contrast, \tbd{casual} PMFs with bluer spectra are generated by new physics after inflation \citep[Vachaspati][]{YYY}. 
 We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
@@
 \begin{figure*}[htb]\centering
-\includegraphics[width=0.9\textwidth,clip,trim={1.cm 12.cm 6cm 5cm}]{pmf_templates.pdf}
+\includegraphics[width=0.9\textwidth,clip,trim={.5cm 12.cm 6cm 5cm}]{pmf_templates.pdf}
   \caption[CMB polarization from PMFs]{

### 2017-02-06 pmf.tex

--- 2017-02-06 pmf.tex
@@
 We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
-Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{XXX}. 
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{mack01}. 
 In contrast, \tbd{casual} PMFs with bluer spectra require new physics after inflation \citep[e.g.,][]{YYY}. 

### 2017-02-06 pmf.tex
try to arxiv format

--- 2017-02-06 pmf.tex
@@
 \documentclass[apj]{emulateapj}
+\pdfoutput=1
 %\documentclass[preprint2]{aastex61}
@@
 \usepackage{soul}
+
+\newcommand{\jcap}{JCAP}
 
@@
 We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
-Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{XXX}. 
-In contrast, \tbd{casual} PMFs with bluer spectra require new physics after inflation \citep[e.g.,][]{YYY}. 
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01, }. 
+In contrast,  PMFs with bluer spectra require new physics after inflation \citep[e.g.,][]{YYY}. 
 We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 

### 2017-02-06 pmf.tex
some refs
debtable change

@@
 We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
-Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01, }. 
-In contrast,  PMFs with bluer spectra require new physics after inflation \citep[e.g.,][]{YYY}. 
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01}.%\footnote{We select $n_B = -2.9$ as opposed to another number near -3 to facilitate comparison to other PMF papers.}
+In contrast, causal PMFs with bluer spectra require later phase transitions or other new physics after inflation \citep[e.g.,][]{durrer03, subramanian16}. 
 We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 

### 2017-02-06 pmf.tex
refs added

--- 2017-02-06 pmf.tex
@@
 We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
-Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{mack01}. 
-In contrast, \tbd{casual} PMFs with bluer spectra require new physics after inflation \citep[e.g.,][]{YYY}. 
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$.
+In contrast, causal PMFs with bluer spectra require new physics after inflation~\cite{2008PhRvD..78f3012K, 2002PhRvD..65l3004M}.
 We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 

### 2017-02-06 pmf.tex

--- 2017-02-06 pmf.tex
@@
 \documentclass[apj]{emulateapj}
-\pdfoutput=1
 %\documentclass[preprint2]{aastex61}
@@
 We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
-Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01, }. 
-In contrast,  PMFs with bluer spectra require new physics after inflation \citep[e.g.,][]{YYY}. 
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01,2008PhRvD..78f3012K}.%\footnote{We select $n_B = -2.9$ as opposed to another number near -3 to facilitate comparison to other PMF papers, while avoiding the singularity at -3.}
+In contrast, causal PMFs with bluer spectra require later phase transitions or other new physics after inflation \citep[e.g.,][]{durrer03, subramanian16}. 
 We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 

### 2017-02-07 pmf.tex
author names
added initial
grammar

@@
 \title{Current and future constraints on primordial magnetic fields}
-\author{D.~Sutton\altaffilmark{\Melbourne}, C.~Feng\altaffilmark{\uci}, and C.~L.~Reichardt\altaffilmark{\Melbourne}}
+\author{Dylan~R.~Sutton\altaffilmark{\Melbourne}, Chang~Feng\altaffilmark{\uci}, and Christian~L.~Reichardt\altaffilmark{\Melbourne}}
 \altaffiltext{\Melbourne}{School of Physics, University of Melbourne, Parkville, VIC 3010, Australia}
@@
 We find a 95\% limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-this is somewhat better then the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
+this is somewhat better than the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
 The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16} codes. 

### 2017-02-07 pmf.tex
grammar

@@
 Clearly, continuing to improve the sensitivity of CMB experiments to CMB-S4 and beyond will be a major boon to PMF searches. 
-In the general, 11-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered till the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
+In the general, 11-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered until the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
 
@@
 We find they do not. 
-We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of s Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
+We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of a Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
 We find negligible, sub-percent shifts in the forecasted PMF uncertainties for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 

### 2017-02-07 pmf.tex
keywords cosmic background radiation --- early universe --- magnetic fields --- polarization
grammar, planck sources updated, made the Polarbear text look cooler

@@
 \newcommand{\sptnew}{SPT-3G}
-\newcommand{\pb}{POLARBEAR}
+\newcommand{\pb}{\textsc{Polarbear}}
 \newcommand{\simons}{Simons Array}
@@
 
-\keywords{dark energy --- cosmic background radiation --- early universe }
+\keywords{ cosmic background radiation --- early universe --- magnetic fields --- polarization }
 \section{Introduction}
@@
 With the CMB power spectrum data that will be the focus of this paper, \citet{planck15-19} find 95\% CL upper limits ranging from $\bpmf < 5.6$\,nG to $<0.7$\,nG depending on the exact model. 
-Here \bpmf{} is the rms field strength on a 1\,Mpc length scale. 
+Here \bpmf{} is the rms magnetic field strength on a 1\,Mpc length scale. 
 The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement \citep{polarbear15}. 
@@
 We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
-Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01,2008PhRvD..78f3012K}.%\footnote{We select $n_B = -2.9$ as opposed to another number near -3 to facilitate comparison to other PMF papers, while avoiding the singularity at -3.}
+Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01,2008PhRvD..78f3012K}.
+%\footnote{We select $n_B = -2.9$ as opposed to another number near -3 to facilitate comparison to other PMF papers, while avoiding the singularity at -3.}
 In contrast, causal PMFs with bluer spectra require later phase transitions or other new physics after inflation \citep[e.g.,][]{durrer03, subramanian16}. 
-We have compared calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
+We have compared the calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
 We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
 The origin of the difference is unclear. 
-We have chosen to use the  more recent \citet{zucca16} code instead of CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts. 
+We have chosen to use the  more recent \citet{zucca16} code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
@@
 %and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements. 
-The other datasets do not have a large impact on the observed limits. 
+The other datasets do not have a large impact on the observed limits for a scale-invariant PMF, although they would for bluer PMFs. 
 In short, the factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
@@
 The 95\% CL upper limit on \apmf{} drops slightly again.  
-This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms, r and \apmf{}.
+This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms: r and \apmf{}.
 
@@
 We therefore importance sample the chains to apply a flat prior on \bpmf. 
-We find a 95\% limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
+We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
 this is somewhat better than the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
@@
 In this work, we have improved the current upper limits on the strength of   primordial magnetic fields by including more CMB B-mode polarization data. 
-By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we have found the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
+By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we have found that the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
 The biggest contributor to this improvement is the low-$\ell$ B-mode data from \bicepkeck{}.

### 2017-04-13 response.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{soul}

\usepackage[usenames, dvipsnames]{color}

\begin{document}

Dear Editor,
\\

We'd like to thank the reviewer for their time, carefully reading our paper and providing their valuable feedback. Below we address their feedback and list the changes we've made to the paper in response.
\\

\textcolor{blue}{The reviewer's feedback is shown in blue.}

Our response to the feedback will be included in black.

\textcolor{PineGreen}{The changed sections in our paper will then be included below in green \textbf{with additions presented in boldface} and removed sections presented with a strike through them.}
\\

\textcolor{blue}{The end of the 2nd paragraph says that this work constrains the possibility of PMFs "or parity-violating physics". As far as I can tell, the analysis uses only parity-even spectra, such as TT, TE, EE and BB. The authors should either clarify what they mean or remove the claim.}

In addition to producing a non-zero EB and TB power spectrum, PMFs and other parity-violating physics are also known to convert EE power into BB power. By looking for excess power in the BB power spectrum we can find the strength of PMFs or equate the effects of parity-violating physics to an equivalent PMF field strength.

\textcolor{PineGreen}{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (\citep{carroll98,lue99}) or primordial magnetic fields (PMFs) (\citep{kosowsky96, seshadri01}).  
Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.  }
\\

\textcolor{blue}{The work assumes a fixed PMF template based on a model with a fixed value of the PMF generation time: $a_{\nu}/a_{PMF}$. This parameter is entirely arbitrary, and directly determines the amplitude of the tensor mode, which is responsible for the tight bound the authors get from BICEP2/Keck. I think it is misleading to present bounds based on this assumption as bounds on PMF. The authors should, at the very least, add a discussion of how the bound changes if one allows the PMF generation time to be a free parameter that is marginalized over. In such a case, the bound will be dominated by the vector mode contribution, with SPTPol likely dominating the constraints.}

As per the advice of the reviewer we have removed any mention of the CMBACT code.

\textcolor{PineGreen}{
\st{
We have compared the calculated templates to the outputs of the earlier CMBACT-derived code.
We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
The origin of the difference is unclear.
We have chosen to use the more recent (Zucca16) code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}
\textbf{We use the code from zucca16 which allows us to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}}
\\

\textcolor{PineGreen}{
We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
this is somewhat better than the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done.}
\textcolor{PineGreen}{
\st{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16}}}
\textcolor{PineGreen}{
\textbf{The improvement comes from our choice of value for the PMF generation time versus the decision in \citet{planck15-19} to marginalise over PMF generation time altogether.}}
\textcolor{PineGreen}{
\st{Using the CMBACT-derived code that planck15-19 used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.
Returning to} \textbf{Using} the \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is  reduced only slightly to $\bpmf < \upperBall$\,nG.}
\\

\textcolor{blue}{The authors report a factor of 2 difference in the normalization of the tensor mode between the public code provided by Zucca et al and a "CMBACT-derived code", saying that "the origin of the difference is unclear". The public version of CMBACT is a code for CMB anisotropies from cosmic strings and does not concern PMFs. Any code that the authors might have used would be a private modification. Either the authors should clarify what code they are referring to, or avoid mentioning it.}

\textcolor{pinegreen}{}
\\

\textcolor{blue}{In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same
parameters) between the CMBACT-derived and Zucca et al. (2016) codes". The also claim that Planck used "the CMBACT-derived" code. This is a false claim. Firstly, see the point 3 above. Secondly, as far as I know, Planck used a private code written primarily by Daniela Paoletti.}

\textcolor{blue}{Instead, the "improvement" comes from the fact that the analysis by Planck collaboration (as well as Zucca et al) marginalized over the PMF generation time, which negated the contribution of the PMF tensor modes to the constraints.}

\textcolor{blue}{In summary, I think the paper contains some claims that need revisiting. I suggest repeating the analysis with the PMF generation time set free and report the bounds in that case. Only then they can be seriously compared to previous results in the literature.}

\end{document}

### 2017-04-13 pmf.tex
junk
submit

@@
 The constraints from CMB-S4 have the potential to rule out much of the parameter space for PMFs.
-
 \end{abstract}
@@
 CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or primordial magnetic fields (PMFs) \citep{kosowsky96, seshadri01}.
-Both effects lead to the rotation of E-modes into B-modes. 
+Both effects lead to the rotation of E-modes into B-modes \textcolor{red}{which leads to an increase in power in the BB spectrum.}
 By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
@@
 In contrast, causal PMFs with bluer spectra require later phase transitions or other new physics after inflation \citep[e.g.,][]{durrer03, subramanian16}. 
-We have compared the calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} \citep{pogosian99}. 
+\st{
+We have compared the calculated templates to the outputs of the earlier CMBACT-derived code}\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}}
+}
+\citep{pogosian99}.
+\st{
 We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
 The origin of the difference is unclear.
-We have chosen to use the  more recent \citet{zucca16} code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.
+}
+\st{We have chosen to use the more recent} \citet{zucca16} \st{code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}
+\textcolor{red}{We use the code from} \citet{zucca16} \textcolor{red}{which allows us to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
@@
 this is somewhat better than the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16} codes. 
-Using the CMBACT-derived code that \citet{planck15-19} used, we find a consistent upper limit of $\bpmf < 1.9$\,nG. 
-Returning to the  \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is  reduced only slightly to $\bpmf < \upperBall$\,nG. 
+\st{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and} \citet{zucca16} \st{codes.}
+\textcolor{red}{The improvement comes from our choice of value for the PMF generation time versus the decision in} \citet{planck15-19} \textcolor{red}{to marginalise over PMF generation time altogether.}
+\st{Using the CMBACT-derived code that} \citet{planck15-19} \st{used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.
+Returning to} \textcolor{red}{Using} the  \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is  reduced only slightly to $\bpmf < \upperBall$\,nG. 
 The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero. 

### 2017-04-19 pmf.tex
starting to propagate upodates

@@
 
-\newcommand{\jcap}{JCAP}
+%\newcommand{\jcap}{JCAP}
 
@@
 \newcommand{\cpmf}{\ensuremath{C_{\ell}^{\rm PMF}}}
+
+\newcommand{\cpmftens}{\ensuremath{C_{\ell}^{\rm PMF,\,tens}}}
+\newcommand{\cpmfvec}{\ensuremath{C_{\ell}^{\rm PMF,\,vec}}}
 \newcommand{\apmf}{\ensuremath{A_{\rm PMF}}}
@@
 \newcommand{\gab}[1]{\textcolor{Orchid}{[{\bf GS}: #1]}}
-
+\newcommand{\changed}[1]{\textcolor{Red}{#1}}
+\newcommand{\removed}[1]{\textcolor{Red}{}}
 \include{number_list}
@@
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
+%\changed{Most of the improvement is due to the addition of the \bicepkeck{} and \sptpol{} data.} 
 We also forecast the expected  limits from soon-to-deploy CMB experiments (like \sptnew{},  \advactpol, or the \simons) and the proposed CMB-S4 experiment. 
@@
 CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence \citep{carroll98,lue99} or primordial magnetic fields (PMFs) \citep{kosowsky96, seshadri01}.
-Both effects lead to the rotation of E-modes into B-modes \textcolor{red}{which leads to an increase in power in the BB spectrum.}
+Both effects lead to the rotation of E-modes into B-modes, thereby increasing the amplitude of the BB power spectrum.
 By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength. 
@@
 \be
-C_\ell = C_\ell^{\rm{CAMB}} + \apmf \cpmf
+\changed{C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]}
 \ee
-The calculation of the PMF template, \cpmf, is described in \S\ref{sec:template}. 
+\changed{The calculation of the PMF templates, \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
+The parameter $\beta$ relates the timing of neutrino decoupling and the generation of the PMF, and is defined by $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$, where $a_x$ represents the scale factor at the respective events.
+}
 Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.
 
-For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to PMFs. 
+For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \changed{2 parameters, \apmf{} and $\beta$, }describing the power due to PMFs.
 We adopt flat priors on all parameters. 
-In particular, note that this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
+\changed{There are two points to note about the PMF priors. 
+First, this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
+In the current era of upper limits, this prior choice has some impact on the resulting PMF limits. 
+Second, the exact range of the uniform prior on $\beta$ matters. 
+Here we follow \citet{planck15-19} and \citet{zucca16} and use $\beta \in [11.513, 41.447]$.\footnote{This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$.}
+However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
+If we follow \citet{polarbear15} who used $\beta \in [0,39]$, the \planck-only upper limit is nearly eight times higher, and the combined dataset limit nearly two times higher. }
 We sometimes also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
@@
 We can translate the normalization, $A_B$, into more physically-motivated units by calculating the rms of the PMF field strength over a length scale of 1\,Mpc, which we will call \bpmf. 
-Finally, the timing of when PMFs are generated relative to neutrino decoupling matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
-The timing is typically parametrized by the ratio of the scale factors at neutrino decoupling and PMF generation, $a_{\nu}/a_{\rm{PMF}}$.
+\changed{
+Finally, the timing of when PMFs are generated relative to neutrino decoupling matters for the tensor component because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos.
+The timing is  parametrized by $\beta = ln(a_{\nu}/a_{\rm{PMF}})$,  the natural logarithm of the ratio of the scale factors at neutrino decoupling and PMF generation. 
+}
 
@@
 In contrast, causal PMFs with bluer spectra require later phase transitions or other new physics after inflation \citep[e.g.,][]{durrer03, subramanian16}. 
-\st{
-We have compared the calculated templates to the outputs of the earlier CMBACT-derived code}\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}}
-}
-\citep{pogosian99}.
+\removed{
+We have compared the calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}}
+\citep{pogosian99}.}
+
 \st{
@@
 \ee
-Note that the power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, which is not captured in the above expression. 
 An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed power lead to only modestly better limits on the magnetic field strength. 
 However, if a PMF is detected, the steep scaling between \bpmf{} and the observed CMB B-mode power spectrum would allow excellent constraints on the PMF properties.
+
+\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
+We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
+\be \label{eqn:betascaling}
+\apmf^{tens} \propto \beta^{1.9},
+\ee
+to an excellent approximation. 
+We use this $\beta$ power law form to handle the PMF timing dependence. }
 
@@
 Adding the ground-based experiments brings this limit to $\apmf <  \upperAall$. 
-We test which datasets are important by adding single datasets to the \planck{} data, and find that the majority of this improvement is due to the \bicepkeck{}  
-B-mode power spectrum measurements: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$. 
+We test which datasets are important by adding single datasets to the \planck{} data, \changed{and find that the source of the improvement is evenly split between \sptpol{} and \bicepkeck{}. 
+Adding either one to \planck{} yields the same upper limit: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$ versus  $\apmf^{\planck+\sptpol}) < \upperAsptpol$. 
+Extending the $\beta$ prior to lower values would shift the relative weight more towards \sptpol{} (and vice-versa). 
+}
 %and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements. 
@@
 First, we vary the largest source of  B-mode power, gravitational lensing, by allowing \alens{} to float. 
-Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power). 
+Somewhat counterintuitively, the limits are \changed{somewhat} better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power).
 In this case for  Planck alone, the 95\% confidence upper limit is $\apmf <  \upperAplkalens$, dropping to $\apmf <  \upperAallalens$ with the ground-based experiments. 
 Next we introduce inflationary gravitational waves, as parameterized by the tensor-to-scalar ratio r. 
-The 95\% CL upper limit on \apmf{} drops slightly again.  
+The 95\% CL upper limit on \apmf{} drops \st{slightly} again.  
 This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms: r and \apmf{}.
@@
 this is somewhat better than the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
+\changed{It is possible the difference is due to poor sampling of low values of \bpmf{} when importance sampling the chain. }
 \st{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and} \citet{zucca16} \st{codes.}
-\textcolor{red}{The improvement comes from our choice of value for the PMF generation time versus the decision in} \citet{planck15-19} \textcolor{red}{to marginalise over PMF generation time altogether.}
-\st{Using the CMBACT-derived code that} \citet{planck15-19} \st{used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.
-Returning to} \textcolor{red}{Using} the  \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is  reduced only slightly to $\bpmf < \upperBall$\,nG. 
+\st{Using the CMBACT-derived code that} \citet{planck15-19} \st{used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.}
+\changed{Adding the ground-based polarization measurements reduces the 95\% CL upper limit only slightly to $\bpmf < \upperBall$\,nG. }
 The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero. 
@@
 We consider the constraints on PMFs in two cosmologies. 
-Our fiducial cosmology is a 11-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf. 
+Our fiducial cosmology is a \changed{12}-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf{} \changed{ + $\beta$}.
 Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species. 
-This 11-parameter model is our default cosmological model when forecasting future PMF constraints as these extensions are all well-motivated theoretically. 
-We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case and is with the tensor-to-scalar ratio, $r$. 
+This \changed{12}-parameter model is our default cosmological model when forecasting future PMF constraints as these extensions are all well-motivated theoretically. 
+We have examined the degree to which \apmf{} is degenerate with the 10 parameters unrelated to PMFs -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case and is with the tensor-to-scalar ratio, $r$.
 The reason for this degeneracy is illustrated in Fig.~\ref{fig:pmf-bb}, which shows that the tensor mode power due to inflationary gravitational waves and a PMF with $n_B\,=\,-2.9$ is nearly identical on large angular scales.
-To test the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' 7-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf.
+To test the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' \changed{8}-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf{} \changed{ + $\beta$}.
 In both cases, we always marginalize over unknown Poisson EE and BB  terms due to polarized extragalactic sources. 
@@
 Such de-lensing techniques have long been proposed for inflationary gravitational wave searches \citep[e.g.][]{knox02,kesden02,seljak04a,simard15} and more recently been demonstrated on real \planck{} data \citep{larsen16}.
-
-%As a sanity check, we look at the Fisher matrix forecasts for Planck alone as well in both of these cases. 
-%For both chains,  we look at the sigma in MCMC with \apmf{} allowed to go negative. 
-%While a negative \apmf{} is unphysical, this insulates the analysis against the data preferring negative values, and thereby producing tighter limits. 
-%We find for \lcdm{}  + \apmf{}: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
-%We find for the 11-parameter model: $\sigma(\apmf) = XX$ (to be compared to YY from the Fisher matrix). 
-%This degree of consistency is reasonable. \tbd{}
 
@@
 
-We thank Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
+We thank the \changed{referee as well as} Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
 C. Reichardt is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 

### 2017-04-19 pmf.tex
more propagation

@@
 For the real data, we focus on the most theoretically motivated scenario of an approximately scale-invariant spectrum for the PMFs ($n_B=-2.9$), although we will consider other scenarios in the forecasts of the next section.
-The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \planck{} alone in the simple 7-parameter model. 
-The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}. 
+The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \planck{} alone in the simple \changed{8}-parameter model. 
+The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+PMF. 
 Adding the ground-based experiments brings this limit to $\apmf <  \upperAall$. 
@@
 This is on-par with, although 30\% better than, the actual upper limit from the \planck{} data.  
-Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the 7-parameter model to $\sigma(\apmf)=0.015$. 
-The relative improvement is larger in the more realistic 11-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
-Thus within the 11-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
+Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the \changed{8}-parameter model to $\sigma(\apmf)=0.015$. 
+The relative improvement is larger in the more realistic \changed{12}-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
+Thus within the \changed{12}-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
 The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
-$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other 11-parameters.
+$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the \changed{other} parameters.
 The improvement from adding the SPT-3G and Simons Array experiments to \planck{} remains impressive for these values of $n_B$.
-For the 11-parameter model and $n_B=-1$, adding SPT-3G and Simons Array to \planck{} leads to a 17-fold reduction in $\sigma(\apmf)$ from \fisherAlooseNbOneplk{} to \fisherAlooseNbOneSThree{}.
+For the \changed{12}-parameter model and $n_B=-1$, adding SPT-3G and Simons Array to \planck{} leads to a 17-fold reduction in $\sigma(\apmf)$ from \fisherAlooseNbOneplk{} to \fisherAlooseNbOneSThree{}.
 For $n_B=2$, there is a 20-fold reduction from $\sigma(\apmf) = \fisherAlooseNbTwoplk$ to  \fisherAlooseNbTwoSThree. 
@@
 We begin by considering our fiducial CMB-S4 configuration, as laid out in Table~\ref{tab:experiments}. 
-For this fiducial configuration and the 11-parameter cosmological model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes. 
+For this fiducial configuration and the \changed{12}-parameter cosmological model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes. 
 The expected uncertainties for CMB-S4 are $\sigma(\apmf^{n_B=-2.9}) =   \fisherAlooseSFour$, $\sigma(\apmf^{n_B=-1}) =   \fisherAlooseNbOneSFour$, and $\sigma(\apmf^{n_B=2}) =   \fisherAlooseNbTwoSFour$.
@@
 The goal of this section is to quantify the magnitude of that improvement: has the information gain saturated, or will further reductions in noise substantially improve PMF searches. 
-Figure~\ref{fig:sensitivity} shows the uncertainty on \apmf{} as a function of the map noise level for the three PMF templates in either the 11 or 7-parameter cosmological models. 
+Figure~\ref{fig:sensitivity} shows the uncertainty on \apmf{} as a function of the map noise level for the three PMF templates in either the \changed{12} or \changed{8}-parameter cosmological models. 
 For this figure, we have fixed the rest of the experimental configuration (i.e.~everything except the polarized noise levels) to the values of the CMB-S4 row in Table~\ref{tab:experiments}. 
 Clearly, continuing to improve the sensitivity of CMB experiments to CMB-S4 and beyond will be a major boon to PMF searches. 
-In the general, 11-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered until the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
+In the general, \changed{12}-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered until the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
 
@@
   In the case of $n_B=2$, the uncertainties have been multiplied by a factor of $10^5$ to allow them to be plotted on the same scale. 
-  The black lines are for the fiducial 11-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
-  The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the 11-parameter model due a degeneracy with the tensor-to-scalar ratio. 
+  The black lines are for the fiducial \changed{12}-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
+  The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the \changed{12}-parameter model due a degeneracy with the tensor-to-scalar ratio. 
   The PMF constraints improve rapidly with lower noise levels in all six cases up to $\sim$\,1\,\ukarcmin, which is close to the  fiducial CMB-S4 noise levels. 
@@
    In the $n_B=2$ case, the uncertainties have been multiplied by a factor of $10^5$ for plotting purposes. 
-  The black lines are for the fiducial 11-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
+  The black lines are for the fiducial \changed{12}-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
   The cosmological model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size becomes less important. 
@@
    Note that in the case of $n_B=2$, the uncertainties have been multiplied by a factor of $10^5$ for plotting purposes. 
-   There is essentially no difference to the preferred areas between the 11-parameter cosmological model (black) or the restricted \lcdm{}+\apmf{} 7-parameter model (light blue). 
+   There is essentially no difference to the preferred areas between the \changed{12}-parameter cosmological model (black) or the restricted \lcdm{}+\changed{PMF 8}-parameter model (light blue). 
      Fortunately, the minima for all three templates are relatively broad, and a survey covering 15+\% of the sky will do well for all values of the PMF spectral index. 
@@
   \caption[Map knee dependence]{
-  Recovering large angular scales is only important for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\apmf{} 7-parameter model (solid, light blue line). 
-The achieved map 1/f knee frequency makes no difference to CMB-S4 PMF searches in the 11-parameter model (black lines). 
-  For $n_B=-2.9$, this transition occurs because the 11-parameter model introduces a degeneracy with r on the large angular scales impacted by the map 1/f knee. 
-  The 1/f knee frequency also makes no difference for the bluer PMF templates  (dashed and dash-dotted black lines) in either the restricted (light blue) or full 11-parameter (black) model space. 
+  Recovering large angular scales is only important for a nearly scale-invariant PMF ($n_B = -2.9$) in the restricted \lcdm{}+\changed{PMF 8}-parameter model (solid, light blue line). 
+The achieved map 1/f knee frequency makes no difference to CMB-S4 PMF searches in the \changed{12}-parameter model (black lines). 
+  For $n_B=-2.9$, this transition occurs because the \changed{12}-parameter model introduces a degeneracy with r on the large angular scales impacted by the map 1/f knee. 
+  The 1/f knee frequency also makes no difference for the bluer PMF templates  (dashed and dash-dotted black lines) in either the restricted (light blue) or full \changed{12}-parameter (black) model space.
      Note that in the case of $n_B=2$, the forecasts have been multiplied by a factor of $10^5$ for plotting purposes. 
@@
 For the bluer PMF spectra ($n_B=-1$ or 2), the forecasts show no dependence on the knee frequency. 
-For the fiducial 11-parameter model, our ability to separate a PMF from other physics is coming from sub-degree angular scales. 
+For the fiducial \changed{12}-parameter model, our ability to separate a PMF from other physics is coming from sub-degree angular scales. 
 %An instrument built to precisely measure gravitational lensing of the CMB should do very well at searching for PMFs. 
@@
 We have also shown that the next generation of experiments should dramatically reduce these limits, with the potential to detect PMFs for the first time. 
-The so-called stage III experiments, which will begin taking data in 2017, can be expected to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a five-parameter extension to \lcdm{} and foregrounds.
+The so-called stage III experiments, which will begin taking data in 2017, can be expected to set upper limits at the level of $\apmf < 0.02$ even after marginalizing over a six-parameter extension to \lcdm{} and foregrounds.
 
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We have shown that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$, and less optimistic versions can still set upper limits on order of $\apmf < 0.006$ in a 11-parameter cosmological model with  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf.
+We have shown that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$, and less optimistic versions can still set upper limits on order of $\apmf < 0.006$ in a \changed{12}-parameter cosmological model with  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf{} \changed{+$\beta$}.
 This represents a three-fold improvement over the forecasts for the stage III experiments and a more than 100-fold improvement over the current limits for this cosmological model. 

### 2017-04-24 pmf.tex
i

@@
 We thank the \changed{referee as well as} Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
-C. Reichardt is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 
+CR is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 
 CF acknowledges support from NASA grants NASA NNX16AJ69G and NASA NNX16AF39G. 

### 2017-05-05 pmf.tex
updates to real data

@@
 \changed{The calculation of the PMF templates, \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
-The parameter $\beta$ relates the timing of neutrino decoupling and the generation of the PMF, and is defined by $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$, where $a_x$ represents the scale factor at the respective events.
-}
+The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events. }
 Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.
@@
 
-Given that we are still in the era of upper limits, we do not explore the full 3-dimensional PMF parameter space in this work. 
-Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG, $n_B = -2.9$ and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
-We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}. 
-We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
+Given that we are still in the era of upper limits, we \changed{fix the value of $n_B$ instead of exploring the full 3-dimensional PMF parameter space. 
+For the real data, we focus on nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.  
 Quantum mechanical zero-point fluctuations during inflation can generate an approximately scale-invariant PMF with a spectral index close to $n_B = -3$ \citep[e.g.,][]{turner88, mack01,2008PhRvD..78f3012K}.
@@
 In contrast, causal PMFs with bluer spectra require later phase transitions or other new physics after inflation \citep[e.g.,][]{durrer03, subramanian16}. 
-\removed{
-We have compared the calculated templates to the outputs of the earlier CMBACT-derived code\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}}
-\citep{pogosian99}.}
-
-\st{
-We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
-The origin of the difference is unclear.
-}
-\st{We have chosen to use the more recent} \citet{zucca16} \st{code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}
-\textcolor{red}{We use the code from} \citet{zucca16} \textcolor{red}{which allows us to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}
+We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}. 
+For each value of $n_B$, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}
 The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
@@
 Temperature data is not the main focus of this work, and  and we find our \planck{} results  to be consistent with \citet{planck15-19}, suggesting the impact of the scalar terms is minor. 
-The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}.
+The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb} \changed{and against each other in Fig.~\ref{fig:pmf-nb}. }
 
@@
 We test which datasets are important by adding single datasets to the \planck{} data, \changed{and find that the source of the improvement is evenly split between \sptpol{} and \bicepkeck{}. 
-Adding either one to \planck{} yields the same upper limit: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$ versus  $\apmf^{\planck+\sptpol}) < \upperAsptpol$. 
+Adding either one to \planck{} yields the same 95\% CL upper limit: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$ versus  $\apmf^{\planck+\sptpol}) < \upperAsptpol$. 
 Extending the $\beta$ prior to lower values would shift the relative weight more towards \sptpol{} (and vice-versa). 
+Similarly, increasing the value of $n_B$ would  increase the relative importance of the smaller angular scales measured by \sptpol.
+In short, the source of the factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is due to a more accurate measurement of the B-mode power spectrum at all scales.
 }
-%and \sptpol{} ($\apmf <  \upperAsptpol$) B-mode power spectrum measurements. 
-The other datasets do not have a large impact on the observed limits for a scale-invariant PMF, although they would for bluer PMFs. 
-In short, the factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is primarily due to a more accurate measurement of the B-mode power spectrum at large angular scales.
 
@@
 We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-this is somewhat better than the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-\changed{It is possible the difference is due to poor sampling of low values of \bpmf{} when importance sampling the chain. }
+\changed{similar to} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
 \st{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and} \citet{zucca16} \st{codes.}
 \st{Using the CMBACT-derived code that} \citet{planck15-19} \st{used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.}
-\changed{Adding the ground-based polarization measurements reduces the 95\% CL upper limit only slightly to $\bpmf < \upperBall$\,nG. }
-The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero. 
-These results are higher than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.
+\changed{Adding the ground-based polarization measurements reduces the 95\% CL upper limit significantly to $\bpmf < \upperBall$\,nG. }
+\st{The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero.
+}
+\changed{These results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}
 

### 2017-05-25 pmf.tex
minute changes

@@
 However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
-If we follow \citet{polarbear15} who used $\beta \in [0,39]$, the \planck-only upper limit is nearly eight times higher, and the combined dataset limit nearly two times higher. }
+If we follow \citet{polarbear15} who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset. }
 We sometimes also add \alens{} as a simple way of marginalizing over uncertainty in the predicted lensed BB power spectrum for any extension to the \lcdm{} model. 
@@
 \st{Using the CMBACT-derived code that} \citet{planck15-19} \st{used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.}
-\changed{Adding the ground-based polarization measurements reduces the 95\% CL upper limit significantly to $\bpmf < \upperBall$\,nG. }
+\changed{Adding the ground-based polarization measurements significantly reduces the 95\% CL upper limit to $\bpmf < \upperBall$\,nG. }
 \st{The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero.
 }
-\changed{These results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}
+\changed{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}
 

### 2017-05-30 response.tex
updated response

@@
 \usepackage[usenames, dvipsnames]{color}
+
+\newcommand{\sqdeg}{deg$^2$ }
+\newcommand{\omb}{\ensuremath{\Omega_b h^2}}
+\newcommand{\omc}{\ensuremath{\Omega_c h^2}}
+\newcommand{\clpp}{\ensuremath{C_{L}^{\phi\phi}}}
+\newcommand{\cpmf}{\ensuremath{C_{\ell}^{\rm PMF}}}
+
+\newcommand{\cpmftens}{\ensuremath{C_{\ell}^{\rm PMF,\,tens}}}
+\newcommand{\cpmfvec}{\ensuremath{C_{\ell}^{\rm PMF,\,vec}}}
+\newcommand{\apmf}{\ensuremath{A_{\rm PMF}}}
+\newcommand{\bpmf}{\ensuremath{B_{\rm 1\,Mpc}}}
+\newcommand{\alens}{\ensuremath{A_{\rm lens}}}
+\newcommand{\lcdm}{\ensuremath{\Lambda}CDM}
+\newcommand{\nrun}{\ensuremath{n_{\rm run}}}
+\newcommand{\neff}{\ensuremath{N_{\rm eff}}}
+\newcommand{\ho}{H\ensuremath{_0}}
+\newcommand{\mnu}{\ensuremath{\sum m_\nu}}
+\newcommand{\ukarcmin}{\ensuremath{\mu}{\rm K-arcmin}}
+\newcommand{\lknee}{\ensuremath{\ell_{\rm knee}}}
+\newcommand{\fermilat}{\textit{Fermi}-LAT}
+
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
+\newcommand{\planck}{{\sl Planck}}
+\newcommand{\wmap}{{\sl WMAP}}
+\newcommand{\bicepkeck}{BICEP2/Keck Array}
+\newcommand{\sptnew}{SPT-3G}
+\newcommand{\pb}{\textsc{Polarbear}}
+\newcommand{\simons}{Simons Array}
+\newcommand{\sptpol}{SPTpol}
+\newcommand{\advactpol}{Adv.~ACTpol}
+
+\newcommand{\tbd}[1]{\textcolor{Red}{{\bf TBD}: #1}}
+\newcommand{\gab}[1]{\textcolor{Orchid}{[{\bf GS}: #1]}}
+\newcommand{\changed}[1]{\textcolor{Red}{#1}}
+\newcommand{\removed}[1]{\textcolor{Red}{}}
 
@@
 
+\\
+\textcolor{red}{Changes by section - to dos}
+\\
+
+\changed{2.2 old}
+
+\be
+C_\ell = C_\ell^{\rm{CAMB}} + \apmf \cpmf
+\ee
+
+The calculation of the PMF template, \cpmf, is described in \S\ref{sec:template}.
+
+For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to PMFs.
+
+\changed{2.2 new}
+
+\be
+C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]
+\ee
+The calculation of the PMF templates, \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
+The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.
+
+For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \changed{2 parameters, \apmf{} and $\beta$, }describing the power due to PMFs.
+
+There are two points to note about the PMF priors. 
+First, this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
+In the current era of upper limits, this prior choice has some impact on the resulting PMF limits. 
+Second, the exact range of the uniform prior on $\beta$ matters. 
+Here we follow \citet{planck15-19} and \citet{zucca16} and use $\beta \in [11.513, 41.447]$.\footnote{This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$.}
+However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
+If we follow \citet{polarbear15} who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.
+
 \end{document}

### 2017-06-07 response.tex
response update

@@
 \newcommand{\changed}[1]{\textcolor{Red}{#1}}
-\newcommand{\removed}[1]{\textcolor{Red}{}}
+\newcommand{\removed}[1]{\st{#1}}
+\newcommand{\added}[1]{\textbf{#1}}
+\newcommand{\reviewer}[1]{\textcolor{Blue}{#1}}
+\newcommand{\diff}[1]{\textcolor{PineGreen}{#1}}
+\newcommand{\hide}[1]{\iffalse{#1}}
 
@@
 Dear Editor,
-\\
 
-We'd like to thank the reviewer for their time, carefully reading our paper and providing their valuable feedback.
+We'd like to thank the \reviewer{reviewer} for their time, carefully reading our paper and providing their valuable feedback.
 Below we address their feedback and list the changes we've made to the paper in response.
-\\
 
-\textcolor{blue}{The reviewer's feedback is shown in blue.}
+\reviewer{The reviewer's feedback is shown in blue.}
 
@@
 
-\textcolor{PineGreen}{The changed sections in our paper will then be included below in green \textbf{with additions presented in boldface} and removed sections presented with a strike through them.}
-\\
+\diff{The changed sections in our paper will then be included below in green \added{with additions presented in boldface} and removed sections presented with a strike through them.}
 
-\textcolor{blue}{The end of the 2nd paragraph says that this work constrains the possibility of PMFs "or parity-violating physics".
+\reviewer{The end of the 2nd paragraph says that this work constrains the possibility of PMFs "or parity-violating physics".
 As far as I can tell, the analysis uses only parity-even spectra, such as TT, TE, EE and BB.
@@
 
-\textcolor{PineGreen}{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (\citep{carroll98,lue99}) or primordial magnetic fields (PMFs) (\citep{kosowsky96, seshadri01}).
+\diff{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (\citep{carroll98,lue99}) or primordial magnetic fields (PMFs) (\citep{kosowsky96, seshadri01}).
 Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
  By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.  }
-\\
 
-\textcolor{blue}{The work assumes a fixed PMF template based on a model with a fixed value of the PMF generation time: $a_{\nu}/a_{PMF}$.
+\reviewer{The work assumes a fixed PMF template based on a model with a fixed value of the PMF generation time: $a_{\nu}/a_{PMF}$.
 This parameter is entirely arbitrary, and directly determines the amplitude of the tensor mode, which is responsible for the tight bound the authors get from BICEP2/Keck.
@@
 
-\textcolor{PineGreen}{
-\st{
+\diff{
+\removed{
 We have compared the calculated templates to the outputs of the earlier CMBACT-derived code.
@@
 The origin of the difference is unclear.
-We have chosen to use the more recent (Zucca16) code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}
-\textbf{We use the code from zucca16 which allows us to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}}
-\\
+We have chosen to use the more recent (Zucca16) code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}}
 
-\textcolor{PineGreen}{
-We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-this is somewhat better than the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done.}
-\textcolor{PineGreen}{
-\st{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16}}}
-\textcolor{PineGreen}{
-\textbf{The improvement comes from our choice of value for the PMF generation time versus the decision in \citet{planck15-19} to marginalise over PMF generation time altogether.}}
-\textcolor{PineGreen}{
-\st{Using the CMBACT-derived code that planck15-19 used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.
-Returning to} \textbf{Using} the \citet{zucca16} code and adding the ground-based polarization measurements, we find the upper limit is  reduced only slightly to $\bpmf < \upperBall$\,nG.}
-\\
+In addition, we added further discussion about the the significance of $a_{\nu}/a_{PMF}$ to section 2.2 (Method):
 
-\textcolor{blue}{The authors report a factor of 2 difference in the normalization of the tensor mode between the public code provided by Zucca et al and a "CMBACT-derived code", saying that "the origin of the difference is unclear".
+\diff{
+\be
+C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]
+\ee
+The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling} are described in \S\ref{sec:template}. 
+\added{The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.}}
+
+\reviewer{The authors report a factor of 2 difference in the normalization of the tensor mode between the public code provided by Zucca et al and a "CMBACT-derived code", saying that "the origin of the difference is unclear".
 The public version of CMBACT is a code for CMB anisotropies from cosmic strings and does not concern PMFs.
@@
 
-\textcolor{pinegreen}{}
+As above, we removed mentions of CMBACT code as well as its results, thus there is no mention of the factor of 2 difference in the normalization of the tensor mode.
+
+\diff{}
 \\
 
-\textcolor{blue}{In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same
+\reviewer{In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same
 parameters) between the CMBACT-derived and Zucca et al.
@@
 
-\textcolor{blue}{Instead, the "improvement" comes from the fact that the analysis by Planck collaboration (as well as Zucca et al) marginalized over the PMF generation time, which negated the contribution of the PMF tensor modes to the constraints.}
+\reviewer{Instead, the "improvement" comes from the fact that the analysis by Planck collaboration (as well as Zucca et al) marginalized over the PMF generation time, which negated the contribution of the PMF tensor modes to the constraints.}
 
-\textcolor{blue}{In summary, I think the paper contains some claims that need revisiting.
+\reviewer{In summary, I think the paper contains some claims that need revisiting.
 I suggest repeating the analysis with the PMF generation time set free and report the bounds in that case.
@@
 
-\\
-\textcolor{red}{Changes by section - to dos}
-\\
+\changed{Changes by section - to dos}
 
@@
 
-\be
-C_\ell = C_\ell^{\rm{CAMB}} + \apmf \cpmf
-\ee
+For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to PMFs.
 
-The calculation of the PMF template, \cpmf, is described in \S\ref{sec:template}.
-
-For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to PMFs.
+\removed{In particular, note that} this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature.
 
@@
 
-\be
-C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]
+For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \added{2 parameters, \apmf{} and $\beta$,}describing the power due to PMFs.
+
+\added{There are two points to note about the PMF priors. 
+First}, this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
+\added{In the current era of upper limits, this prior choice has some impact on the resulting PMF limits. 
+Second, the exact range of the uniform prior on $\beta$ matters. 
+Here we follow (planck15-19) and  (zucca16) and use $\beta \in [11.513, 41.447]$.\footnote{This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$.}
+However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
+If we follow (polarbear15) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset. }
+
+\changed{2.3 old}
+
+Finally, the timing of when PMFs are generated relative to neutrino decoupling matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
+The timing is \removed{typically parametrized by the ratio of the scale factors at neutrino decoupling and PMF generation, $a_{\nu}/a_{\rm{PMF}}$.}
+
+Given that we are still in the era of upper limits, \removed{we do not explore} the full 3-dimensional PMF parameter space \removed{in this work. 
+Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG, $n_B = -2.9$ and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
+We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}.}
+We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.
+
+The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}
+
+Note that the power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, which is not captured in the above expression.
+
+Note that the power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, \removed{which is not captured in the above expression.}
+
+\changed{2.3 new}
+
+Finally, the timing of when PMFs are generated relative to neutrino decoupling matters \added{for the tensor component} because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos.
+The timing is  parametrized by \added{$\beta = ln(a_{\nu}/a_{\rm{PMF}})$,  the natural logarithm of the ratio of the scale factors at neutrino decoupling and PMF generation.}
+
+Given that we are still in the era of upper limits, we \added{fix the value of $n_B$ instead of exploring} the full 3-dimensional PMF parameter space. 
+\added{For the real data}, we focus on nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.
+
+\added{We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}. 
+For each value of $n_B$, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}
+
+The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb} \added{and against each other in Fig.~\ref{fig:pmf-nb}. }
+
+The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
+\added{We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
+\be \label{eqn:betascaling}
+\apmf^{tens} \propto \beta^{1.9},
 \ee
-The calculation of the PMF templates, \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
-The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.
+to an excellent approximation. 
+We use this $\beta$ power law form to handle the PMF timing dependence. }
 
-For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \changed{2 parameters, \apmf{} and $\beta$, }describing the power due to PMFs.
+\changed{3.1 old}
 
-There are two points to note about the PMF priors. 
-First, this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
-In the current era of upper limits, this prior choice has some impact on the resulting PMF limits. 
-Second, the exact range of the uniform prior on $\beta$ matters. 
-Here we follow \citet{planck15-19} and \citet{zucca16} and use $\beta \in [11.513, 41.447]$.\footnote{This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$.}
-However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
-If we follow \citet{polarbear15} who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.
+The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \planck{} alone in the simple \removed{7}-parameter model. 
+The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}.
+
+Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power).
+
+Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
+We therefore importance sample the chains to apply a flat prior on \bpmf. 
+We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
+\removed{this is somewhat better than} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
+\removed{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16} codes. 
+Using the CMBACT-derived code that \citet{planck15-19} used, we find a consistent upper limit of $\bpmf < 1.9$\,nG. 
+Returning to the  \citet{zucca16} code and adding} the ground-based polarization measurements\removed{, we find} the upper limit \removed{is  reduced only slightly} to $\bpmf < \upperBall$\,nG. 
+\removed{The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero.
+}
+\removed{These} results are \removed{higher} than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}\removed{; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.}
+
+\changed{3.1 new}
+
+The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \planck{} alone in the simple \added{8}-parameter model. 
+The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\added{PMF}.
+
+We test which datasets are important by adding single datasets to the \planck{} data, \added{and find that the source of the improvement is evenly split between \sptpol{} and \bicepkeck{}.
+Adding either one to \planck{} yields the same 95\% CL upper limit: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$ versus  $\apmf^{\planck+\sptpol}) < \upperAsptpol$. 
+Extending the $\beta$ prior to lower values would shift the relative weight more towards \sptpol{} (and vice-versa). 
+Similarly, increasing the value of $n_B$ would  increase the relative importance of the smaller angular scales measured by \sptpol.}
+In short, the \added{source of the} factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is due to a more accurate measurement of the B-mode power spectrum at all scales.
+
+Somewhat counterintuitively, the limits are somewhat better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power).
+
+The 95\% CL upper limit on \apmf{} drops \removed{slightly} again.
+
+Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
+We therefore importance sample the chains to apply a flat prior on \bpmf. 
+We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
+\added{similar to} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
+\added{Adding the ground-based polarization measurements significantly reduces the 95\% CL upper limit to $\bpmf < \upperBall$\,nG. }
+\added{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}
+
+\changed{4.1 old}
+
+We consider the constraints on PMFs in two cosmologies. 
+Our fiducial cosmology is a \removed{11}-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf. 
+Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species.
+
+This \removed{11-parameter} model is our default cosmological model when forecasting future PMF constraints as these extensions are all well-motivated theoretically. 
+We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case and is with the tensor-to-scalar ratio, $r$.
+
+To test the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' \removed{7-parameter} model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf.
+
+\changed{4.1 new}
+
+We consider the constraints on PMFs in two cosmologies. 
+\added{Our fiducial cosmology is a \added{12}-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf{} \changed{ + $\beta$}.}
+Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species.
+
+This \added{12}-parameter model is our default cosmological model when forecasting future PMF constraints as these extensions are all well-motivated theoretically. 
+We have examined the degree to which \apmf{} is degenerate with the 10 parameters \added{unrelated to PMFs} -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case and is with the tensor-to-scalar ratio, $r$.
+
+To test the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' \added{8}-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf{} \added{ + $\beta$}.
+
+\changed{4.2 old}
+
+Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the \st{7}-parameter model to $\sigma(\apmf)=0.015$. 
+The relative improvement is larger in the more realistic st{11}-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
+Thus within the st{11}-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
+The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
+$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other st{11}-parameters.
+
+\changed{4.2 new}
+
+Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the \added{8}-parameter model to $\sigma(\apmf)=0.015$. 
+The relative improvement is larger in the more realistic \added{12}-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
+Thus within the \added{12}-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
+The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
+$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the \added{other} parameters.
+
+For the \added{12}-parameter model and $n_B=-1$, adding SPT-3G and Simons Array to \planck{} leads to a 17-fold reduction in $\sigma(\apmf)$ from \fisherAlooseNbOneplk{} to \fisherAlooseNbOneSThree{}.
+
+\changed{4.3 old}
+
+\changed{4.3 new}
+
+For this fiducial configuration and the \added{12}-parameter cosmological model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes.
+
+\changed{4.4 old}
+
+\changed{4.4 new}
+
+Figure~\ref{fig:sensitivity} shows the uncertainty on \apmf{} as a function of the map noise level for the three PMF templates in either the \added{12} or \added{8}-parameter cosmological models.
+
+In the general, \added{12}-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered until the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
+
+  The black lines are for the fiducial \added{12}-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
+  The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the \added{12}-parameter model due a degeneracy with the tensor-to-scalar ratio.
+
+\changed{4.5 old}
+\changed{4.5 new}
+
+  The black lines are for the fiducial \added{12}-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model.
+
+\changed{4.6 old}
+\changed{4.6 new}
+   There is essentially no difference to the preferred areas between the \added{12}-parameter cosmological model (black) or the restricted \lcdm{}+\added{PMF 8}-parameter model (light blue).
+
+\changed{4.7 old}
+\changed{4.7 new}
+11 -> 12
+7 -> 8 parameter
 

### 2017-06-09 response.tex
response update

@@
 
+In response, we have repeated the analysis, adding $\beta = ln(a_{\nu}/a_{PMF})$ as a free-parameter.
+
+We include a discussion on the significance of $\beta$ in section 2.2 as follows:
+
+\diff{
+\be
+C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]
+\ee
+The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling} are described in \S\ref{sec:template}. 
+\added{The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.} Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.}
+
+\diff{For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \added{2 parameters, \apmf{} and $\beta$,}describing the power due to PMFs.
+We adopt flat priors on all parameters. 
+\added{There are two points to note about the PMF priors. 
+First}, this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
+\added{In the current era of upper limits, this prior choice has some impact on the resulting PMF limits. 
+Second, the exact range of the uniform prior on $\beta$ matters. 
+Here we follow (planck15-19) and  (zucca16) and use $\beta \in [11.513, 41.447]$.\footnote{This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$.}
+However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
+If we follow (polarbear15) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.}}
+
+Section 2.3:
+
+\diff{Finally, the timing of when PMFs are generated relative to neutrino decoupling matters \added{for the tensor component} because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos.
+The timing is \removed{typically parametrized by the ratio of the scale factors at neutrino decoupling and PMF generation, $a_{\nu}/a_{\rm{PMF}}$.} parametrized by \added{$\beta = ln(a_{\nu}/a_{\rm{PMF}})$,  the natural logarithm of the ratio of the scale factors at neutrino decoupling and PMF generation.}}
+
+Further note that since we have added $/beta$ to the analysis, our fisher models have increased from 6 and 11 parameter models to 7 and 12 parameter models.
+(Due to the prevalence of this change we have not listed its occurances here).
+
+\reviewer{The authors report a factor of 2 difference in the normalization of the tensor mode between the public code provided by Zucca et al and a "CMBACT-derived code", saying that "the origin of the difference is unclear".
+The public version of CMBACT is a code for CMB anisotropies from cosmic strings and does not concern PMFs.
+Any code that the authors might have used would be a private modification.
+Either the authors should clarify what code they are referring to, or avoid mentioning it.}
+
 As per the advice of the reviewer we have removed any mention of the CMBACT code.
@@
 We have chosen to use the more recent (Zucca16) code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}}
-
-In addition, we added further discussion about the the significance of $a_{\nu}/a_{PMF}$ to section 2.2 (Method):
-
-\diff{
-\be
-C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]
-\ee
-The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling} are described in \S\ref{sec:template}. 
-\added{The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.}}
-
-\reviewer{The authors report a factor of 2 difference in the normalization of the tensor mode between the public code provided by Zucca et al and a "CMBACT-derived code", saying that "the origin of the difference is unclear".
-The public version of CMBACT is a code for CMB anisotropies from cosmic strings and does not concern PMFs.
-Any code that the authors might have used would be a private modification.
-Either the authors should clarify what code they are referring to, or avoid mentioning it.}
-
-As above, we removed mentions of CMBACT code as well as its results, thus there is no mention of the factor of 2 difference in the normalization of the tensor mode.
 
@@
 \changed{Changes by section - to dos}
-
-\changed{2.2 old}
-
-For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and a seventh parameter \apmf{} describing the power due to PMFs.
-
-\removed{In particular, note that} this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature.
-
-\changed{2.2 new}
-
-For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \added{2 parameters, \apmf{} and $\beta$,}describing the power due to PMFs.
-
-\added{There are two points to note about the PMF priors. 
-First}, this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
-\added{In the current era of upper limits, this prior choice has some impact on the resulting PMF limits. 
-Second, the exact range of the uniform prior on $\beta$ matters. 
-Here we follow (planck15-19) and  (zucca16) and use $\beta \in [11.513, 41.447]$.\footnote{This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$.}
-However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
-If we follow (polarbear15) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset. }
 

### 2017-06-09 pmf.tex
updated numbers and plots

@@
 In the minimal cosmological model, the 1-$\sigma$ forecast for \planck{}+\ho{} is $\sigma(\apmf)=\fisherAplk$ for a best-motivated, nearly-scale invariant PMF spectrum (i.e.~$n_B=-2.9$). 
-This is on-par with, although 30\% better than, the actual upper limit from the \planck{} data.  
-Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the \changed{8}-parameter model to $\sigma(\apmf)=0.015$. 
+\changed{We have set a Gaussian prior on $\beta$ with $\sigma_\beta$ chosen such that the Fisher forecast matches the actual upper limit from the \planck{} data.  }
+Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by \changed{more than} an order of magnitude in the \changed{8}-parameter model to $\sigma(\apmf)=\fisherASThree$.
 The relative improvement is larger in the more realistic \changed{12}-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
-Thus within the \changed{12}-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
+Thus within the \changed{12}-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=\fisherAlooseSThree$. 
 The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
@@
 However, larger telescopes are also more expensive to build which means for a fixed experimental budget, they would necessitate less ambitious focal planes and lower instantaneous mapping speeds. 
-We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin{} for a FWHM of 4$^\prime$; a noise level of 2.9 \ukarcmin{} for a FWHM of 2$^\prime$; and a noise level of 4.1 \ukarcmin{} for a FWHM of 1$^\prime$.
+We very crudely approximated a cost-neutral setup with a noise level of 1.3 \ukarcmin{} for a FWHM of 4$^\prime$; a noise level of 2.8 \ukarcmin{} for a FWHM of 2$^\prime$; and a noise level of 4.0 \ukarcmin{} for a FWHM of 1$^\prime$.
 We find that 
-improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.2 or 1.1 for $n_B = -2.9, -1, +2$ respectively.
+improving the mapping speed rather than telescope size leads to somewhat better potential limits for these experimental configurations, by a factor of 1.6, 1.1 or 1.1 for $n_B = -2.9, -1, +2$ respectively.
 However the results are close enough that the crudeness of the cost-neutral estimates used here is a worry, and the preference might flip for more accurately costed setups. 
@@
 With that said, the PMF constraints improve by a factor of 1.4-1.5 (depending on the cosmological model) going from 10\% to 25\% of the full sky, and are nearly flat (a 6\% improvement) from 25\% to 70\% of the sky (the widest area likely to be possible after galactic cuts).
-Conversely for $n_B=-1$ or +2, the optimal survey area is smaller at 10\% of the full sky. 
+Conversely for $n_B=-1$ or +2, the optimal survey area is \changed{around 15}\% of the full sky. 
 Note however that the minimum is extremely broad with only a 10\% worsening of the expected uncertainty as the survey area is increased from 10\% to 70\% of the  full sky. 
-A survey of around 25\% of the sky would perform well for all three considered PMF models.
+A survey \changed{ covering at least} 25\% of the sky would perform well for all three considered PMF models.
 
@@
 We generally find the forecasts to be insensitive to the 1/f knee or galactic foreground removal at the default beam size of 4$^\prime$. 
-It appears that even in the nearly scale-invariant case, the PMF constraint is coming primarily from smaller angular scales due to the the degeneracy with the tensor-to-scalar ratio at large angular scales.
-Without this degeneracy, i.e. in the simple \lcdm{}+\apmf{} model, dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 3.2 for a nearly scale-invariant PMF. 
+It appears that even in the nearly scale-invariant case, the PMF constraint is coming primarily from smaller angular scales due to the degeneracy \changed{at large angular scales with both the tensor-to-scalar ratio and the PMF timing parameter $\beta$}.
+\st{Without this degeneracy, i.e. in the simple \lcdm{}+\apmf{} model, dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 3.2 for a nearly scale-invariant PMF. 
 In this case, the degradation accelerates once the 1/f knee rises to $\lknee{} \gtrsim 70$. 
-This is consistent with the earlier statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. 
+This is consistent with the earlier statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. }
 For the bluer PMF spectra ($n_B=-1$ or 2), the forecasts show no dependence on the knee frequency. 
@@
 By adding \bicepkeck{}, \pb, and \sptpol{} to \planck{} we have found that the 95\% CL upper limit on the PMF power falls nearly two-fold from $\apmf < \upperAplk$ to $\apmf < \upperAall$. 
-The biggest contributor to this improvement is the low-$\ell$ B-mode data from \bicepkeck{}.
+\changed{The two major contributors to this improvement are the low-$\ell$ B-mode data from \bicepkeck{} and the high-$\ell$ B-mode data from \sptpol. }
 
@@
 The potential for detection increases even further with planned experiments like the Simons Observatory or CMB-S4. 
-We have shown that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$, and less optimistic versions can still set upper limits on order of $\apmf < 0.006$ in a \changed{12}-parameter cosmological model with  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf{} \changed{+$\beta$}.
+We have shown that an ideal version of CMB-S4 might decrease the 95\% CL upper limits eight-fold, to $\apmf < 0.0025$, and \changed{more realistic} versions can still set upper limits on order of $\apmf < 0.006$ in a \changed{12}-parameter cosmological model with  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf{} \changed{+$\beta$}.
 This represents a three-fold improvement over the forecasts for the stage III experiments and a more than 100-fold improvement over the current limits for this cosmological model. 

### 2017-06-13 pmf.tex
chang's comment

@@
 \changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
-We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
+We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as $\beta^{1.9}$ to an excellent approximation. 
+We use this $\beta$ power law form to handle the PMF timing dependence. 
+Thus the tensor PMF power will scale as:
 \be \label{eqn:betascaling}
-\apmf^{tens} \propto \beta^{1.9},
+\apmf^{tens} \propto  \bpmf^4 \beta^{1.9},
 \ee
-to an excellent approximation. 
-We use this $\beta$ power law form to handle the PMF timing dependence. }
+}
 

### 2017-06-13 pmf.tex
edited the tex around eq (3)

--- 2017-06-09 pmf.tex
@@
 \be
-\changed{C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]}
+\changed{C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]}\label{clmodel}
 \ee
@@
 \be \label{eqn:scaling}
-\apmf \propto \bpmf^4.
+C_{\ell}^{\rm{vec}} \propto \bpmf^4.
 \ee
@@
 
-\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
-We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
+\changed{The power in the tensor mode depends on the timing of PMF generation relative to neutrino decoupling. 
+%We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as $\beta^{1.9}$ to an excellent %approximation. 
+We use the code developed by \citet{zucca16} to compute the tensor power spectra with a fixed magnetic field strength but different $\beta$ values.
+Given the fact that the amplitude of the tensor mode reaches the maximum around $\ell$ = 100, we assume a simple power law and extrapolate the scaling relation between the power and the parameter $\beta$ from an ensemble of amplitudes at $\ell$ =100.
+Similar to the vector mode, the tensor power depends on the amplitude of the magnetic field as well.
+%We use this $\beta$ power law form to handle the PMF timing dependence. 
+Thus the tensor PMF power scales as:
 \be \label{eqn:betascaling}
-\apmf^{tens} \propto \beta^{1.9},
+C_{\ell}^{\rm{tens}} \propto  \bpmf^4 \beta^{1.9},
 \ee
-to an excellent approximation. 
-We use this $\beta$ power law form to handle the PMF timing dependence. }
+which corresponds to the last term in Eq. (\ref{clmodel}).
+}
 

### 2017-06-13 response.tex
updated response

@@
 \usepackage[usenames, dvipsnames]{color}
+
+\usepackage[table,usenames,dvipsnames]{xcolor}
+%\usepackage{amsmath}
+%\usepackage{subfigure}
+\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
+\usepackage{natbib}
+%\usepackage{natbib}
+\bibliographystyle{fapj}
+%\usepackage{graphicx}
+%\usepackage{multirow}
+\usepackage{soul}
 
@@
 
+\include{number_list}
+
 \begin{document}
@@
 Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
- By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.  }
+By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.}
 
@@
 \ee
-The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling} are described in \S\ref{sec:template}. 
+The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmftens{}, and the motivation for the $\beta$ scaling} are described in \S\ref{sec:template}. 
 \added{The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.} Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.}
@@
 
-Section 2.3:
+And section 2.3:
 
 \diff{Finally, the timing of when PMFs are generated relative to neutrino decoupling matters \added{for the tensor component} because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos.
-The timing is \removed{typically parametrized by the ratio of the scale factors at neutrino decoupling and PMF generation, $a_{\nu}/a_{\rm{PMF}}$.} parametrized by \added{$\beta = ln(a_{\nu}/a_{\rm{PMF}})$,  the natural logarithm of the ratio of the scale factors at neutrino decoupling and PMF generation.}}
+The timing is parametrized by \added{$\beta = ln(a_{\nu}/a_{\rm{PMF}})$, the natural logarithm of the ratio of the scale factors at neutrino decoupling and PMF generation.}}
 
-Further note that since we have added $/beta$ to the analysis, our fisher models have increased from 6 and 11 parameter models to 7 and 12 parameter models.
+In addition we have added $\beta$ to our analysis:
+
+\diff{Given that we are still in the era of upper limits, we \added{fix the value of $n_B$ instead of exploring} the full 3-dimensional PMF parameter space. 
+\added{For the real data}, we focus on nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.}
+
+\diff{\added{We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}. 
+For each value of $n_B$, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}}
+
+\diff{The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb} \added{and against each other in Fig.~\ref{fig:pmf-nb}. }}
+
+\diff{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
+\added{We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
+\be \label{eqn:betascaling}
+\apmf^{tens} \propto \beta^{1.9},
+\ee
+to an excellent approximation. 
+We use this $\beta$ power law form to handle the PMF timing dependence.}}
+
+Further note that since we have added $\beta$ to the analysis, our fisher models have increased from 6 and 11 parameter models to 7 and 12 parameter models.
 (Due to the prevalence of this change we have not listed its occurances here).
@@
 As per the advice of the reviewer we have removed any mention of the CMBACT code.
-
-\diff{
-\removed{
-We have compared the calculated templates to the outputs of the earlier CMBACT-derived code.
-We find excellent agreement  for the vector modes as would be hoped, however a roughly factor of two difference on the tensor mode power. 
-The origin of the difference is unclear.
-We have chosen to use the more recent (Zucca16) code instead of the CMBACT-derived code, largely due to our desire to extend the calculation out to $\ell=10000$ for the Fisher matrix forecasts.}}
 
@@
 
+After setting PMF generation time as a free parameter we find:
+
+\diff{}
+
 \changed{Changes by section - to dos}
-
-\changed{2.3 old}
-
-Finally, the timing of when PMFs are generated relative to neutrino decoupling matters because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos. 
-The timing is \removed{typically parametrized by the ratio of the scale factors at neutrino decoupling and PMF generation, $a_{\nu}/a_{\rm{PMF}}$.}
-
-Given that we are still in the era of upper limits, \removed{we do not explore} the full 3-dimensional PMF parameter space \removed{in this work. 
-Instead, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG, $n_B = -2.9$ and $a_{\nu}/a_{\rm{PMF}} = 10^9$.
-We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}.}
-We focus on the nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.
-
-The PMF template is plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb}
-
-Note that the power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, which is not captured in the above expression.
-
-Note that the power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, \removed{which is not captured in the above expression.}
-
-\changed{2.3 new}
-
-Finally, the timing of when PMFs are generated relative to neutrino decoupling matters \added{for the tensor component} because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos.
-The timing is  parametrized by \added{$\beta = ln(a_{\nu}/a_{\rm{PMF}})$,  the natural logarithm of the ratio of the scale factors at neutrino decoupling and PMF generation.}
-
-Given that we are still in the era of upper limits, we \added{fix the value of $n_B$ instead of exploring} the full 3-dimensional PMF parameter space. 
-\added{For the real data}, we focus on nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.
-
-\added{We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}. 
-For each value of $n_B$, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}
-
-The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb} \added{and against each other in Fig.~\ref{fig:pmf-nb}. }
-
-The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
-\added{We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
-\be \label{eqn:betascaling}
-\apmf^{tens} \propto \beta^{1.9},
-\ee
-to an excellent approximation. 
-We use this $\beta$ power law form to handle the PMF timing dependence. }
 
@@
 
-Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
+Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent "detection" of \bpmf. 
 We therefore importance sample the chains to apply a flat prior on \bpmf. 
@@
 \removed{this is somewhat better than} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-\removed{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \citet{zucca16} codes. 
-Using the CMBACT-derived code that \citet{planck15-19} used, we find a consistent upper limit of $\bpmf < 1.9$\,nG. 
-Returning to the  \citet{zucca16} code and adding} the ground-based polarization measurements\removed{, we find} the upper limit \removed{is  reduced only slightly} to $\bpmf < \upperBall$\,nG. 
+\removed{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \mbox{\citet{zucca16}} codes.
+Using the CMBACT-derived code that \mbox{\citet{planck15-19}} used, we find a consistent upper limit of $\bpmf < 1.9$\,nG. 
+Returning to the \mbox{\citet{zucca16}} code and} adding the ground-based polarization measurements\removed{, we find} the upper limit \removed{is  reduced only slightly} to $\bpmf < \upperBall$\,nG. 
 \removed{The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero.
 }
-\removed{These} results are \removed{higher} than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}\removed{; we were unable to reproduce their listed upper limit for \planck{} + \sptpol{}.}
+\removed{These} results are \removed{higher} than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}
 
@@
 
-The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \planck{} alone in the simple \added{8}-parameter model. 
+The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \plan+{} alone in the simple \added{8}-parameter model. 
 The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\added{PMF}.
@@
 
-The 95\% CL upper limit on \apmf{} drops \removed{slightly} again.
+The 95\% CL upper limit on \apmf{} drops again.
 

### 2017-06-13 response.tex
updated response.tex made reviewer copy of pmf.tex, now known as pmfchanges.tex removed strikeout text and the coloring from changed sections of pmf.tex

@@
 \usepackage{soul}
-
+\setlength{\parindent}{0pt}
 \newcommand{\sqdeg}{deg$^2$ }
@@
 
-Dear Editor,
+Dear Editor,\\
 
-We'd like to thank the \reviewer{reviewer} for their time, carefully reading our paper and providing their valuable feedback.
-Below we address their feedback and list the changes we've made to the paper in response.
+We'd like to thank the reviewer for their time, carefully reading our paper and providing their valuable feedback.
+Below we address their feedback and list the changes we've made to the paper in response.\\
 
-\reviewer{The reviewer's feedback is shown in blue.}
+\reviewer{The reviewer's feedback is shown in blue.}\\
 
-Our response to the feedback will be included in black.
+Our response to the feedback will be included in black.\\
 
-\diff{The changed sections in our paper will then be included below in green \added{with additions presented in boldface} and removed sections presented with a strike through them.}
+\diff{The changed sections in our paper will then be included below in green \added{with additions presented in boldface} and removed sections presented with a strike through them.}\\
 
@@
 Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
-By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.}
+By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.}\\
 
@@
 However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
-If we follow (polarbear15) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.}}
+If we follow (polarbear15) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.}}\\
 
@@
 Further note that since we have added $\beta$ to the analysis, our fisher models have increased from 6 and 11 parameter models to 7 and 12 parameter models.
-(Due to the prevalence of this change we have not listed its occurances here).
+(Due to the prevalence of this change we have not listed its occurances here).\\
 
@@
 
-\diff{}
-\\
-
-\reviewer{In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same
-parameters) between the CMBACT-derived and Zucca et al.
+\reviewer{In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and Zucca et al.
 (2016) codes".
-The also claim that Planck used "the CMBACT-derived" code.
+They also claim that Planck used "the CMBACT-derived" code.
 This is a false claim.
@@
 
-After setting PMF generation time as a free parameter we find:
+We have indeed mistakenly attributed CMBACT to Planck. After setting PMF generation time as a free parameter we find:
 
-\diff{}
+\diff{The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \plan+{} alone in the simple \added{8}-parameter model. 
+The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\added{PMF}. }
 
-\changed{Changes by section - to dos}
+\diff{We test which datasets are important by adding single datasets to the \planck{} data, \added{and find that the source of the improvement is evenly split between \sptpol{} and \bicepkeck{}.
+	Adding either one to \planck{} yields the same 95\% CL upper limit: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$ versus  $\apmf^{\planck+\sptpol}) < \upperAsptpol$. 
+	Extending the $\beta$ prior to lower values would shift the relative weight more towards \sptpol{} (and vice-versa). 
+	Similarly, increasing the value of $n_B$ would  increase the relative importance of the smaller angular scales measured by \sptpol.}
+In short, the \added{source of the} factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is due to a more accurate measurement of the B-mode power spectrum at all scales.}
 
-\changed{3.1 old}
+\diff{Somewhat counterintuitively, the limits are somewhat better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power). }
 
-The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \planck{} alone in the simple \removed{7}-parameter model. 
-The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\apmf{}.
+\diff{The 95\% CL upper limit on \apmf{} drops again.}
 
-Somewhat counterintuitively, the limits are slightly better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power).
-
-Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent "detection" of \bpmf. 
+\diff{Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
 We therefore importance sample the chains to apply a flat prior on \bpmf. 
 We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-\removed{this is somewhat better than} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-\removed{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and \mbox{\citet{zucca16}} codes.
-Using the CMBACT-derived code that \mbox{\citet{planck15-19}} used, we find a consistent upper limit of $\bpmf < 1.9$\,nG. 
-Returning to the \mbox{\citet{zucca16}} code and} adding the ground-based polarization measurements\removed{, we find} the upper limit \removed{is  reduced only slightly} to $\bpmf < \upperBall$\,nG. 
-\removed{The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero.
-}
-\removed{These} results are \removed{higher} than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}
+\added{similar to} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
+\added{Adding the ground-based polarization measurements significantly reduces the 95\% CL upper limit to $\bpmf < \upperBall$\,nG. }
+\added{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}}
 
+\iffalse
 \changed{3.1 new}
@@
 7 -> 8 parameter
+\fi
 

### 2017-06-14 response.tex
cleaned citations on response.tex

@@
 
-\diff{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (\citep{carroll98,lue99}) or primordial magnetic fields (PMFs) (\citep{kosowsky96, seshadri01}).
+\diff{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (Carroll 1998; Lue et al.
+1999) or primordial magnetic fields (PMFs) (Kosowsky & Loeb
+1996; Seshadri & Subramanian 2001).  
 Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
@@
 \ee
-The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmftens{}, and the motivation for the $\beta$ scaling} are described in \S\ref{sec:template}. 
+The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmftens{}, and the motivation for the $\beta$ scaling} are described in \S 2.3. 
 \added{The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.} Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.}
 
-\diff{For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \added{2 parameters, \apmf{} and $\beta$,}describing the power due to PMFs.
+\diff{For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \added{2 parameters, \apmf{} and $\beta$, }describing the power due to PMFs.
 We adopt flat priors on all parameters. 
@@
 Second, the exact range of the uniform prior on $\beta$ matters. 
-Here we follow (planck15-19) and  (zucca16) and use $\beta \in [11.513, 41.447]$.\footnote{This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$.}
+Here we follow Planck Collaboration et al. (2016) and Zucca et al. (2016) and use $\beta \in [11.513, 41.447]$. (This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$).
 However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
-If we follow (polarbear15) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.}}\\
+If we follow Ade et al. (2015) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.}}\\
 
@@
 
-\diff{\added{We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S\ref{sec:forecasts}. 
-For each value of $n_B$, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}}
+\diff{\added{We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S 4 
+For each value of $n_B$, we use publicly released modifications to CAMB from Zucca et al.
+(2016) to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}}
 
-\diff{The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb} \added{and against each other in Fig.~\ref{fig:pmf-nb}. }}
+\diff{The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig. 2 \added{and against each other in Fig. 3. }}
 
 \diff{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
-\added{We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
+\added{We evaluate the tensor power predicted by the Zucca et al. (2016) code while stepping $\beta$ by two from 2 to 20, and find it scales as:
 \be \label{eqn:betascaling}
@@
 
-As per the advice of the reviewer we have removed any mention of the CMBACT code.
+As per the advice of the reviewer we have removed any mention of the CMBACT code.\\
 
@@
 We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-\added{similar to} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
+\added{similar to} the limit found by Planck Collaboration et al. (2016) of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
 \added{Adding the ground-based polarization measurements significantly reduces the 95\% CL upper limit to $\bpmf < \upperBall$\,nG. }
-\added{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}}
+\added{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by Zucca et al. (2016).}}
 

### 2017-06-14 response.tex
response

@@
 
-We'd like to thank the reviewer for their time, carefully reading our paper and providing their valuable feedback.
-Below we address their feedback and list the changes we've made to the paper in response.\\
+We thank the reviewer for their  careful read of our paper, and their comments and suggestions. Below we address their feedback and list the changes we've made to the paper in response.\\
 
@@
 Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
-By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.}\\
+By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.\\
 

### 2017-06-14 response.tex
reponse.tex

--- 2017-06-14 response.tex
@@
 
-\diff{The changed sections in our paper will then be included below in green \added{with additions presented in boldface} and removed sections presented with a strike through them.}\\
+\diff{The changed sections in our paper will then be included below in green \added{with additions presented in boldface}}\\
 

### 2017-06-14 response.tex
submit

@@
 
-\reviewer{The reviewer's feedback is shown in blue.}\\
+The reviewer's comments are shown in \reviewer{blue,} our response is in black, and the revised text in the paper is in \diff{green}. \\
 
-Our response to the feedback will be included in black.\\
+\section{Major comments}
 
-\diff{The changed sections in our paper will then be included below in green \added{with additions presented in boldface}}\\
-
-\reviewer{The end of the 2nd paragraph says that this work constrains the possibility of PMFs "or parity-violating physics".
-As far as I can tell, the analysis uses only parity-even spectra, such as TT, TE, EE and BB.
-The authors should either clarify what they mean or remove the claim.}
-
-In addition to producing a non-zero EB and TB power spectrum, PMFs and other parity-violating physics are also known to convert EE power into BB power.
-By looking for excess power in the BB power spectrum we can find the strength of PMFs or equate the effects of parity-violating physics to an equivalent PMF field strength.
-
-\diff{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (Carroll 1998; Lue et al.
-1999) or primordial magnetic fields (PMFs) (Kosowsky & Loeb
-1996; Seshadri & Subramanian 2001).  
-Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
-By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.}\\
-
-\reviewer{The work assumes a fixed PMF template based on a model with a fixed value of the PMF generation time: $a_{\nu}/a_{PMF}$.
+\subsection{$\beta$ should be marginalized over}
+\begin{itemize}
+\item \reviewer{The work assumes a fixed PMF template based on a model with a fixed value of the PMF generation time: $a_{\nu}/a_{PMF}$.
 This parameter is entirely arbitrary, and directly determines the amplitude of the tensor mode, which is responsible for the tight bound the authors get from BICEP2/Keck.
@@
 
-In response, we have repeated the analysis, adding $\beta = ln(a_{\nu}/a_{PMF})$ as a free-parameter.
+\item \reviewer{In summary, I think the paper contains some claims that need revisiting.
+I suggest repeating the analysis with the PMF generation time set free and report the bounds in that case.
+Only then they can be seriously compared to previous results in the literature.}
+\end{itemize}
 
-We include a discussion on the significance of $\beta$ in section 2.2 as follows:
+We agree with the referee that freeing the PMF generation time would strengthen the results, and have implemented this in both the fits to the real data and the Fisher matrix forecasts.
+All the numbers and plots have been updated with results that are marginalized over $\beta$.
+This significantly changes the results for the real data, making SPTpol more competitive with BICEP2/Keck as the referee expected. 
+The impact on the Fisher forecasts however is fairly minor.\\
 
-\diff{
-\be
-C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]
-\ee
-The calculation of the PMF templates,\added{ \cpmfvec{} and \cpmftens{}, and the motivation for the $\beta$ scaling} are described in \S 2.3. 
-\added{The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events.} Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.}
+We have updated the text in light of this change.
+There are significant additions to Sec 2.2 (Methods) and 2.3 (PMF template) to describe what happens when $\beta$ is varied.
+The text of Sec 3 has also been updated to reflect the new upper limits (with $\beta$ marginalized over), and the lesser relative importance of BICEP2/Keck.\\
 
-\diff{For the real data, unless noted, we assume the six-parameter, spatially-flat \lcdm{} model with a single massive neutrino of 60\,meV and \added{2 parameters, \apmf{} and $\beta$, }describing the power due to PMFs.
-We adopt flat priors on all parameters. 
-\added{There are two points to note about the PMF priors. 
-First}, this is a flat prior on the observed PMF power, $\apmf$, not the rms magnetic field strength, \bpmf, that has often been used in the literature. 
-\added{In the current era of upper limits, this prior choice has some impact on the resulting PMF limits. 
-Second, the exact range of the uniform prior on $\beta$ matters. 
-Here we follow Planck Collaboration et al. (2016) and Zucca et al. (2016) and use $\beta \in [11.513, 41.447]$. (This corresponds to $log_{10} (a_{\nu}/a_{\rm{PMF}}) \in[4,17]$).
-However, the constraints, especially those from \planck{} alone, weaken substantially if the lower bound on $\beta$ is lowered further. 
-If we follow Ade et al. (2015) who used $\beta \in [0,39]$, the upper limits are relaxed by a factor of roughly eight for \planck-only and by a factor of two for the combined dataset.}}\\
+Additionally, there is a small change in the first paragraph of 4.2 to describe how the prior placed on $\beta$ in the Fisher analysis.
+There are also a number of places that had referred to 6 and 11 parameter models that now refer to 7 and 12 parameter models.
+\\\\
 
-And section 2.3:
-
-\diff{Finally, the timing of when PMFs are generated relative to neutrino decoupling matters \added{for the tensor component} because the PMF-induced stress anisotropy can be compensated by decoupled or partially-decoupled neutrinos.
-The timing is parametrized by \added{$\beta = ln(a_{\nu}/a_{\rm{PMF}})$, the natural logarithm of the ratio of the scale factors at neutrino decoupling and PMF generation.}}
-
-In addition we have added $\beta$ to our analysis:
-
-\diff{Given that we are still in the era of upper limits, we \added{fix the value of $n_B$ instead of exploring} the full 3-dimensional PMF parameter space. 
-\added{For the real data}, we focus on nearly-scale-invariant ($n_B = -2.9$) PMF template in this work due to its connection to inflation.}
-
-\diff{\added{We also consider $n_B\,=\,-1$ and $n_B\,=\,2$ for the forecasts in \S 4 
-For each value of $n_B$, we use publicly released modifications to CAMB from Zucca et al.
-(2016) to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}}
-
-\diff{The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig. 2 \added{and against each other in Fig. 3. }}
-
-\diff{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
-\added{We evaluate the tensor power predicted by the Zucca et al. (2016) code while stepping $\beta$ by two from 2 to 20, and find it scales as:
-\be \label{eqn:betascaling}
-\apmf^{tens} \propto \beta^{1.9},
-\ee
-to an excellent approximation. 
-We use this $\beta$ power law form to handle the PMF timing dependence.}}
-
-Further note that since we have added $\beta$ to the analysis, our fisher models have increased from 6 and 11 parameter models to 7 and 12 parameter models.
-(Due to the prevalence of this change we have not listed its occurances here).\\
-
+\subsection{CMBACT / Planck PMF code}
 \reviewer{The authors report a factor of 2 difference in the normalization of the tensor mode between the public code provided by Zucca et al and a "CMBACT-derived code", saying that "the origin of the difference is unclear".
@@
 Any code that the authors might have used would be a private modification.
-Either the authors should clarify what code they are referring to, or avoid mentioning it.}
-
-As per the advice of the reviewer we have removed any mention of the CMBACT code.\\
-
-\reviewer{In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and Zucca et al.
+Either the authors should clarify what code they are referring to, or avoid mentioning it.\\
+In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and Zucca et al.
 (2016) codes".
@@
 Firstly, see the point 3 above.
-Secondly, as far as I know, Planck used a private code written primarily by Daniela Paoletti.}
+Secondly, as far as I know, Planck used a private code written primarily by Daniela Paoletti.\\
+Instead, the "improvement" comes from the fact that the analysis by Planck collaboration (as well as Zucca et al) marginalized over the PMF generation time, which negated the contribution of the PMF tensor modes to the constraints.}
+\\\\
 
-\reviewer{Instead, the "improvement" comes from the fact that the analysis by Planck collaboration (as well as Zucca et al) marginalized over the PMF generation time, which negated the contribution of the PMF tensor modes to the constraints.}
+We had indeed mistakenly attributed CMBACT to Planck. 
+The private CMBACT-derived code was used in the Polarbear PMF paper (Ade et al.
+Phys.
+Rev.
+D 92, 123509 (2015)), and did have the factor of two difference in normalization that mimicked the change in reported upper limits due to varying beta.
+We mis-identified this as the cause for the difference in the reported Planck limits.\\
 
-\reviewer{In summary, I think the paper contains some claims that need revisiting.
-I suggest repeating the analysis with the PMF generation time set free and report the bounds in that case.
-Only then they can be seriously compared to previous results in the literature.}
+We have now struck all mention of CMBACT. There is no longer a discussion of the differences in the Planck numbers since $\beta$ floats in both works.
 
-We have indeed mistakenly attributed CMBACT to Planck. After setting PMF generation time as a free parameter we find:
+\section{Minor comments:}
+\subsection{Parity-violating physics}
+\reviewer{The end of the 2nd paragraph says that this work constrains the possibility of PMFs "or parity-violating physics".
+As far as I can tell, the analysis uses only parity-even spectra, such as TT, TE, EE and BB.
+The authors should either clarify what they mean or remove the claim.}
+\\\\
 
-\diff{The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \plan+{} alone in the simple \added{8}-parameter model. 
-The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\added{PMF}. }
+In addition to producing a non-zero EB and TB power spectrum, PMFs and other parity-violating physics are also known to convert EE power into BB power.
+By looking for excess power in the BB power spectrum we can find the strength of PMFs or equate the effects of parity-violating physics to an equivalent PMF field strength.\\\\
 
-\diff{We test which datasets are important by adding single datasets to the \planck{} data, \added{and find that the source of the improvement is evenly split between \sptpol{} and \bicepkeck{}.
-	Adding either one to \planck{} yields the same 95\% CL upper limit: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$ versus  $\apmf^{\planck+\sptpol}) < \upperAsptpol$. 
-	Extending the $\beta$ prior to lower values would shift the relative weight more towards \sptpol{} (and vice-versa). 
-	Similarly, increasing the value of $n_B$ would  increase the relative importance of the smaller angular scales measured by \sptpol.}
-In short, the \added{source of the} factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is due to a more accurate measurement of the B-mode power spectrum at all scales.}
-
-\diff{Somewhat counterintuitively, the limits are somewhat better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power). }
-
-\diff{The 95\% CL upper limit on \apmf{} drops again.}
-
-\diff{Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
-We therefore importance sample the chains to apply a flat prior on \bpmf. 
-We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-\added{similar to} the limit found by Planck Collaboration et al. (2016) of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-\added{Adding the ground-based polarization measurements significantly reduces the 95\% CL upper limit to $\bpmf < \upperBall$\,nG. }
-\added{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by Zucca et al. (2016).}}
-
-\iffalse
-\changed{3.1 new}
-
-The ground-based CMB polarization data  substantially reduce the allowed PMF power; we see a factor of two reduction over \plan+{} alone in the simple \added{8}-parameter model. 
-The 95\% confidence upper limit for \planck{} is $\apmf <  \upperAplk$ for \lcdm{}+\added{PMF}.
-
-We test which datasets are important by adding single datasets to the \planck{} data, \added{and find that the source of the improvement is evenly split between \sptpol{} and \bicepkeck{}.
-Adding either one to \planck{} yields the same 95\% CL upper limit: $\apmf^{\planck+\bicepkeck} <  \upperAbicep$ versus  $\apmf^{\planck+\sptpol}) < \upperAsptpol$. 
-Extending the $\beta$ prior to lower values would shift the relative weight more towards \sptpol{} (and vice-versa). 
-Similarly, increasing the value of $n_B$ would  increase the relative importance of the smaller angular scales measured by \sptpol.}
-In short, the \added{source of the} factor of two reduction in the upper limit on \apmf{} for a nearly-scale-invariant PMF spectrum ($n_B=-2.9$) is due to a more accurate measurement of the B-mode power spectrum at all scales.
-
-Somewhat counterintuitively, the limits are somewhat better with \alens{} allowed to vary (this is due to a mild preference for \alens{} above unity which increases the lensed B-mode power).
-
-The 95\% CL upper limit on \apmf{} drops again.
-
-Given this scaling, the observed upper limits with a flat prior on \apmf{} would lead to an apparent ``detection" of \bpmf. 
-We therefore importance sample the chains to apply a flat prior on \bpmf. 
-We find a 95\% CL upper limit of $\bpmf < \upperBplk$\,nG for \planck{} alone,
-\added{similar to} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-\added{Adding the ground-based polarization measurements significantly reduces the 95\% CL upper limit to $\bpmf < \upperBall$\,nG. }
-\added{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}
-
-\changed{4.1 old}
-
-We consider the constraints on PMFs in two cosmologies. 
-Our fiducial cosmology is a \removed{11}-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf. 
-Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species.
-
-This \removed{11-parameter} model is our default cosmological model when forecasting future PMF constraints as these extensions are all well-motivated theoretically. 
-We have examined the degree to which \apmf{} is degenerate with the other 10 parameters -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case and is with the tensor-to-scalar ratio, $r$.
-
-To test the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' \removed{7-parameter} model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf.
-
-\changed{4.1 new}
-
-We consider the constraints on PMFs in two cosmologies. 
-\added{Our fiducial cosmology is a \added{12}-parameter model that extends \lcdm{} with  four  commonly considered extensions as well as PMFs:  \lcdm{} +  $r$ + \nrun{} +  \neff{} + \mnu{} + \apmf{} \changed{ + $\beta$}.}
-Here, $r$ is the tensor-to-scalar ratio, \nrun{} is running of the scalar index, \neff{} is the effective number of relativistic species, and \mnu{} is the sum of the neutrino species.
-
-This \added{12}-parameter model is our default cosmological model when forecasting future PMF constraints as these extensions are all well-motivated theoretically. 
-We have examined the degree to which \apmf{} is degenerate with the 10 parameters \added{unrelated to PMFs} -- the only strong degeneracy is in the $n_B\,=\,-2.9$ case and is with the tensor-to-scalar ratio, $r$.
-
-To test the degree to which parameter degeneracies limit the inferred constraints,  we also quote constraints from a `minimal' \added{8}-parameter model in which the PMF power is the only extension to \lcdm{}:  \lcdm{} + \apmf{} \added{ + $\beta$}.
-
-\changed{4.2 old}
-
-Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the \st{7}-parameter model to $\sigma(\apmf)=0.015$. 
-The relative improvement is larger in the more realistic st{11}-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
-Thus within the st{11}-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
-The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
-$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the other st{11}-parameters.
-
-\changed{4.2 new}
-
-Adding  EE and BB bandpowers from two stage-III experiments, \sptnew{} and \simons{}, reduces the uncertainty by an order of magnitude in the \added{8}-parameter model to $\sigma(\apmf)=0.015$. 
-The relative improvement is larger in the more realistic \added{12}-parameter model, as parameter degeneracies substantially weaken (by a factor of five) the \planck+\ho{} constraints on \apmf{}, while weakening the stage III constraint by a  more modest 40\%.
-Thus within the \added{12}-parameter model,  the addition of stage III CMB experiments improves the \apmf{} uncertainty by a factor of $\sim$\,35 to  $\sigma(\apmf)=0.022$. 
-The parameter degeneracies largely disappear for steeper PMF spectra (i.e.
-$n_B=-1$ or 2) as the PMF B-mode spectra then peaks at very small scales and this small-scale power can not be mimicked by any of the \added{other} parameters.
-
-For the \added{12}-parameter model and $n_B=-1$, adding SPT-3G and Simons Array to \planck{} leads to a 17-fold reduction in $\sigma(\apmf)$ from \fisherAlooseNbOneplk{} to \fisherAlooseNbOneSThree{}.
-
-\changed{4.3 old}
-
-\changed{4.3 new}
-
-For this fiducial configuration and the \added{12}-parameter cosmological model, we find a 3-fold reduction over the stage III experiments for all three PMF template shapes.
-
-\changed{4.4 old}
-
-\changed{4.4 new}
-
-Figure~\ref{fig:sensitivity} shows the uncertainty on \apmf{} as a function of the map noise level for the three PMF templates in either the \added{12} or \added{8}-parameter cosmological models.
-
-In the general, \added{12}-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered until the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).
-
-  The black lines are for the fiducial \added{12}-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model. 
-  The model only matters in the nearly-scale invariant PMF case, where the constraints degrade in the \added{12}-parameter model due a degeneracy with the tensor-to-scalar ratio.
-
-\changed{4.5 old}
-\changed{4.5 new}
-
-  The black lines are for the fiducial \added{12}-parameter model, while the light blue lines are for the minimal \lcdm{}+\apmf{} model.
-
-\changed{4.6 old}
-\changed{4.6 new}
-   There is essentially no difference to the preferred areas between the \added{12}-parameter cosmological model (black) or the restricted \lcdm{}+\added{PMF 8}-parameter model (light blue).
-
-\changed{4.7 old}
-\changed{4.7 new}
-11 -> 12
-7 -> 8 parameter
-\fi
+\diff{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (Carroll 1998; Lue et al.
+1999) or primordial magnetic fields (PMFs) (Kosowsky \& Loeb
+1996; Seshadri \& Subramanian 2001).  
+Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
+By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.}\\
 

### 2017-07-03 response_rnd2.tex
ref response

--- 2017-06-14 response.tex
@@
 
-\section{Major comments}
+\reviewer{1. The abstract does not mention that the constraints are derived specifically on the scale-invariant PMF, nor it mentions what $A_{PMF}$ is and how it is related to the PMF strength.}
 
-\subsection{$\beta$ should be marginalized over}
-\begin{itemize}
-\item \reviewer{The work assumes a fixed PMF template based on a model with a fixed value of the PMF generation time: $a_{\nu}/a_{PMF}$.
-This parameter is entirely arbitrary, and directly determines the amplitude of the tensor mode, which is responsible for the tight bound the authors get from BICEP2/Keck.
-I think it is misleading to present bounds based on this assumption as bounds on PMF.
-The authors should, at the very least, add a discussion of how the bound changes if one allows the PMF generation time to be a free parameter that is marginalized over.
-In such a case, the bound will be dominated by the vector mode contribution, with SPTPol likely dominating the constraints.}
+We have restated the abstract to be more clear:
+\diff{We reduce twofold the 95\% CL upper limit on the CMB anisotropy power due to a nearly-scale-invariant PMF, with an allowed B-mode power at $\ell=1500$ of $D_{\ell=1500}^{BB} < 0.071 \mu K^2$ for \planck{} versus $D_{\ell=1500}^{BB} < 0.034 \mu K^2$ for the combined dataset.
+}
+\\\\
+We have also added supporting text to the Results section:
+\diff{To facilitate a physical interpretation, we can restate these limits as an allowed B-mode power  at $\ell=1500$, which is near the peak of the PMF contribution. 
+The equivalent limits on the allowed B-mode power are $D_{\ell=1500}^{BB} < 0.071 \mu K^2$ for \planck{}-alone and $D_{\ell=1500}^{BB} < 0.034 \mu K^2$ when the ground-based experiments are added. }
+\\\\
+\reviewer{2.
+The drafts says "...
+scalar contributions are not implemented in the code", referring to the Zucca et el modification of CAMB.
+That is not true.
+Instead, it should say that the authors chose not to use the scalar contributions.}
 
-\item \reviewer{In summary, I think the paper contains some claims that need revisiting.
-I suggest repeating the analysis with the PMF generation time set free and report the bounds in that case.
-Only then they can be seriously compared to previous results in the literature.}
-\end{itemize}
-
-We agree with the referee that freeing the PMF generation time would strengthen the results, and have implemented this in both the fits to the real data and the Fisher matrix forecasts.
-All the numbers and plots have been updated with results that are marginalized over $\beta$.
-This significantly changes the results for the real data, making SPTpol more competitive with BICEP2/Keck as the referee expected. 
-The impact on the Fisher forecasts however is fairly minor.\\
-
-We have updated the text in light of this change.
-There are significant additions to Sec 2.2 (Methods) and 2.3 (PMF template) to describe what happens when $\beta$ is varied.
-The text of Sec 3 has also been updated to reflect the new upper limits (with $\beta$ marginalized over), and the lesser relative importance of BICEP2/Keck.\\
-
-Additionally, there is a small change in the first paragraph of 4.2 to describe how the prior placed on $\beta$ in the Fisher analysis.
-There are also a number of places that had referred to 6 and 11 parameter models that now refer to 7 and 12 parameter models.
+We have struck ``in the code" from the sentence.
+\\\\
+\reviewer{3.
+To a casual reader it would seem mysterious that the tensor mode amplitude depends on beta as a power of 1.9 that had to be found by fitting.
+The tensor mode spectrum is simply multiplied by a factor of $[const+ln(a_nu/a_PMF)]^2$.
+It would make more sense to simply define beta with the constant included.
+At least, the authors should explain that its 1.9 and not 2 because of the way beta was defined.}
 \\\\
 
-\subsection{CMBACT / Planck PMF code}
-\reviewer{The authors report a factor of 2 difference in the normalization of the tensor mode between the public code provided by Zucca et al and a "CMBACT-derived code", saying that "the origin of the difference is unclear".
-The public version of CMBACT is a code for CMB anisotropies from cosmic strings and does not concern PMFs.
-Any code that the authors might have used would be a private modification.
-Either the authors should clarify what code they are referring to, or avoid mentioning it.\\
-In the results section, the authors claim that "The improvement [compared to Planck] is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and Zucca et al.
-(2016) codes".
-They also claim that Planck used "the CMBACT-derived" code.
-This is a false claim.
-Firstly, see the point 3 above.
-Secondly, as far as I know, Planck used a private code written primarily by Daniela Paoletti.\\
-Instead, the "improvement" comes from the fact that the analysis by Planck collaboration (as well as Zucca et al) marginalized over the PMF generation time, which negated the contribution of the PMF tensor modes to the constraints.}
-\\\\
-
-We had indeed mistakenly attributed CMBACT to Planck. 
-The private CMBACT-derived code was used in the Polarbear PMF paper (Ade et al.
-Phys.
-Rev.
-D 92, 123509 (2015)), and did have the factor of two difference in normalization that mimicked the change in reported upper limits due to varying beta.
-We mis-identified this as the cause for the difference in the reported Planck limits.\\
-
-We have now struck all mention of CMBACT. There is no longer a discussion of the differences in the Planck numbers since $\beta$ floats in both works.
-
-\section{Minor comments:}
-\subsection{Parity-violating physics}
-\reviewer{The end of the 2nd paragraph says that this work constrains the possibility of PMFs "or parity-violating physics".
-As far as I can tell, the analysis uses only parity-even spectra, such as TT, TE, EE and BB.
-The authors should either clarify what they mean or remove the claim.}
-\\\\
-
-In addition to producing a non-zero EB and TB power spectrum, PMFs and other parity-violating physics are also known to convert EE power into BB power.
-By looking for excess power in the BB power spectrum we can find the strength of PMFs or equate the effects of parity-violating physics to an equivalent PMF field strength.\\\\
-
-\diff{CMB B-mode measurements can also be used to constrain more exotic models, such as the possible existence of cosmic birefringence (Carroll 1998; Lue et al.
-1999) or primordial magnetic fields (PMFs) (Kosowsky \& Loeb
-1996; Seshadri \& Subramanian 2001).  
-Both effects lead to the rotation of E-modes into B-modes \textbf{which leads to an increase in power in the BB spectrum.}
-By equating the magnitude of the resulting B-modes, parity-violating processes can be translated into an equivalent PMF strength.}\\
-
 \end{document}

### 2017-07-03 pmf.tex
beta scaling
ref response

--- 2017-06-13 pmf.tex
@@
 \newcommand{\gab}[1]{\textcolor{Orchid}{[{\bf GS}: #1]}}
-\newcommand{\changed}[1]{\textcolor{Red}{#1}}
-\newcommand{\removed}[1]{\textcolor{Red}{}}
+\newcommand{\changed}[1]{\textcolor{Black}{#1}}
+\newcommand{\removed}[1]{\textcolor{Black}{}}
 \include{number_list}
@@
 We present new limits on the amplitude of potential primordial magnetic fields (PMFs) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol.
-We reduce twofold the 95\% CL upper limit on the CMB anisotropy power due to PMFs, from $\apmf < \upperAplk$ for \planck{} alone to $\apmf < \upperAall$ for the combined dataset. 
+We reduce twofold the 95\% CL upper limit on the CMB anisotropy power due to a nearly-scale-invariant PMF, with an allowed B-mode power at $\ell=1500$ of $D_{\ell=1500}^{BB} < 0.071 \mu K^2$ for \planck{} versus $D_{\ell=1500}^{BB} < 0.034 \mu K^2$ for the combined dataset.
+%$\apmf < \upperAplk$ for \planck{} alone to $\apmf < \upperAall$ for the combined dataset. 
 %Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
@@
 For each value of $n_B$, we use publicly released modifications to CAMB from \citet{zucca16} to calculate a PMF template for the CMB TT, TE, EE and BB power spectra at fixed parameters: \bpmf = 2.5\,nG and $\beta=20.72$ ($a_{\nu}/a_{\rm{PMF}} = 10^9$).}
-The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented in the code. 
+The calculated templates include tensor and vector PMF contributions; scalar contributions are not implemented. 
 The lack of scalar terms should not matter for CMB polarization data. 
@@
 Adding the ground-based experiments brings this limit to $\apmf <  \upperAall$. 
+To facilitate a physical interpretation, we can restate these limits as an allowed B-mode power  at $\ell=1500$, which is near the peak of the PMF contribution. 
+The equivalent limits on the allowed B-mode power are $D_{\ell=1500}^{BB} < 0.071 \mu K^2$ for \planck{}-alone and $D_{\ell=1500}^{BB} < 0.034 \mu K^2$ when the ground-based experiments are added. 
 We test which datasets are important by adding single datasets to the \planck{} data, \changed{and find that the source of the improvement is evenly split between \sptpol{} and \bicepkeck{}. 
@@
 Next we introduce inflationary gravitational waves, as parameterized by the tensor-to-scalar ratio r. 
-The 95\% CL upper limit on \apmf{} drops \st{slightly} again.  
+The 95\% CL upper limit on \apmf{} drops again.  
 This is easily understood as a splitting of the large-scale B-mode power between two positive-definite terms: r and \apmf{}.
@@
 \changed{similar to} the limit found by \citet{planck15-19} of $\bpmf < 2.0$\,nG with $n_B=-2.9$ held fixed as we have done. 
-\st{The improvement is due to a difference in the calculated tensor PMF power (for the same parameters) between the CMBACT-derived and} \citet{zucca16} \st{codes.}
-\st{Using the CMBACT-derived code that} \citet{planck15-19} \st{used, we find a consistent upper limit of $\bpmf < 1.9$\,nG.}
 \changed{Adding the ground-based polarization measurements significantly reduces the 95\% CL upper limit to $\bpmf < \upperBall$\,nG. }
-\st{The improvement from adding more data is less than one might predict because the combined likelihood peaks approximately $1\,\sigma$ above zero, whereas the \planck{}-only constraints peaks at zero.
-}
 \changed{Due to the inclusion of the \bicepkeck{} and POLARBEAR data, these results are slightly lower than the \planck{} + \sptpol{} upper limit of $<1.2\,$nG quoted by \citet{zucca16}.}
@@
 It appears that even in the nearly scale-invariant case, the PMF constraint is coming primarily from smaller angular scales due to the degeneracy \changed{at large angular scales with both the tensor-to-scalar ratio and the PMF timing parameter $\beta$}.
-\st{Without this degeneracy, i.e. in the simple \lcdm{}+\apmf{} model, dropping \lknee{} from 400 to 50 reduces the uncertainty by a factor of 3.2 for a nearly scale-invariant PMF. 
-In this case, the degradation accelerates once the 1/f knee rises to $\lknee{} \gtrsim 70$. 
-This is consistent with the earlier statement for the same simple model that the current upper limits are dominated by the BICEP2/Keck Array data at low-$\ell$. }
 For the bluer PMF spectra ($n_B=-1$ or 2), the forecasts show no dependence on the knee frequency. 
@@
 
-We thank the \changed{referee as well as} Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
+We thank the referee as well as Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
 CR is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 

### 2017-07-24 pmf.tex
beta scalin response

@@
 
-\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
-We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as $\beta^{1.9}$ to an excellent approximation. 
+\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, and is expected to scale approximately as $\beta^2$ \citep{lewis04,shaw10b}.   
+We double-check this expectation for $\beta$ in the range 2 to 20 using the  \citet{zucca16} code, and find the computed tensor power scales as $\beta^{1.9}$
 We use this $\beta$ power law form to handle the PMF timing dependence. 

### 2017-07-24 response_rnd2.tex
beta scaling response

@@
 \\\\
+We prefer to keep the current definition of $\beta$ rather than introducing an additional additive constant, as it parallels the definitions used in previous constraints.
+For instance, Zucca et al 2016 define $\beta$ around Table II as $\beta = log_{10}(\tau_\nu/\tau_B)$; Planck 2015 results.
+
+We have edited the language to better reflect the expectation:
+\diff{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling, and is expected to scale approximately as $\beta^2$ \citep{lewis04,shaw10b}.   
+We double-check this expectation for $\beta$ in the range 2 to 20 using the  \citet{zucca16} code, and find the computed tensor power scales as $\beta^{1.9}$. }
 

### 2017-08-09 pmf.tex
fixed typos

@@
 \ee
-\changed{The calculation of the PMF templates, \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
+\changed{The calculation of the PMF templates, \cpmfvec{} and \cpmftens{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
 The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events. }
@@
 The lack of scalar terms should not matter for CMB polarization data. 
-Temperature data is not the main focus of this work, and  and we find our \planck{} results  to be consistent with \citet{planck15-19}, suggesting the impact of the scalar terms is minor. 
+Temperature data is not the main focus of this work, and we find our \planck{} results  to be consistent with \citet{planck15-19}, suggesting the impact of the scalar terms is minor. 
 The PMF templates are plotted against other signals in the CMB B-mode power spectrum in Fig.~\ref{fig:pmf-bb} \changed{and against each other in Fig.~\ref{fig:pmf-nb}. }
